### 2012-07-19 paper.tex
Add paper template.
And it was good.

%%% template.tex
%%%
%%% This LaTeX source document can be used as the basis for your technical
%%% paper or abstract. Intentionally stripped of annotation, the parameters
%%% and commands should be adjusted for your particular paper - title, 
%%% author, article DOI, etc.
%%% The accompanying ``template.annotated.tex'' provides copious annotation
%%% for the commands and parameters found in the source document. (The code
%%% is identical in ``template.tex'' and ``template.annotated.tex.'')

\documentclass[annual]{acmsiggraph}

\TOGonlineid{45678}
\TOGvolume{0}
\TOGnumber{0}
\TOGarticleDOI{1111111.2222222}
\TOGprojectURL{}
\TOGvideoURL{}
\TOGdataURL{}
\TOGcodeURL{}

\title{Goes Here}

\author{}
\pdfauthor{}

\keywords{}

\begin{document}

%% \teaser{
%%   \includegraphics[height=1.5in]{images/sampleteaser}
%%   \caption{Spring Training 2009, Peoria, AZ.}
%% }

\maketitle

\begin{abstract}

\end{abstract}

\keywordlist

\TOGlinkslist

\copyrightspace

\section{Introduction}

\section{Conclusion}
\section*{Acknowledgements}

\bibliographystyle{acmsiggraph}
\bibliography{template}
\end{document}

### 2012-07-28 paper.tex
Experiments

@@
 \section{Introduction}
+\section{System Description}
+\subsection{Input API}
+Specification of an optimization problem using our API.
+\subsection{Optimization Framework}
+Describe four main components and some built-in libraries.
+\section{Experiments}
+\subsection{Previous Work}
+Subsurface scattering. Mechanical properties
+\subsection{Textured Model}
+Input: a textured 3D model and
+	measured Albedo of print material.
 
+Output: (Probably gray-scale) Material arranged for different printers in different formats: STL, fable,Gcode.
+
+Printers: Our printer, Makerbot, Objet, maybe Zcorp.
+
+\subsection{New Examples for Mechanical Properties}
+Ball bounce to certain height. Loaded dice.
+
+Printer:objet, ours.
+
+\section{Possible Extension}
+UI to specify input deformation.
 \section{Conclusion}

### 2012-07-29 paper.tex
Intro

@@
 \section{Introduction}
+3D printing has the potential to dramatically reduce the required time and cost of
+fabricating custom materials and objects. In particular, it allows the fabrication of materials with complex internal
+structures that are difficult or impossible to manufacture with other technologies. Additive manufacturing could be
+much more widely adopted and easier to use, given a high-fidelity translation from specifications of objects defined
+in terms of their mechanical, optical, and appearance properties to output-device-specific computer
+programs that produce the best possible approximation of these digital objects. However, this is still one of
+the most important unsolved problems in digital direct manufacturing. Due to its combinatorial nature, this
+problem becomes more and more challenging as the range of different printable materials increases. This paper
+aims to provide an abstraction mechanism and a software framework for translating specifications to fabrication
+instructions. It is possible to design a computationally efficient and general process for translating virtual objects
+with desired mechanical, electrical, optical, and appearance properties into composite printable materials.
+We will achieve this goal through a reduction-optimization-simulation approach.
+\section{Previous Work}
+
 \section{System Description}
+The software framework (shown in Figure~\ref{fig:framework}) is composed of 
+a set of software
+modules that can be easily modified or exchanged. The first component
+of this framework is an output-device-independent description API
+that allows the user to specify any physical object in terms of its physical
+properties such as geometry, mechanical behaviors, and appearance. 
+The framework will also provide physically-based
+simulation tools that accurately predict the behavior of our output device.
+The goal of the optimization module is to search through
+the space of possible device outputs and deliver one that best matches the
+desired model. In order to evaluate the quality of the match between the
+simulation output and the desired model we need to develop appropriate
+comparison metrics. Finally, a central component of our framework is
+a reduction model which makes the optimization problem tractable by
+reducing the search space as much as possible.
+The reduction model can specified by experts or deduced from a
+set of examples. Next, we will describe each element of the framework in
+more detail.
+\begin{figure}
+\caption{API overview}
+\label{fig:framework}
+\end{figure}
 \subsection{Input API}
-Specification of an optimization problem using our API.
+Our input API allows a designer to either
+define material properties for sections of an object
+or specify behavior of an object. 
+The designer
+can use functions to describe properties such as reflectance (e.g., BRDFs, BSSRDFs), 
+stiffness, or other spatially varying properties. 
+Although it is possible to define the object directly by only specifying material
+properties, intuitive user
+interfaces will aid in specifying the objects and their properties
+in terms of intuitive metaphors.
+For example, the elastic properties of an object can be specified by a set of
+example displacements from the rest pose and the corresponding applied forces.
 \subsection{Optimization Framework}

### 2012-07-29 paper.tex
empty teaser
Paste Optimization and simulation text

--- 2012-07-28 paper.tex
@@
 
+\usepackage{caption}
+\usepackage{subcaption}
+
 \title{Goes Here}
@@
 
-%% \teaser{
-%%   \includegraphics[height=1.5in]{images/sampleteaser}
-%%   \caption{Spring Training 2009, Peoria, AZ.}
-%% }
+ \teaser{
+   \begin{subfigure}[b]{0.3\textwidth}
+	\centering
+%    	\includegraphics[width=\textwidth]{a}
+      	\caption{}
+        \label{teaser:original}
+        \end{subfigure}
+        ~ 
+        \begin{subfigure}[b]{0.3\textwidth}
+                \centering
+%    	\includegraphics[width=\textwidth]{a}
+                \caption{}
+                \label{teaser:ours}
+        \end{subfigure}
+        ~
+        \begin{subfigure}[b]{0.3\textwidth}
+                \centering
+%    	\includegraphics[width=\textwidth]{a}
+                \caption{}
+                \label{teaser:makerbot}
+        \end{subfigure}
+        ~
+        \begin{subfigure}[b]{0.3\textwidth}
+                \centering
+%    	\includegraphics[width=\textwidth]{a}
+                \caption{}
+                \label{teaser:objet}
+        \end{subfigure}
+        \caption{A textured mesh printed with different types of 3D printers.
+        	(a)original model.(b)printed with our printer.(c)makerbot.
+        	(d)objet}\label{teaser}
+ }
 
@@
 \section{Introduction}
+3D printing has the potential to dramatically reduce the required time and cost of
+fabricating custom materials and objects. In particular, it allows the fabrication of materials with complex internal
+structures that are difficult or impossible to manufacture with other technologies. Additive manufacturing could be
+much more widely adopted and easier to use, given a high-fidelity translation from specifications of objects defined
+in terms of their mechanical, optical, and appearance properties to output-device-specific computer
+programs that produce the best possible approximation of these digital objects. However, this is still one of
+the most important unsolved problems in digital direct manufacturing. Due to its combinatorial nature, this
+problem becomes more and more challenging as the range of different printable materials increases. This paper
+aims to provide an abstraction mechanism and a software framework for translating specifications to fabrication
+instructions. It is possible to design a computationally efficient and general process for translating virtual objects
+with desired mechanical, electrical, optical, and appearance properties into composite printable materials.
+We will achieve this goal through a reduction-optimization-simulation approach.
+\section{Previous Work}
+
 \section{System Description}
+The software framework (shown in Figure~\ref{fig:framework}) is composed of 
+a set of software
+modules that can be easily modified or exchanged. The first component
+of this framework is an output-device-independent description API
+that allows the user to specify any physical object in terms of its physical
+properties such as geometry, mechanical behaviors, and appearance. 
+The framework will also provide physically-based
+simulation tools that accurately predict the behavior of our output device.
+The goal of the optimization module is to search through
+the space of possible device outputs and deliver one that best matches the
+desired model. In order to evaluate the quality of the match between the
+simulation output and the desired model we need to develop appropriate
+comparison metrics. Finally, a central component of our framework is
+a reduction model which makes the optimization problem tractable by
+reducing the search space as much as possible.
+The reduction model can specified by experts or deduced from a
+set of examples. Next, we will describe each element of the framework in
+more detail.
+\begin{figure}
+\caption{API overview}
+\label{fig:framework}
+\end{figure}
 \subsection{Input API}
-Specification of an optimization problem using our API.
-\subsection{Optimization Framework}
+Our input API allows a designer to either
+define material properties for sections of an object
+or specify behavior of an object. 
+The designer
+can use functions to describe properties such as reflectance (e.g., BRDFs, BSSRDFs), 
+stiffness, or other spatially varying properties. 
+Although it is possible to define the object directly by only specifying material
+properties, intuitive user
+interfaces will aid in specifying the objects and their properties
+in terms of intuitive metaphors.
+For example, the elastic properties of an object can be specified by a set of
+example displacements from the rest pose and the corresponding applied forces.
+\subsection{Search Space Reduction and Optimization}
 Describe four main components and some built-in libraries.
+In our
+framework, we propose an optimization component that
+searches through the space of all possible device outputs
+obtained by the simulator to nd the one that best reproduces
+the desired object. Unfortunately, this search space
+is usually high-dimensional. For example, when the printing
+volume has N voxels and each of these voxels can be
+assigned to one of M base materials, the search space
+has NM dimensions. To overcome this problem, we reduce
+the search space to a lower-dimensional space using
+a reduction model. The goal of the reduction step is to
+shrink the search space as much as possible but at the
+same time not to prune out good solutions. The reduced
+space allows for the use of standard optimization techniques such as simulated annealing, genetic algorithms,
+Markov Chain Monte Carlo methods, and even an exhaustive search. The low-dimensional space produced by the
+reducer can be dened in two dierent ways. First, a reduction model can be explicitly specied by an expert, for
+example, by dening structures of base materials and rules how dierent base materials can be combined together.
+The second way to specify a reduction model is implicit. In this case, the user provides a set of examples of
+valid material structures. Then, a machine learning algorithm infers both basic material structures and the rules
+for combining them. The optimization framework can be further improved by employing techniques that cluster
+partial solutions that yield similar output properties [1], avoiding combinatorial explosion of the search space.
+Furthermore, we can employ bounds on the solution based on physical constraints of the base materials.
+\subsection{Simulation}
+Another key step in the process of converting abstractions to physical output is being able to
+simulate what an output device is going to generate given a well-defined input. A simulation allows the
+user to preview how the output will look and behave. This simulation is a generalization of the print-preview function
+available in word processing applications. As physical output generation might be costly or time-consuming, it
+is extremely beneficial for users to be able to preview the output and make immediate changes to the design. That
+means that the simulation must accurately predict the output. It's necessary to develop very efficient and accurate rendering
+and finite element simulation packages. Since we run the simulation multiple times within the optimization method
+we can cache and reuse partial simulation results, speeding up the evaluation process at least 10-100 times. Furthermore,
+we will ensure that the simulation is accurate by measuring properties of the printing materials and using
+these measurements to estimate the parameters of data-driven material models (e.g., for elasticity, reflectance).
 \section{Experiments}

### 2012-07-30 paper.tex
fix 'f'

@@
 Markov Chain Monte Carlo methods, and even an exhaustive search. The low-dimensional space produced by the
-reducer can be dened in two dierent ways. First, a reduction model can be explicitly specied by an expert, for
-example, by dening structures of base materials and rules how dierent base materials can be combined together.
+reducer can be defined in two different ways. First, a reduction model can be explicitly specified by an expert, for
+example, by defining structures of base materials and rules how different base materials can be combined together.
 The second way to specify a reduction model is implicit. In this case, the user provides a set of examples of

### 2012-07-30 paper.tex
Copy more text from proposal

@@
 \section{Previous Work}
+\subsection{Simulation of the Appearance of Ink Combinations}
+[20] built a system
+for the measurement of Bidirectional Reflectance Distribution Functions (BRDFs) and were able
+to acquire BRDFs for both single-layer and multi-layer ink printouts (e.g., an ink covered by a
+varnish layer). They then acquired a database of many different combinations of ink layers (up to
+seven layer combinations were considered). However, they did not develop a method to simulate
+the appearance of arbitrary ink layers. They were able to interpolate the appearance by spatially
+multiplexing small tiles of different base combinations. By linearity of light transport, the simulation
+of the combined appearance was reduced to linear combinations of the base BRDFs. 
+simulation method for the appearance of translucent materials [59]. 
+They
+built a measurement system for estimating multiple-scattering in homogeneous material slabs. They
+measured both transmission and refection for a set of base materials used by the OBJET Connex
+multi-material printer. 
+Using these measurements, our simulations framework was able to predict
+diffuse reflections and transmissions in multi-layered translucent objects composed of base material
+layers.
+In the proposed research, we will extend these methods to cover the complete appearance of
+volumetric materials that accounts for both directly reflected light and light scattering within the
+material volume. 
+We will use efficient simulation methods that allows us to simulate the appearance
+of complex structures composed from these base materials. We developed an initial framework for
+simulating behavior of multi-layered materials, where each layer is a homogeneous base material.
+Then we extend this simulation to materials in which each voxel is made of a different measured
+material. Since this general simulation is expensive and requires path-tracing algorithms, we used
+algorithms that are based on fast numerical integration of our low-dimensional representations
+and the use of pre-computation, similar to pre-computed light transport approaches [63].
+\subsection{Simulation of Deformation Behavior}
+In previous work, the problem
+of modeling and simulating soft materials and their deformation behavior [22, 60].
+In order to accurately model deformation behaviors they built a system that allowed measuring how
+a given material deforms subject to a variety of external forces. 
+The system used an automated
+robot arm to apply desired forces and a vision subsystem to measure corresponding surface deformations.
+We modeled deformation behavior of a material using a stress-strain relationship. Since
+the deformation behavior of many of our materials was non-linear, we developed a model that could
+accurately represent this behavior and that was also easy to fit to the surface measurements. In
+our model, the stress-strain relationship was represented as a collection of linear stress-strain relationships.
+We used a properly chosen function to interpolate between these linear relationships
+and obtain a non-linear model. Using this system and model we could accurately measure material
+deformation of a collection of materials produced by a multi-material printer and fit these observation
+to the stress-strain model. Then, using this material model within a Finite Element Method
+we could accurately simulate behavior of any shape made from a composite of measured materials.
+In the proposed research, we would like to address the shortcomings of our current measurement
+and models. First, our current approach handles only elastic material deformation. We would like to
+extend our current data-driven model to viscoelastic materials. In fact, most real materials exhibit
+this property, which is characterized by hysteresis (or material memory). For these materials, it is
+not possible to predict the behavior of a material only based on the currently applied stress. One also
+has to know the history (or the sequence) of applied stress values to accurately simulate material
+behavior. In order to determine the material model one has to measure the so called hysteresis
+loops in the stress-strain space (as opposed to a single stress-strain curve for elastic materials). The
+hysteresis loop is the result of the damping effect which causes the material to behave differently
+depending whether stress is applied or removed as some of the energy is dissipated within the
+material into heat. Additional advantage of using this material model is that it will allow us to
+handle dynamic material deformations.
 
+In order to measure viscoelastic material properties, we will need to modify our current measurement
+system and procedures. We will use repeatable, time-coded measurements to estimate
+Figure 5: From left to right: Force-and-deformation capture of a non-linear heterogeneous pillow;
+synthesized deformation with fitted material parameters; and interactive deformation synthesized
+with our soft tissue modeling technique using scattered data interpolation [60].
+
+We will also use faster resonating actuators and high-speed
+camera systems to track material deformations at high frame rates. Furthermore, we plan to track
+the whole material volume rather than the outer material surface. This is possible since we can
+print materials in clear color as well. Thus small color-coded markers can be easily embedded into
+the material structure. These markers can be tracked in 3D using a multi-camera system.
 \section{System Description}
@@
 framework, we propose an optimization component that
-searches through the space of all possible device outputs
-obtained by the simulator to nd the one that best reproduces
+searches through the space of possible device inputs
+to find the one that best reproduces
 the desired object. Unfortunately, this search space
@@
 assigned to one of M base materials, the search space
-has NM dimensions. To overcome this problem, we reduce
+has $N^M$ dimensions. To overcome this problem, we reduce
 the search space to a lower-dimensional space using
@@
 for combining them. The optimization framework can be further improved by employing techniques that cluster
-partial solutions that yield similar output properties [1], avoiding combinatorial explosion of the search space.
+partial solutions that yield similar output properties, avoiding combinatorial explosion of the search space.
 Furthermore, we can employ bounds on the solution based on physical constraints of the base materials.
+
 \subsection{Simulation}
 Another key step in the process of converting abstractions to physical output is being able to
-simulate what an output device is going to generate given a well-defined input. A simulation allows the
-user to preview how the output will look and behave. This simulation is a generalization of the print-preview function
-available in word processing applications. As physical output generation might be costly or time-consuming, it
-is extremely beneficial for users to be able to preview the output and make immediate changes to the design. That
-means that the simulation must accurately predict the output. It's necessary to develop very efficient and accurate rendering
+simulate what an output device is going to generate given a well-defined input. 
+A simulation allows the user to preview how the output will look and behave. 
+This simulation is a generalization of the print-preview function
+available in word processing applications.
+As physical output generation might be costly or time-consuming, 
+it is extremely beneficial for users to be able to preview the output and make immediate changes to the design.
+That means that the simulation must accurately predict the output. 
+It's necessary to develop very efficient and accurate rendering
 and finite element simulation packages. Since we run the simulation multiple times within the optimization method
-we can cache and reuse partial simulation results, speeding up the evaluation process at least 10-100 times. Furthermore,
-we will ensure that the simulation is accurate by measuring properties of the printing materials and using
+we can cache and reuse partial simulation results, speeding up the evaluation process at least 10-100 times.
+Furthermore, we will ensure that the simulation is accurate by measuring properties of the printing materials and using
 these measurements to estimate the parameters of data-driven material models (e.g., for elasticity, reflectance).
+\section{Programming with Our API}
+
 \section{Experiments}

### 2012-07-30 paper.tex
code example

@@
 example displacements from the rest pose and the corresponding applied forces.
-\subsection{Search Space Reduction and Optimization}
-Describe four main components and some built-in libraries.
-In our
-framework, we propose an optimization component that
+\subsection{Search Space Decomposition and Reduction}
+Our framework includes an optimization component that
 searches through the space of possible device inputs
@@
 assigned to one of M base materials, the search space
-has $N^M$ dimensions. To overcome this problem, we reduce
+has $N^M$ dimensions. To overcome this problem, we decompose the search
+space into similar subproblems and also reduce
 the search space to a lower-dimensional space using
@@
 shrink the search space as much as possible but at the
-same time not to prune out good solutions. The reduced
-space allows for the use of standard optimization techniques such as simulated annealing, genetic algorithms,
-Markov Chain Monte Carlo methods, and even an exhaustive search. The low-dimensional space produced by the
+same time not to prune out good solutions. The low-dimensional space produced by the
 reducer can be defined in two different ways. First, a reduction model can be explicitly specified by an expert, for
@@
 Furthermore, we can employ bounds on the solution based on physical constraints of the base materials.
-
+\section{Optimization}
+Our optimization component is an interface to 
+existing standard optimization techniques
+such as simulated annealing, genetic algorithms and
+Markov Chain Monte Carlo methods, as well as custom optimization algorithms implemented
+by more advanced users.
 \subsection{Simulation}
@@
 \section{Programming with Our API}
+Code examples:
+To generate textured model:
+\begin{verbatim}
+Manager manager;
+manager.loadMaterialLibrary("material_file");
+manager.setGenerator(new HeightFieldGenerator());
+manager.setSimulator(new SomeColorSimulator());
+manager.setMetric(new SomeColorMetric());
+manager.setOptimizer(
+  new SimulatedAnealing/GradientDescent());
+Objective obj;
+Scene scene;
+TexturedShape shape("filename"), goal("filename1");
+scene.addShape(shape);
+obj.setScene(scene);
+obj.setGoal(goal);
+manager.addObjective(obj);
+\end{verbatim}
 
+To generate BRDF
+\begin{verbatim}
+manager.setGenerator(new StackingGenerator());
+manager.setSimulator(new BRDFSimulator());
+manager.setMetric(new SomeImageMetric());
+Shape shape("filename"), 
+Image goal("filename1");
+\end{verbatim}
+
+Deformation
+\begin{verbatim}
+scene.addForce(new Force(pos, dir, shapeID));
+scene.addConstraint(
+  new Constraint(FIX_VERTEX, vertexList, shapeID));
+Shape goal;
+manager.setSimulator(new FEMSimulator());
+\end{verbatim}
 \section{Experiments}

### 2012-07-30 paper.tex
figures

@@
 Scene scene;
-TexturedShape shape("filename"), goal("filename1");
+TexturedShape shape("filename");
+TexturedShape goal("filename1");
 scene.addShape(shape);
@@
 scene.addConstraint(
-  new Constraint(FIX_VERTEX, vertexList, shapeID));
+  new Constraint(
+    FIX_VERTEX, vertexList, shapeID));
 Shape goal;
@@
 \end{verbatim}
+
 \section{Experiments}
@@
 Subsurface scattering. Mechanical properties
+\begin{figure}
+\begin{subfigure}[b]{0.3\textwidth}
+	\centering
+% 	\includegraphics[width=\textwidth]{a}
+   	\caption{}
+    \label{fig:ssOrigin}
+    \end{subfigure}
+    ~ 
+    \begin{subfigure}[b]{0.3\textwidth}
+    \centering
+%  	\includegraphics[width=\textwidth]{a}
+    \caption{}
+    \label{fig:ssPrint}
+\end{subfigure}
+\caption{Subsurface Scattering. (a)Original object. (b)Printed model.}
+\label{fig:SS}
+\end{figure}
+
+\begin{figure}
+\begin{subfigure}[b]{0.3\textwidth}
+	\centering
+% 	\includegraphics[width=\textwidth]{a}
+   	\caption{}
+    \label{fig:deformPhoto}
+    \end{subfigure}
+    ~ 
+    \begin{subfigure}[b]{0.3\textwidth}
+    \centering
+%  	\includegraphics[width=\textwidth]{a}
+    \caption{}
+    \label{fig:deformPrint}
+\end{subfigure}
+\caption{Matching deformation. (a)photo of a slab being pushed. (b)Printed model being pushed.}
+\label{fig:deform}
+\end{figure}
+
+Two error plots showing subsurface scattering and deformation errors decrease
+after each iteration in Figure~\ref{fig:err}.
+
+\begin{figure}
+\begin{subfigure}[b]{0.3\textwidth}
+	\centering
+% 	\includegraphics[width=\textwidth]{a}
+   	\caption{}
+    \label{fig:ssErr}
+    \end{subfigure}
+    ~ 
+    \begin{subfigure}[b]{0.3\textwidth}
+    \centering
+%  	\includegraphics[width=\textwidth]{a}
+    \caption{}
+    \label{fig:deformErr}
+\end{subfigure}
+\caption{Error plots for 
+optimizing subsurface-scattering and deformation properties 
+iteratively. (a)Subsurface scattering errors. (b)Deformation errors.}
+\label{fig:err}
+\end{figure}
+
 \subsection{Textured Model}

### 2012-07-30 paper.tex
some citation

@@
 \subsection{Simulation of the Appearance of Ink Combinations}
-[20] built a system
+\cite{Matusik:2009} built a system
 for the measurement of Bidirectional Reflectance Distribution Functions (BRDFs) and were able
@@
 of the combined appearance was reduced to linear combinations of the base BRDFs. 
-simulation method for the appearance of translucent materials [59]. 
+simulation method for the appearance of translucent materials \cite{Hasan:2010}. 
 They
@@
 algorithms that are based on fast numerical integration of our low-dimensional representations
-and the use of pre-computation, similar to pre-computed light transport approaches [63].
+and the use of pre-computation, similar to pre-computed light transport approaches \cite{Sloan:2002}.
 \subsection{Simulation of Deformation Behavior}
 In previous work, the problem
-of modeling and simulating soft materials and their deformation behavior [22, 60].
+of modeling and simulating soft materials and their deformation behavior \cite{Bickel:2010,Bickel:2009}.
 In order to accurately model deformation behaviors they built a system that allowed measuring how
@@
 synthesized deformation with fitted material parameters; and interactive deformation synthesized
-with our soft tissue modeling technique using scattered data interpolation [60].
+with our soft tissue modeling technique using scattered data interpolation \cite{Bickel:2010}.
 
@@
 Manager manager;
-manager.loadMaterialLibrary("material_file");
-manager.setGenerator(new HeightFieldGenerator());
-manager.setSimulator(new SomeColorSimulator());
-manager.setMetric(new SomeColorMetric());
+manager.loadMaterialLib("material_file");
+manager.setGenerator(
+  new HeightFieldGenerator());
+manager.setSimulator(colorSimulator());
+manager.setMetric(someColorMetric());
 manager.setOptimizer(
-  new SimulatedAnealing/GradientDescent());
+  simulatedAnealing);
+  //or e.g. gradientDescent
 Objective obj;
@@
 \begin{verbatim}
-manager.setGenerator(new StackingGenerator());
-manager.setSimulator(new BRDFSimulator());
-manager.setMetric(new SomeImageMetric());
+manager.setGenerator(stackingGenerator);
+manager.setSimulator(brdfSimulator);
+manager.setMetric(someImageMetric);
 Shape shape("filename"), 
@@
 \begin{verbatim}
-scene.addForce(new Force(pos, dir, shapeID));
-scene.addConstraint(
-  new Constraint(
+force = new Force(pos, dir, shapeID);
+constraint = new Constraint(
     FIX_VERTEX, vertexList, shapeID));
+
+scene.addForce(force);
+scene.addConstraint(constraint);
 Shape goal;
-manager.setSimulator(new FEMSimulator());
+manager.setSimulator(femSimulator);
 \end{verbatim}
@@
 	\centering
-% 	\includegraphics[width=\textwidth]{a}
+ %	\includegraphics[width=\textwidth]{Spec2FabData.png}
    	\caption{}
@@
 %  	\includegraphics[width=\textwidth]{a}
-    \caption{}
+    \caption{b}
     \label{fig:ssPrint}
@@
 \bibliographystyle{acmsiggraph}
-\bibliography{template}
+\bibliography{paper}
 \end{document}

### 2012-07-31 paper.tex
add figures

@@
 \usepackage{subcaption}
-
+\usepackage[english]{babel}
 \title{Goes Here}
@@
 	\centering
-%    	\includegraphics[width=\textwidth]{a}
+    	\includegraphics[width=0.6\textwidth]{figure/bunny_orig.png}
       	\caption{}
@@
         ~ 
-        \begin{subfigure}[b]{0.3\textwidth}
+        \begin{subfigure}[b]{0.18\textwidth}
                 \centering
-%    	\includegraphics[width=\textwidth]{a}
+    	\includegraphics[width=\textwidth]{figure/bunny_print1.jpg}
                 \caption{}
@@
         ~
-        \begin{subfigure}[b]{0.3\textwidth}
+        \begin{subfigure}[b]{0.2\textwidth}
                 \centering
-%    	\includegraphics[width=\textwidth]{a}
+    	\includegraphics[width=\textwidth]{figure/bunny_print2.jpg}
                 \caption{}
@@
         ~
-        \begin{subfigure}[b]{0.3\textwidth}
+        \begin{subfigure}[b]{0.18\textwidth}
                 \centering
-%    	\includegraphics[width=\textwidth]{a}
+    	\includegraphics[width=\textwidth]{figure/bunny_print3.jpg}
                 \caption{}
@@
 Furthermore, we can employ bounds on the solution based on physical constraints of the base materials.
-\section{Optimization}
+\subsection{Optimization}
 Our optimization component is an interface to 
@@
 Subsurface scattering. Mechanical properties
-\begin{figure}
-\begin{subfigure}[b]{0.3\textwidth}
-	\centering
- %	\includegraphics[width=\textwidth]{Spec2FabData.png}
-   	\caption{}
-    \label{fig:ssOrigin}
-    \end{subfigure}
-    ~ 
-    \begin{subfigure}[b]{0.3\textwidth}
-    \centering
-%  	\includegraphics[width=\textwidth]{a}
-    \caption{b}
-    \label{fig:ssPrint}
-\end{subfigure}
-\caption{Subsurface Scattering. (a)Original object. (b)Printed model.}
-\label{fig:SS}
-\end{figure}
+A figure showing a material with a particular
+look and deformation properties is shown in Figure~\ref{fig:deform}
 
@@
 	\centering
-% 	\includegraphics[width=\textwidth]{a}
+ 	\includegraphics[width=\textwidth]{figure/slab_origin.png}
    	\caption{}
@@
     \centering
-%  	\includegraphics[width=\textwidth]{a}
+  	\includegraphics[width=\textwidth]{figure/slab_deform.png}
     \caption{}
@@
 \end{subfigure}
-\caption{Matching deformation. (a)photo of a slab being pushed. (b)Printed model being pushed.}
+\caption{Simutaneously matching appearance and deformation. 
+(a)Original slab of a particular looking. (b)printed slab 
+with the same looking and desired deformation.}
 \label{fig:deform}
@@
 	\centering
-% 	\includegraphics[width=\textwidth]{a}
+ 	\includegraphics[width=\textwidth]{figure/error.pdf}
    	\caption{}
@@
     \centering
-%  	\includegraphics[width=\textwidth]{a}
+  	\includegraphics[width=\textwidth]{figure/error.pdf}
     \caption{}
@@
 
+We expand gamut of printable colors by stacking translucent materials. We then applied
+dithering with our expanded colors.
 \subsection{New Examples for Mechanical Properties}
-Ball bounce to certain height. Loaded dice.
+Ball bounce to certain height.
+
+A plot of bounce height after each iteration.
+
+Loaded dice. It has a certain probability to land on "1".
+A table of probability distribution of landing on each side
+is shown in Table~\ref{tab:dice}.
+
+\begin{table}
+\centering
+  \begin{tabular}{ |c| p{0.7in} | p{0.7in} | }
+  \hline
+  face & simulated probability & measured probability\\
+  \hline
+  1 & 0.5 & 0.5\\
+  \hline
+  2 & 0.1 & 0.1\\
+  \hline
+  3 & 0.1 & 0.1\\
+  \hline
+  4 & 0.1 & 0.1\\
+  \hline
+  5 & 0.1 & 0.1\\
+  \hline
+  6 & 0.1 & 0.1\\
+
+  \hline
+  \end{tabular}
+  \caption{Simulated and measured dice probability}
+  \label{tab:dice}
+\end{table}
+
+A plot of simulated probability of landing on "1" after each iteration.
 

### 2012-07-31 paper.tex
add more figures

@@
 A plot of bounce height after each iteration.
+The height and desired height is plotted in Figure~\ref{fig:ball}
+\begin{figure}
+	\centering
+ 	\includegraphics[width=0.3\textwidth]{figure/ballHeight.pdf}
+\caption{Simulated height per-iteration of a ball bouncing after free-falling at 1 meter height.
+	Redline is desired height.}
+\label{fig:ball}
+\end{figure}
 
-Loaded dice. It has a certain probability to land on "1".
+A loaded die as shown in Figure~\ref{fig:die}. 
+\begin{figure}
+	\centering
+ 	\includegraphics[width=0.25\textwidth]{figure/die.png}
+\caption{A printed loaded die}
+\label{fig:die}
+\end{figure}
+It has a certain probability to land on "1".
 A table of probability distribution of landing on each side

### 2012-08-01 paper.tex
figure for probability of loaded die

@@
         	(d)objet}\label{teaser}
+	\label{fig:texture}
  }
@@
 the desired object. Unfortunately, this search space
-is usually high-dimensional. For example, when the printing
+is usually intractable. For example, when the printing
 volume has N voxels and each of these voxels can be
 assigned to one of M base materials, the search space
-has $N^M$ dimensions. To overcome this problem, we decompose the search
+contains $N^M$ choices. To overcome this problem, we decompose the search
 space into similar subproblems and also reduce
@@
 example, by defining structures of base materials and rules how different base materials can be combined together.
+In this paper, all reduction models are manually specified by us.
 The second way to specify a reduction model is implicit. In this case, the user provides a set of examples of
@@
 existing standard optimization techniques
-such as simulated annealing, genetic algorithms and
-Markov Chain Monte Carlo methods, as well as custom optimization algorithms implemented
+such as simulated annealing, variational inference and
+Markov Chain Monte Carlo methods,
+as well as custom optimization algorithms implemented
 by more advanced users.
@@
 \section{Programming with Our API}
+We provide a built-in library that handles common tasks such as assigning texture,
+simulating deformation, and optimizing for a stacking.
+A casual user mostly make function calls to an existing 
+manager to pass data and to run the optimization.
+More advanced user can configure the manager to achieve more specific requirements.
+For example, he can swap out an existing optimization module to achieve a better accuracy or 
+a faster speed.
+A professional user can implement more modules when he wants to deal with new
+material properties that are not handled by our built-in library. In that case,
+he needs to know what value the new property is in print materials, he needs to know
+how to simulate for the new property, and how to measure error of the new property.
+
+In below, we provide code snippets that handles three common tasks
+that we expect a moderately advanced user would write.
+
 Code examples:
@@
 Subsurface scattering. Mechanical properties
-A figure showing a material with a particular
+A material with a particular
 look and deformation properties is shown in Figure~\ref{fig:deform}
@@
 dithering with our expanded colors.
+Results are shown in Figure~\ref{fig:texture}
 \subsection{New Examples for Mechanical Properties}
@@
 
-A loaded die as shown in Figure~\ref{fig:die}. 
+A loaded die as shown in Figure~\ref{fig:die}. This example is interesting because
+a local change will have some global effect.
 \begin{figure}
@@
 
-A plot of simulated probability of landing on "1" after each iteration.
+A plot of simulated probability of landing on "1" after each iteration
+is shown in Figure~\ref{fig:dieErr}.
+
+\begin{figure}
+	\centering
+ 	\includegraphics[width=0.3\textwidth]{figure/die.pdf}
+\caption{Probability of die landing on 1 after each iteration.}
+\label{fig:dieErr}
+\end{figure}
 
@@
 
+More ideas:
+balancing bird with texture.
 \section{Possible Extension}

### 2012-08-01 paper.tex
API figure placeholder

@@
 \begin{figure}
+\includegraphics[width=0.45\textwidth]{figure/framework.pdf}
 \caption{API overview}
@@
 \subsection{Input API}
+Our input API handles three tasks: specifying an optimization problem,
+maintaining a material library and configuring existing modules of
+the optimization process.
+An overview of the three components of our API is shown in Figure~\ref{fig:inputAPI}
+
+\begin{figure}
+\includegraphics[width=0.45\textwidth]{figure/inputAPI.pdf}
+\caption{Input API overview}
+\label{fig:inputAPI}
+\end{figure}
+
 Our input API allows a designer to either

### 2012-08-01 paper.tex
add built-in component section

@@
 \usepackage[english]{babel}
-\title{Goes Here}
+\title{Spec2Fab: A  High-Fidelity Mapping from Specification to Fabrication}
 
@@
 the material structure. These markers can be tracked in 3D using a multi-camera system.
+\subsection{Optimization for Fabrication}
+Caustics, shadowpix, balloon
 \section{System Description}
@@
 \includegraphics[width=0.45\textwidth]{figure/framework.pdf}
-\caption{API overview}
+\caption{API overview. The diagram will become nicer.}
 \label{fig:framework}
@@
 \includegraphics[width=0.45\textwidth]{figure/inputAPI.pdf}
-\caption{Input API overview}
+\caption{Input API. The diagram will become nicer.}
 \label{fig:inputAPI}
@@
 these measurements to estimate the parameters of data-driven material models (e.g., for elasticity, reflectance).
-\section{Programming with Our API}
+
+\section{Built-in Components}
 We provide a built-in library that handles common tasks such as assigning texture,
 simulating deformation, and optimizing for a stacking.
+\subsection{Generator}
+\begin{enumerate}
+\item A generator that uses a uniform grids with homogeneous
+material in each grid cell. (A foam structure is treated as one homogeneous material).
+\item A generator that decomposes a mesh into columns of stackings where each
+column can be addressed separately by Generator::chooseSection.
+This is useful for problems where local changes don't global effects such as
+matching texture, matching mechanical properties of each column.
+\item A polynomial spline representation for modifying the surface mesh.
+\item A polynomial spline for height field of internal material layers (does not modify
+surface mesh).
+\end{enumerate}
+
+\subsection{Simulator}
+\begin{enumerate}
+\item Physics simulator with FEM, rigid body simulation
+and simple collision resolution.
+\item nVidia optiX to do photon mapping for caustics. Maybe also BRDF and shadows.
+We need to look at its speed.
+\item local computations such as reflectance and local mechanical properties given a stacking.
+\end{enumerate}
+
+\subsection{Metric}
+Optionally returns a gradient represented as an array of signed floats.
+\begin{enumerate}
+\item Compare a mesh and its deformed state. There is one-to-one correspondence of 
+vertices.
+\item compare two images
+\item compare two real numbers such as weight and bouncing height.
+\end{enumerate}
+
+\subsection{Optimizer}
+\begin{enumerate}
+\item MCMC, Simulated Anealing, SPSA
+\item Branch and bound (plus clustering of similar configurations)
+\item (Optional) reinforcement learning, deep neural networks...
+\end{enumerate}
+
+\section{Programming with Our API}
 A casual user mostly make function calls to an existing 

### 2012-08-01 paper.tex
need more citation

@@
 
-To generate BRDF
+To optimize BRDF for a particular camera view point and lighting.
 \begin{verbatim}
+scene.setCamera(camera);
+scene.addLight(light);
 manager.setGenerator(stackingGenerator);
@@
 
-Deformation
+Defining elasticity properties
+by specifying deformation 
+reaction to a force applied to a point.
+
 \begin{verbatim}
@@
 \section{Experiments}
+\section{Print Material Characterization and Measurement}
+
 \subsection{Previous Work}

### 2012-08-01 paper.tex
Add more citations

@@
 \subsection{Optimization for Fabrication}
-Caustics, shadowpix, balloon
+\cite{Finckh:2010} computing surface height field
+of transparent material to match caustics pattern.
+ShadowPix \cite{Bermano:2012} produced surface geometry
+that produces different images 
+under different lighting
+directions. \cite{sko:2012} produced balloons that match 3D models when
+inflated.
 \section{System Description}

### 2012-08-02 paper.tex
castics example

@@
 \section{Experiments}
-\section{Print Material Characterization and Measurement}
+\subsection{Print Material Characterization and Measurement}
 
-\subsection{Previous Work}
-Subsurface scattering. Mechanical properties
-A material with a particular
-look and deformation properties is shown in Figure~\ref{fig:deform}
+\subsection{Subsurface Scattering, Deformation and Mass}
+Combining previous work on replicating
+subsurface scattering and deformation behavior, 
+we produced
+material with a particular
+look and deformation properties as shown in Figure~\ref{fig:deform}.
+We als considered one additional property:mass. In this example, we
+tried to make the material as light as possible.
+\section{Caustics for a Mesh}
+We demonstrate how to produce a 3D model with specific caustic shape under a particular lighting,
+similar to \cite{Finckh:2010}. The difference is that we optimize on an arbitrary 3D model,
+and we use a generic rendering package (NVidia optiX). Our algorithm took 6 hours to finish
+with $4000$ spline control points for the model and $600\times 600$ resolution for the caustic image. A 
+picture of our printed result under desired lighting is shown in Figure~\ref{fig:caustic}.
 

### 2012-10-08 paper.tex
add caustic image
add figure for composing generators

@@
 assigned to one of M base materials, the search space
-contains $N^M$ choices. To overcome this problem, we decompose the search
+contains $N^M$ choices. 
+To overcome this problem, we decompose the search
 space into similar subproblems and also reduce
-the search space to a lower-dimensional space using
-a reduction model. The goal of the reduction step is to
+the search space to a lower-dimensional space using a reduction model. 
+The goal of the reduction step is to
 shrink the search space as much as possible but at the
@@
 \subsection{Generator}
+Generator uses a reduced representation
+of material assignments.
+Each generator is defined over a domain in the input shape.
+We provide a few basic generators and a composition operator.
+Let the input shape be over a domain $\Omega$.
+The composition of two generators $G_2\circ G_1$ is implemented by
+first letting $G_1$ reduce over a domain $\Omega_1$ and
+then letting $G_2$ reduce $\Omega_2 = \Omega-\Omega_1$.
+An example is shown in Figure~\ref{fig:genCompose}
+\begin{figure}[h]
+\includegraphics[scale=0.2]{figure/genCompose.png}
+\caption{Composition of two generators. $G_1$ is a fine-grained
+surface voxelization and $G_2$ is a very coarse inner
+grid.}
+\label{fig:genCompose}
+\end{figure}
 \begin{enumerate}
@@
 tried to make the material as light as possible.
-\section{Caustics for a Mesh}
-We demonstrate how to produce a 3D model with specific caustic shape under a particular lighting,
-similar to \cite{Finckh:2010}. The difference is that we optimize on an arbitrary 3D model,
-and we use a generic rendering package (NVidia optiX). Our algorithm took 6 hours to finish
-with $4000$ spline control points for the model and $600\times 600$ resolution for the caustic image. A 
-picture of our printed result under desired lighting is shown in Figure~\ref{fig:caustic}.
-
 \begin{figure}
@@
 \label{fig:err}
+\end{figure}
+
+\section{Caustics for a Mesh}
+We demonstrate how to produce a 3D model with specific caustic shape under a particular lighting,
+similar to \cite{Finckh:2010}. The difference is that we optimize on an arbitrary 3D model,
+and we use a generic rendering package (NVidia optiX). Our algorithm took 6 hours to finish
+with $4000$ spline control points for the model and $600\times 600$ resolution for the caustic image. A 
+picture of our printed result under desired lighting is shown in Figure~\ref{fig:caustic}.
+
+\begin{figure}
+	\centering
+ 	\includegraphics[width=0.3\textwidth]{figure/caustic.jpg}
+\caption{Teapot with a caustic image.}
+\label{fig:caustic}
 \end{figure}

### 2012-10-08 paper.tex
in each experiment , what generators to use

@@
 \end{figure}
+
+We will provide the following generators.
 \begin{enumerate}
@@
 material in each grid cell. (A foam structure is treated as one homogeneous material).
-\item A generator that decomposes a mesh into columns of stackings where each
-column can be addressed separately by Generator::chooseSection.
-This is useful for problems where local changes don't global effects such as
-matching texture, matching mechanical properties of each column.
-\item A polynomial spline representation for modifying the surface mesh.
-\item A polynomial spline for height field of internal material layers (does not modify
-surface mesh).
+\item A generator that decomposes a mesh into columns of stackings.
+\item A polynomial spline for outline of a material.
 \end{enumerate}
-
+We use composition of the above basic generators to make the examples in 
+the result section.
 \subsection{Simulator}
@@
 \section{Experiments}
+We used various generators in our experiments.
 \subsection{Print Material Characterization and Measurement}
-
 \subsection{Subsurface Scattering, Deformation and Mass}
@@
 look and deformation properties as shown in Figure~\ref{fig:deform}.
-We als considered one additional property:mass. In this example, we
+We als considered one additional property:mass. 
+In this example, we
 tried to make the material as light as possible.
+
+We tried different combinations of generators in this experiment.
+We compared the performance of these different generator
+in terms of run-time and error.
+\begin{enumerate}
+\item Spline for top layer, fine-grained voxelization for mid layer
+and a coarse grid for bottom layer.
+\item Voxels for top layer, splines for middle layer and a coarse
+bottom layer.
+\item Find-grained voxels for top layer and coarse grid for bottom layer.
+\end{enumerate}
+
 \begin{figure}
@@
 
-\section{Caustics for a Mesh}
+\subsection{Caustics for a Mesh}
 We demonstrate how to produce a 3D model with specific caustic shape under a particular lighting,
 similar to \cite{Finckh:2010}. The difference is that we optimize on an arbitrary 3D model,
-and we use a generic rendering package (NVidia optiX). Our algorithm took 6 hours to finish
+and we use a generic rendering package (NVidia optiX). 
+We represented the surface with a spline surface.
+Our algorithm took 6 hours to finish
 with $4000$ spline control points for the model and $600\times 600$ resolution for the caustic image. A 
@@
 
-We expand gamut of printable colors by stacking translucent materials. We then applied
+When printing texture, only the outer layer matters. We used 
+a composition of two generators: a very high resolution grid
+for the outer layer and a uniform material for the inside.
+
+We expand the set of printable colors by stacking translucent materials. We then applied
 dithering with our expanded colors.
@@
 \subsection{New Examples for Mechanical Properties}
-Ball bounce to certain height.
+Ball bounce to certain height. We used a higher resolution
+grid for the out layer and very low resolution
+for the inner mesh.
 
@@
 a local change will have some global effect.
+We used very high resolution grid for the surface to match texture
+of a die. The inner lay has only $3\times 3$ resolution.
 \begin{figure}

### 2012-12-20 paper.tex
edits part 1

@@
 \usepackage[english]{babel}
-\title{Spec2Fab: A  High-Fidelity Mapping from Specification to Fabrication}
+\title{Spec2Fab: A  Graph-Based Framework for Fabricating Fabrication Algorithms}
 
@@
 \keywords{}
+
+\newcommand{\note}[1]{\marginpar{\LARGE $\spadesuit$}
+			$\spadesuit$ {\bf #1} $\spadesuit$}
 
@@
 
+\note{Teaser should be all different results produced using spec2Fab, texture, subsurface scattering, caustics etc...}
+
 \section{Introduction}
-3D printing has the potential to dramatically reduce the required time and cost of
-fabricating custom materials and objects. In particular, it allows the fabrication of materials with complex internal
-structures that are difficult or impossible to manufacture with other technologies. Additive manufacturing could be
-much more widely adopted and easier to use, given a high-fidelity translation from specifications of objects defined
-in terms of their mechanical, optical, and appearance properties to output-device-specific computer
-programs that produce the best possible approximation of these digital objects. However, this is still one of
-the most important unsolved problems in digital direct manufacturing. Due to its combinatorial nature, this
-problem becomes more and more challenging as the range of different printable materials increases. This paper
-aims to provide an abstraction mechanism and a software framework for translating specifications to fabrication
-instructions. It is possible to design a computationally efficient and general process for translating virtual objects
-with desired mechanical, electrical, optical, and appearance properties into composite printable materials.
-We will achieve this goal through a reduction-optimization-simulation approach.
+Computational fabrication couples new digital manufacturing techniques with novel numerical algorithms to produce objects with remarkable physical characteristics.
+These methods are of great interest in computer graphics for two reasons: First, they provide us with  new class of output devices which can render into  real-life and second, they yield valuable insight into the accuracy of our numerical models of the world.
+
+In this paper we focus on a fundamental problem in producing any such custom object:  optimal material assignment.
+Given an object one must find a spatially varying material distribution that satisfies some given criteria.
+The algorithms that solve these problems are often complicated to develop, implement, test and modify.
+We provide a new graph-based framework which decomposes such problems into a small set of constituent components alleviating the above issues as well as facilitating the development and testing of novel algorithms.
+
 \section{Previous Work}
@@
 inflated.
-\section{System Description}
-The software framework (shown in Figure~\ref{fig:framework}) is composed of 
-a set of software
-modules that can be easily modified or exchanged. The first component
-of this framework is an output-device-independent description API
-that allows the user to specify any physical object in terms of its physical
-properties such as geometry, mechanical behaviors, and appearance. 
-The framework will also provide physically-based
-simulation tools that accurately predict the behavior of our output device.
-The goal of the optimization module is to search through
-the space of possible device outputs and deliver one that best matches the
-desired model. In order to evaluate the quality of the match between the
-simulation output and the desired model we need to develop appropriate
-comparison metrics. Finally, a central component of our framework is
-a reduction model which makes the optimization problem tractable by
-reducing the search space as much as possible.
-The reduction model can specified by experts or deduced from a
-set of examples. Next, we will describe each element of the framework in
-more detail.
-\begin{figure}
-\includegraphics[width=0.45\textwidth]{figure/framework.pdf}
-\caption{API overview. The diagram will become nicer.}
-\label{fig:framework}
-\end{figure}
-\subsection{Input API}
-Our input API handles three tasks: specifying an optimization problem,
-maintaining a material library and configuring existing modules of
-the optimization process.
-An overview of the three components of our API is shown in Figure~\ref{fig:inputAPI}
+\subsection{Shade Trees}
+\note{Should talk about influences from Shade Trees and Shader networks, note that these methods do not have tunable parameters}
+\section{Contributions}
+The overall contribution of our work is a flexible framework for the construction of material assignment algorithms.
+Our second contribution is the ``Reducer Network'',  a graphical data structure which describes both the geometric partitioning and material parameterization of  a given object.
+We couple this with a ``Tuner Network'' which automatically tunes the parameters of the Reducer Network to produce a fabricable object.
+Finally we will describe our API which utilizes these structures to produce numerous material assignment algorithms from a set of primitive operations.
+\section{Methods}
+Below we will describe the key components of our framework and its associated API. 
+\subsection{The Reducer Network}
+Computing material assignments at output device resolution is computationally intractable.
+Because of this, material assignments are computed  using a reduced representation.
+We specify this representation using a Reducer Network.
+This structure is conceptually similar to those used in programmable shading systems (e.g.
+~\cite{Cook1984}, Maya Shader Networks) .
+However these systems are primarily concerned with assigning known materials and textures to an object's surface whereas we are seeking a volumetric assignment of (as yet) unknown materials.
+In order to accomplish this task we build a directed, acyclic graph which has the object's surface geometry as its root node.
+We define two classes of nodes, geometry nodes and parameterization nodes.
+A geometry nodes takes a volumetric region as input and produces a partition of unity of this region as output.
+The leaf nodes of our graph are the parameterization nodes which associate a material assignment function of the form $\lambda\left(x,y,z,\theta\right)$ to an input volumetric region.
+Lambda can either output material parameters or a discrete material assignment for a spatial point $\left(x,y,z\right)$ given some parameters, here denoted by $\theta$.
+Because the network describes a nested set of partitions of unity we can efficiently perform material queries by passing a query point through the network until it arrives at a parameterization node.
+We note that Reducer Networks do not inherently enforce material continuity between disjoint regions in the graph however, for material assignment problems this is not required.
 
-\begin{figure}
-\includegraphics[width=0.45\textwidth]{figure/inputAPI.pdf}
-\caption{Input API. The diagram will become nicer.}
-\label{fig:inputAPI}
-\end{figure}
+ See \textbf{Figure 1} for an example of a Reducer Network. \note{Desai: Make figure 1}.
 
-Our input API allows a designer to either
-define material properties for sections of an object
-or specify behavior of an object.
-The designer
-can use functions to describe properties such as reflectance (e.g., BRDFs, BSSRDFs), 
-stiffness, or other spatially varying properties. 
-Although it is possible to define the object directly by only specifying material
-properties, intuitive user
-interfaces will aid in specifying the objects and their properties
-in terms of intuitive metaphors.
-For example, the elastic properties of an object can be specified by a set of
-example displacements from the rest pose and the corresponding applied forces.
-\subsection{Search Space Decomposition and Reduction}
-Our framework includes an optimization component that
-searches through the space of possible device inputs
-to find the one that best reproduces
-the desired object. Unfortunately, this search space
-is usually intractable. For example, when the printing
-volume has N voxels and each of these voxels can be
-assigned to one of M base materials, the search space
-contains $N^M$ choices. 
-To overcome this problem, we decompose the search
-space into similar subproblems and also reduce
-the search space to a lower-dimensional space using a reduction model. 
-The goal of the reduction step is to
-shrink the search space as much as possible but at the
-same time not to prune out good solutions. The low-dimensional space produced by the
-reducer can be defined in two different ways. First, a reduction model can be explicitly specified by an expert, for
-example, by defining structures of base materials and rules how different base materials can be combined together.
-In this paper, all reduction models are manually specified by us.
-The second way to specify a reduction model is implicit. In this case, the user provides a set of examples of
-valid material structures. Then, a machine learning algorithm infers both basic material structures and the rules
-for combining them. The optimization framework can be further improved by employing techniques that cluster
-partial solutions that yield similar output properties, avoiding combinatorial explosion of the search space.
-Furthermore, we can employ bounds on the solution based on physical constraints of the base materials.
-\subsection{Optimization}
-Our optimization component is an interface to
-existing standard optimization techniques
-such as simulated annealing, variational inference and
-Markov Chain Monte Carlo methods,
-as well as custom optimization algorithms implemented
-by more advanced users.
-\subsection{Simulation}
-Another key step in the process of converting abstractions to physical output is being able to
-simulate what an output device is going to generate given a well-defined input. 
-A simulation allows the user to preview how the output will look and behave. 
-This simulation is a generalization of the print-preview function
-available in word processing applications.
-As physical output generation might be costly or time-consuming, 
-it is extremely beneficial for users to be able to preview the output and make immediate changes to the design.
-That means that the simulation must accurately predict the output. 
-It's necessary to develop very efficient and accurate rendering
-and finite element simulation packages. Since we run the simulation multiple times within the optimization method
-we can cache and reuse partial simulation results, speeding up the evaluation process at least 10-100 times.
-Furthermore, we will ensure that the simulation is accurate by measuring properties of the printing materials and using
-these measurements to estimate the parameters of data-driven material models (e.g., for elasticity, reflectance).
+\subsection{Tuners}
+\note{Desai: can you write this section, I don't know the details}
+\subsection{Tuning the Reducer Network}
 
-\section{Built-in Components}
-We provide a built-in library that handles common tasks such as assigning texture,
-simulating deformation, and optimizing for a stacking.
-\subsection{Generator}
-Generator uses a reduced representation
-of material assignments.
-Each generator is defined over a domain in the input shape.
-We provide a few basic generators and a composition operator.
-Let the input shape be over a domain $\Omega$.
-The composition of two generators $G_2\circ G_1$ is implemented by
-first letting $G_1$ reduce over a domain $\Omega_1$ and
-then letting $G_2$ reduce $\Omega_2 = \Omega-\Omega_1$.
-An example is shown in Figure~\ref{fig:genCompose}
-\begin{figure}[h]
-\includegraphics[scale=0.2]{figure/genCompose.png}
-\caption{Composition of two generators. $G_1$ is a fine-grained
-surface voxelization and $G_2$ is a very coarse inner
-grid.}
-\label{fig:genCompose}
-\end{figure}
+\subsection{Tuner Network}
+\note{Desai: also this section :) }
+%\section{System Description}
+%The software framework (shown in Figure~\ref{fig:framework}) is composed of 
+%a set of software
+%modules that can be easily modified or exchanged. The first component
+%of this framework is an output-device-independent description API
+%that allows the user to specify any physical object in terms of its physical
+%properties such as geometry, mechanical behaviors, and appearance. 
+%The framework will also provide physically-based
+%simulation tools that accurately predict the behavior of our output device.
+%The goal of the optimization module is to search through
+%the space of possible device outputs and deliver one that best matches the
+%desired model. In order to evaluate the quality of the match between the
+%simulation output and the desired model we need to develop appropriate
+%comparison metrics. Finally, a central component of our framework is
+%a reduction model which makes the optimization problem tractable by
+%reducing the search space as much as possible.
+%The reduction model can specified by experts or deduced from a
+%set of examples. Next, we will describe each element of the framework in
+%more detail.
+%\begin{figure}
+%\includegraphics[width=0.45\textwidth]{figure/framework.pdf}
+%\caption{API overview. The diagram will become nicer.}
+%\label{fig:framework}
+%\end{figure}
+%\subsection{Input API}
+%Our input API handles three tasks: specifying an optimization problem,
+%maintaining a material library and configuring existing modules of
+%the optimization process.
+%An overview of the three components of our API is shown in Figure~\ref{fig:inputAPI}
+%
+%\begin{figure}
+%\includegraphics[width=0.45\textwidth]{figure/inputAPI.pdf}
+%\caption{Input API. The diagram will become nicer.}
+%\label{fig:inputAPI}
+%\end{figure}
+%
+%Our input API allows a designer to either
+%define material properties for sections of an object
+%or specify behavior of an object.
+%The designer
+%can use functions to describe properties such as reflectance (e.g., BRDFs, BSSRDFs), 
+%stiffness, or other spatially varying properties. 
+%Although it is possible to define the object directly by only specifying material
+%properties, intuitive user
+%interfaces will aid in specifying the objects and their properties
+%in terms of intuitive metaphors.
+%For example, the elastic properties of an object can be specified by a set of
+%example displacements from the rest pose and the corresponding applied forces.
+%\subsection{Search Space Decomposition and Reduction}
+%Our framework includes an optimization component that
+%searches through the space of possible device inputs
+%to find the one that best reproduces
+%the desired object. Unfortunately, this search space
+%is usually intractable. For example, when the printing
+%volume has N voxels and each of these voxels can be
+%assigned to one of M base materials, the search space
+%contains $N^M$ choices. 
+%To overcome this problem, we decompose the search
+%space into similar subproblems and also reduce
+%the search space to a lower-dimensional space using a reduction model. 
+%The goal of the reduction step is to
+%shrink the search space as much as possible but at the
+%same time not to prune out good solutions. The low-dimensional space produced by the
+%reducer can be defined in two different ways. First, a reduction model can be explicitly specified by an expert, for
+%example, by defining structures of base materials and rules how different base materials can be combined together.
+%In this paper, all reduction models are manually specified by us.
+%The second way to specify a reduction model is implicit. In this case, the user provides a set of examples of
+%valid material structures. Then, a machine learning algorithm infers both basic material structures and the rules
+%for combining them. The optimization framework can be further improved by employing techniques that cluster
+%partial solutions that yield similar output properties, avoiding combinatorial explosion of the search space.
+%Furthermore, we can employ bounds on the solution based on physical constraints of the base materials.
+%\subsection{Optimization}
+%Our optimization component is an interface to
+%existing standard optimization techniques
+%such as simulated annealing, variational inference and
+%Markov Chain Monte Carlo methods,
+%as well as custom optimization algorithms implemented
+%by more advanced users.
+%\subsection{Simulation}
+%Another key step in the process of converting abstractions to physical output is being able to
+%simulate what an output device is going to generate given a well-defined input. 
+%A simulation allows the user to preview how the output will look and behave. 
+%This simulation is a generalization of the print-preview function
+%available in word processing applications.
+%As physical output generation might be costly or time-consuming, 
+%it is extremely beneficial for users to be able to preview the output and make immediate changes to the design.
+%That means that the simulation must accurately predict the output. 
+%It's necessary to develop very efficient and accurate rendering
+%and finite element simulation packages. Since we run the simulation multiple times within the optimization method
+%we can cache and reuse partial simulation results, speeding up the evaluation process at least 10-100 times.
+%Furthermore, we will ensure that the simulation is accurate by measuring properties of the printing materials and using
+%these measurements to estimate the parameters of data-driven material models (e.g., for elasticity, reflectance).
+%
+%\section{Built-in Components}
+%We provide a built-in library that handles common tasks such as assigning texture,
+%simulating deformation, and optimizing for a stacking.
+%\subsection{Generator}
+%Generator uses a reduced representation
+%of material assignments.
+%Each generator is defined over a domain in the input shape.
+%We provide a few basic generators and a composition operator.
+%Let the input shape be over a domain $\Omega$.
+%The composition of two generators $G_2\circ G_1$ is implemented by
+%first letting $G_1$ reduce over a domain $\Omega_1$ and
+%then letting $G_2$ reduce $\Omega_2 = \Omega-\Omega_1$.
+%An example is shown in Figure~\ref{fig:genCompose}
+%\begin{figure}[h]
+%\includegraphics[scale=0.2]{figure/genCompose.png}
+%\caption{Composition of two generators. $G_1$ is a fine-grained
+%surface voxelization and $G_2$ is a very coarse inner
+%grid.}
+%\label{fig:genCompose}
+%\end{figure}
+%
+%We will provide the following generators.
+%\begin{enumerate}
+%\item A generator that uses a uniform grids with homogeneous
+%material in each grid cell. (A foam structure is treated as one homogeneous material).
+%\item A generator that decomposes a mesh into columns of stackings.
+%\item A polynomial spline for outline of a material.
+%\end{enumerate}
+%We use composition of the above basic generators to make the examples in 
+%the result section.
+%\subsection{Simulator}
+%\begin{enumerate}
+%\item Physics simulator with FEM, rigid body simulation
+%and simple collision resolution.
+%\item nVidia optiX to do photon mapping for caustics. Maybe also BRDF and shadows.
+%We need to look at its speed.
+%\item local computations such as reflectance and local mechanical properties given a stacking.
+%\end{enumerate}
+%
+%\subsection{Metric}
+%Optionally returns a gradient represented as an array of signed floats.
+%\begin{enumerate}
+%\item Compare a mesh and its deformed state. There is one-to-one correspondence of 
+%vertices.
+%\item compare two images
+%\item compare two real numbers such as weight and bouncing height.
+%\end{enumerate}
+%
+%\subsection{Optimizer}
+%\begin{enumerate}
+%\item MCMC, Simulated Anealing, SPSA
+%\item Branch and bound (plus clustering of similar configurations)
+%\item (Optional) reinforcement learning, deep neural networks...
+%\end{enumerate}
+%
+%\section{Programming with Our API}
+%A casual user mostly make function calls to an existing 
+%manager to pass data and to run the optimization.
+%More advanced user can configure the manager to achieve more specific requirements.
+%For example, he can swap out an existing optimization module to achieve a better accuracy or 
+%a faster speed.
+%A professional user can implement more modules when he wants to deal with new
+%material properties that are not handled by our built-in library. In that case,
+%he needs to know what value the new property is in print materials, he needs to know
+%how to simulate for the new property, and how to measure error of the new property.
+%
+%In below, we provide code snippets that handles three common tasks
+%that we expect a moderately advanced user would write.
+%
+%Code examples:
+%To generate textured model:
+%\begin{verbatim}
+%Manager manager;
+%manager.loadMaterialLib("material_file");
+%manager.setGenerator(
+%  new HeightFieldGenerator());
+%manager.setSimulator(colorSimulator());
+%manager.setMetric(someColorMetric());
+%manager.setOptimizer(
+%  simulatedAnealing);
+%  //or e.g. gradientDescent
+%Objective obj;
+%Scene scene;
+%TexturedShape shape("filename");
+%TexturedShape goal("filename1");
+%scene.addShape(shape);
+%obj.setScene(scene);
+%obj.setGoal(goal);
+%manager.addObjective(obj);
+%\end{verbatim}
+%
+%To optimize BRDF for a particular camera view point and lighting.
+%\begin{verbatim}
+%scene.setCamera(camera);
+%scene.addLight(light);
+%manager.setGenerator(stackingGenerator);
+%manager.setSimulator(brdfSimulator);
+%manager.setMetric(someImageMetric);
+%Shape shape("filename"), 
+%Image goal("filename1");
+%\end{verbatim}
+%
+%Defining elasticity properties
+%by specifying deformation 
+%reaction to a force applied to a point.
+%
+%\begin{verbatim}
+%force = new Force(pos, dir, shapeID);
+%constraint = new Constraint(
+%    FIX_VERTEX, vertexList, shapeID));
+%
+%scene.addForce(force);
+%scene.addConstraint(constraint);
+%Shape goal;
+%manager.setSimulator(femSimulator);
+%\end{verbatim}
 
-We will provide the following generators.
-\begin{enumerate}
-\item A generator that uses a uniform grids with homogeneous
-material in each grid cell. (A foam structure is treated as one homogeneous material).
-\item A generator that decomposes a mesh into columns of stackings.
-\item A polynomial spline for outline of a material.
-\end{enumerate}
-We use composition of the above basic generators to make the examples in 
-the result section.
-\subsection{Simulator}
-\begin{enumerate}
-\item Physics simulator with FEM, rigid body simulation
-and simple collision resolution.
-\item nVidia optiX to do photon mapping for caustics. Maybe also BRDF and shadows.
-We need to look at its speed.
-\item local computations such as reflectance and local mechanical properties given a stacking.
-\end{enumerate}
-
-\subsection{Metric}
-Optionally returns a gradient represented as an array of signed floats.
-\begin{enumerate}
-\item Compare a mesh and its deformed state. There is one-to-one correspondence of 
-vertices.
-\item compare two images
-\item compare two real numbers such as weight and bouncing height.
-\end{enumerate}
-
-\subsection{Optimizer}
-\begin{enumerate}
-\item MCMC, Simulated Anealing, SPSA
-\item Branch and bound (plus clustering of similar configurations)
-\item (Optional) reinforcement learning, deep neural networks...
-\end{enumerate}
-
-\section{Programming with Our API}
-A casual user mostly make function calls to an existing 
-manager to pass data and to run the optimization.
-More advanced user can configure the manager to achieve more specific requirements.
-For example, he can swap out an existing optimization module to achieve a better accuracy or 
-a faster speed.
-A professional user can implement more modules when he wants to deal with new
-material properties that are not handled by our built-in library. In that case,
-he needs to know what value the new property is in print materials, he needs to know
-how to simulate for the new property, and how to measure error of the new property.
-
-In below, we provide code snippets that handles three common tasks
-that we expect a moderately advanced user would write.
-
-Code examples:
-To generate textured model:
-\begin{verbatim}
-Manager manager;
-manager.loadMaterialLib("material_file");
-manager.setGenerator(
-  new HeightFieldGenerator());
-manager.setSimulator(colorSimulator());
-manager.setMetric(someColorMetric());
-manager.setOptimizer(
-  simulatedAnealing);
-  //or e.g. gradientDescent
-Objective obj;
-Scene scene;
-TexturedShape shape("filename");
-TexturedShape goal("filename1");
-scene.addShape(shape);
-obj.setScene(scene);
-obj.setGoal(goal);
-manager.addObjective(obj);
-\end{verbatim}
-
-To optimize BRDF for a particular camera view point and lighting.
-\begin{verbatim}
-scene.setCamera(camera);
-scene.addLight(light);
-manager.setGenerator(stackingGenerator);
-manager.setSimulator(brdfSimulator);
-manager.setMetric(someImageMetric);
-Shape shape("filename"), 
-Image goal("filename1");
-\end{verbatim}
-
-Defining elasticity properties
-by specifying deformation 
-reaction to a force applied to a point.
-
-\begin{verbatim}
-force = new Force(pos, dir, shapeID);
-constraint = new Constraint(
-    FIX_VERTEX, vertexList, shapeID));
-
-scene.addForce(force);
-scene.addConstraint(constraint);
-Shape goal;
-manager.setSimulator(femSimulator);
-\end{verbatim}
-
-\section{Experiments}
+\section{Results}
 We used various generators in our experiments.

### 2012-12-20 paper.tex
Fixed some typos

@@
 The algorithms that solve these problems are often complicated to develop, implement, test and modify.
-We provide a new graph-based framework which decomposes such problems into a small set of constituent components alleviating the above issues as well as facilitating the development and testing of novel algorithms.
+We provide a new graph-based framework which decomposes such problems into a small set of constituent components alleviating the above issues as well as facilitating the development and testing of new algorithms.
 
@@
 We define two classes of nodes, geometry nodes and parameterization nodes.
-A geometry nodes takes a volumetric region as input and produces a partition of unity of this region as output.
+A geometry node takes a volumetric region as input and produces a partition of unity of this region as output.
 The leaf nodes of our graph are the parameterization nodes which associate a material assignment function of the form $\lambda\left(x,y,z,\theta\right)$ to an input volumetric region.
@@
 Because the network describes a nested set of partitions of unity we can efficiently perform material queries by passing a query point through the network until it arrives at a parameterization node.
-We note that Reducer Networks do not inherently enforce material continuity between disjoint regions in the graph however, for material assignment problems this is not required.
+We note that Reducer Networks do not inherently enforce material continuity between disjoint regions in the graph however, for material assignment problems this is neither required nor desired.
 

### 2012-12-20 paper.tex
digram

--- 2012-10-08 paper.tex
@@
 \end{enumerate}
-
+\subsection{Mapper and Reducer}
+In some problems such as matching texture colors or local mechanical properties,
+the material assignment decision at one location does not influence
+decisions made at other locations. The free variables of such problems
+are independent of each other. We can express such independency with 
+Mapper and Reducer classes. Mapper takes a problem and decomposes
+it a set of into independent sub-problems. Reducer
+combines solutions to the sub-problems and construct
+a complete solution to the origin problem.
 \section{Programming with Our API}

### 2012-12-20 paper.tex
interrupted

--- 2012-12-20 paper.tex
@@
 \subsection{Tuners}
-\note{Desai: can you write this section, I don't know the details}
-\subsection{Tuning the Reducer Network}
+\note{Desai: can you write this section, I don't know the details.
+
+First pass: write down my ideas conversationally.
+}
+
+Tuners are interfaces between the Reducer Network and generic optimization algorithms.
+A tuner can be attached to a node in the reducer graph.
+When a tuner is attached to a node in the reducer graph, it can tune
+all the free parameters in the subtree rooted at that node.
+\subsection{Tuning a Reducer Node}
+The tuner queries its node for information about the search space such as
+number of free variables, variable types and bounds from the Reducer Network.
+In addition, the tuner will set up call-back functions for error computation.
 
@@
 \note{Desai: also this section :) }
+In many fabrication problems, there are local dependencies between
+different sub-trees. One simplest example is surface texture dithering
+using error-diffusion. To account for such dependencies, we allow
+tuners to share information according to a graph structure.
+If two tuners share an edge, they can share information.
+The network structure is specified by users.
+
 %\section{System Description}

### 2012-12-20 paper.tex
before merge

--- 2012-12-20 paper.tex
@@
 \usepackage[english]{babel}
-\title{Spec2Fab: A  Graph-Based Framework for Fabricating Fabrication Algorithms}
+\usepackage{hyperref}
+\title{Spec2Fab: A  Graph-Based Reduction for Fabricating Fabrication Algorithms}
 
@@
 
-\section{Previous Work}
-\subsection{Simulation of the Appearance of Ink Combinations}
-\cite{Matusik:2009} built a system
-for the measurement of Bidirectional Reflectance Distribution Functions (BRDFs) and were able
-to acquire BRDFs for both single-layer and multi-layer ink printouts (e.g., an ink covered by a
-varnish layer). They then acquired a database of many different combinations of ink layers (up to
-seven layer combinations were considered). However, they did not develop a method to simulate
-the appearance of arbitrary ink layers. They were able to interpolate the appearance by spatially
-multiplexing small tiles of different base combinations. By linearity of light transport, the simulation
-of the combined appearance was reduced to linear combinations of the base BRDFs. 
-simulation method for the appearance of translucent materials \cite{Hasan:2010}. 
-They
-built a measurement system for estimating multiple-scattering in homogeneous material slabs. They
-measured both transmission and refection for a set of base materials used by the OBJET Connex
-multi-material printer. 
-Using these measurements, our simulations framework was able to predict
-diffuse reflections and transmissions in multi-layered translucent objects composed of base material
-layers.
-In the proposed research, we will extend these methods to cover the complete appearance of
-volumetric materials that accounts for both directly reflected light and light scattering within the
-material volume. 
-We will use efficient simulation methods that allows us to simulate the appearance
-of complex structures composed from these base materials. We developed an initial framework for
-simulating behavior of multi-layered materials, where each layer is a homogeneous base material.
-Then we extend this simulation to materials in which each voxel is made of a different measured
-material. Since this general simulation is expensive and requires path-tracing algorithms, we used
-algorithms that are based on fast numerical integration of our low-dimensional representations
-and the use of pre-computation, similar to pre-computed light transport approaches \cite{Sloan:2002}.
-\subsection{Simulation of Deformation Behavior}
-In previous work, the problem
-of modeling and simulating soft materials and their deformation behavior \cite{Bickel:2010,Bickel:2009}.
-In order to accurately model deformation behaviors they built a system that allowed measuring how
-a given material deforms subject to a variety of external forces. 
-The system used an automated
-robot arm to apply desired forces and a vision subsystem to measure corresponding surface deformations.
-We modeled deformation behavior of a material using a stress-strain relationship. Since
-the deformation behavior of many of our materials was non-linear, we developed a model that could
-accurately represent this behavior and that was also easy to fit to the surface measurements. In
-our model, the stress-strain relationship was represented as a collection of linear stress-strain relationships.
-We used a properly chosen function to interpolate between these linear relationships
-and obtain a non-linear model. Using this system and model we could accurately measure material
-deformation of a collection of materials produced by a multi-material printer and fit these observation
-to the stress-strain model. Then, using this material model within a Finite Element Method
-we could accurately simulate behavior of any shape made from a composite of measured materials.
-In the proposed research, we would like to address the shortcomings of our current measurement
-and models. First, our current approach handles only elastic material deformation. We would like to
-extend our current data-driven model to viscoelastic materials. In fact, most real materials exhibit
-this property, which is characterized by hysteresis (or material memory). For these materials, it is
-not possible to predict the behavior of a material only based on the currently applied stress. One also
-has to know the history (or the sequence) of applied stress values to accurately simulate material
-behavior. In order to determine the material model one has to measure the so called hysteresis
-loops in the stress-strain space (as opposed to a single stress-strain curve for elastic materials). The
-hysteresis loop is the result of the damping effect which causes the material to behave differently
-depending whether stress is applied or removed as some of the energy is dissipated within the
-material into heat. Additional advantage of using this material model is that it will allow us to
-handle dynamic material deformations.
-
-In order to measure viscoelastic material properties, we will need to modify our current measurement
-system and procedures. We will use repeatable, time-coded measurements to estimate
-Figure 5: From left to right: Force-and-deformation capture of a non-linear heterogeneous pillow;
-synthesized deformation with fitted material parameters; and interactive deformation synthesized
-with our soft tissue modeling technique using scattered data interpolation \cite{Bickel:2010}.
-
-We will also use faster resonating actuators and high-speed
-camera systems to track material deformations at high frame rates. Furthermore, we plan to track
-the whole material volume rather than the outer material surface. This is possible since we can
-print materials in clear color as well. Thus small color-coded markers can be easily embedded into
-the material structure. These markers can be tracked in 3D using a multi-camera system.
-\subsection{Optimization for Fabrication}
-\cite{Finckh:2010} computing surface height field
-of transparent material to match caustics pattern.
-ShadowPix \cite{Bermano:2012} produced surface geometry
-that produces different images 
-under different lighting
-directions. \cite{sko:2012} produced balloons that match 3D models when
-inflated.
-\subsection{Shade Trees}
-\note{Should talk about influences from Shade Trees and Shader networks, note that these methods do not have tunable parameters}
+\section{Related Work} 
+Here we will review previous algorithms for solving the optimal material assignment problem .
+We divide this review into two broad categories, optimizing for desired optical properties and optimizing for desired mechanical properties.
+Finally we will briefly review work done on modular shader languages as they have influenced our current work.
+\subsection{Material Assignment for Desired Optical Properties}
+Optimizing and manufacturing objects with desired optical characteristics is a popular problem in computer graphics.
+Building objects which embed image in their caustics has been explored by Finch \textit{et al.} ~\shortcite{Finckh:2010} and Papas \textit{et al.}\shortcite{Marios:2011}.
+Optimization based approaches have also been employed to control the subsurface scattering of printed 3D models ~\cite{Hasan:2010}.
+These approaches have also been extended to optically decrypt hidden images ~\cite{Papas:2012}.
+Finally, optimal shadow casting surfaces have been produced which emulate a given set of input images ~\cite{Bermano:2012}.
+\subsection{Material Assignment for Desired Mechanical Properties}
+Fabricating objects with desire deformation characteristics has been explored less in the literature.
+Some recent examples include simulating and manufacturing layered composites ~\cite{Bickel:2010} as well as the design and construction of balloons with a desired shape while inflated ~\cite{sko:2012}.
+Finally, material optimization has been employed to create mechanical clones of human faces ~\cite{Bickel:2012}.
+\subsection{Similarities between Methods}
+\autoref{tb:algorithms} shows the coordinate reduction method as well as the optimization scheme used in all cited works.
+A motivating observation for this research is that, despite different applications, these previous works share, not only a common methodology, but rely on a small set of common components to achieve their goals.
+Thus one could hope to find a small set of components that can be tied together to synthesize existing and new methods.
+Similar approaches have already proven useful for creating complex texture shading examples ~\cite{Cook1984}.
+Our goal in this paper is to produce an analogous mechanism for material assignment problems.
+\begin{table*}[htp]
+\centering
+\caption{The goal type, reduction type and optimization used by previous fabrication works.}
+\begin{tabular}{clll}
+\hline
+\textbf{Paper} & \textbf{Goal} & \textbf{Reduced Coordinates}  & \textbf{Optimization} \\ 
+\hline
+~\cite{Bickel:2010}& Deformation & Layered Materials  & Branch and Bound \\
+~\cite{Finckh:2010} & Optical (Caustics) & B-Spline Surface & ??? \\
+~\cite{Hasan:2010}& Optical (Subsurface) & Layered Materials & Branch and Bound\\ 
+~\cite{Marios:2011} & Optical (Caustics) & Quadratic Surface Tiles & Simulated Annealing \\
+~\cite{Bermano:2012} & Optical (Shadows) & Height Field & Custom/Simulated Annealing \\
+~\cite{Bickel:2012} & Deformation &  Height Field &  Newton-Raphson \\
+~\cite{Papas:2012} & Optical & Quadratic Surface Tiles & Simulated Annealing \\
+~\cite{sko:2012}& Deformation & Triangle Mesh & ALM \\
+\hline
+\end{tabular}
+\label{tb:algorithms}
+\end{table*}
+%\subsection{Simulation of the Appearance of Ink Combinations}
+%\cite{Matusik:2009} built a system
+%for the measurement of Bidirectional Reflectance Distribution Functions (BRDFs) and were able
+%to acquire BRDFs for both single-layer and multi-layer ink printouts (e.g., an ink covered by a
+%varnish layer). They then acquired a database of many different combinations of ink layers (up to
+%seven layer combinations were considered). However, they did not develop a method to simulate
+%the appearance of arbitrary ink layers. They were able to interpolate the appearance by spatially
+%multiplexing small tiles of different base combinations. By linearity of light transport, the simulation
+%of the combined appearance was reduced to linear combinations of the base BRDFs. 
+%simulation method for the appearance of translucent materials \cite{Hasan:2010}. 
+%They
+%built a measurement system for estimating multiple-scattering in homogeneous material slabs. They
+%measured both transmission and refection for a set of base materials used by the OBJET Connex
+%multi-material printer. 
+%Using these measurements, our simulations framework was able to predict
+%diffuse reflections and transmissions in multi-layered translucent objects composed of base material
+%layers.
+%In the proposed research, we will extend these methods to cover the complete appearance of
+%volumetric materials that accounts for both directly reflected light and light scattering within the
+%material volume. 
+%We will use efficient simulation methods that allows us to simulate the appearance
+%of complex structures composed from these base materials. We developed an initial framework for
+%simulating behavior of multi-layered materials, where each layer is a homogeneous base material.
+%Then we extend this simulation to materials in which each voxel is made of a different measured
+%material. Since this general simulation is expensive and requires path-tracing algorithms, we used
+%algorithms that are based on fast numerical integration of our low-dimensional representations
+%and the use of pre-computation, similar to pre-computed light transport approaches \cite{Sloan:2002}.
 \section{Contributions}
@@
 We couple this with a ``Tuner Network'' which automatically tunes the parameters of the Reducer Network to produce a fabricable object.
-Finally we will describe our API which utilizes these structures to produce numerous material assignment algorithms from a set of primitive operations.
+Finally we provide an extensible API which utilizes these structures to produce numerous material assignment algorithms from a set of primitive operations.
 \section{Methods}
 Below we will describe the key components of our framework and its associated API.
+We begin by describing the data structures that tie our framework together, the Reducer Network and the Tuner Network.
+We will then show how these two components interact to provide a compact graphical description of the material assignment problem.
+Finally we will show our basis set of components that we use to produce a wide-range of fabrication algorithms.
 \subsection{The Reducer Network}
@@
 
+\note{I think we should just go with the results we have, texture etc... show the reducer network, tuner network, simulated results and manufactured result (if you have them}
 \section{Results}

### 2012-12-20 paper.tex
interuppted again

--- 2012-12-20 paper.tex
@@
 \note{Should talk about influences from Shade Trees and Shader networks, note that these methods do not have tunable parameters}
+Shade trees \cite{Cook1984} are used to represent complex shading procedures for surfaces with different shading characteristics.
+It is very easy to make modification to a shade tree.
+Shade trees are widely adapted to 3D modeling software
 \section{Contributions}

### 2012-12-20 paper.tex
Blah

--- 2012-12-20 paper.tex
@@
 \usepackage{hyperref}
-\title{Spec2Fab: A  Graph-Based Reduction for Fabricating Fabrication Algorithms}
+\title{Spec2Fab: A  Graph-Based Framework for Fabricating Fabrication Algorithms}
 
@@
 Finally we will briefly review work done on modular shader languages as they have influenced our current work.
-\subsection{Material Assignment for Desired Optical Properties}
+
 Optimizing and manufacturing objects with desired optical characteristics is a popular problem in computer graphics.
@@
 Finally, optimal shadow casting surfaces have been produced which emulate a given set of input images ~\cite{Bermano:2012}.
-\subsection{Material Assignment for Desired Mechanical Properties}
-Fabricating objects with desire deformation characteristics has been explored less in the literature.
+
+Fabricating objects with desired deformation characteristics has been explored less in the literature.
 Some recent examples include simulating and manufacturing layered composites ~\cite{Bickel:2010} as well as the design and construction of balloons with a desired shape while inflated ~\cite{sko:2012}.
 Finally, material optimization has been employed to create mechanical clones of human faces ~\cite{Bickel:2012}.
-\subsection{Similarities between Methods}
+
 \autoref{tb:algorithms} shows the coordinate reduction method as well as the optimization scheme used in all cited works.
-A motivating observation for this research is that, despite different applications, these previous works share, not only a common methodology, but rely on a small set of common components to achieve their goals.
-Thus one could hope to find a small set of components that can be tied together to synthesize existing and new methods.
+A motivating observation for this research is that, despite different applications, these previous works share, not only a common methodology, but a set of common reduced coordinate components.
+These, in conjunction with (often off-the-shelf) optimization techniques form new material assignment algorithms.
+This suggests that one could find a small set of components that can be tied together to synthesize existing and new methods.
 Similar approaches have already proven useful for creating complex texture shading examples ~\cite{Cook1984}.
@@
 ~\cite{Bickel:2010}& Deformation & Layered Materials  & Branch and Bound \\
-~\cite{Finckh:2010} & Optical (Caustics) & B-Spline Surface & ??? \\
+~\cite{Finckh:2010} & Optical (Caustics) & B-Spline Surface & SPSA \\
 ~\cite{Hasan:2010}& Optical (Subsurface) & Layered Materials & Branch and Bound\\ 

### 2012-12-20 paper.tex
Quadratic->Surface Tiles

@@
 ~\cite{Hasan:2010}& Optical (Subsurface) & Layered Materials & Branch and Bound\\ 
-~\cite{Marios:2011} & Optical (Caustics) & Quadratic Surface Tiles & Simulated Annealing \\
+~\cite{Marios:2011} & Optical (Caustics) & Piecewise Constant Tiles & Simulated Annealing \\
 ~\cite{Bermano:2012} & Optical (Shadows) & Height Field & Custom/Simulated Annealing \\
 ~\cite{Bickel:2012} & Deformation &  Height Field &  Newton-Raphson \\
-~\cite{Papas:2012} & Optical & Quadratic Surface Tiles & Simulated Annealing \\
+~\cite{Papas:2012} & Optical & Piecewise Constant Tiles & Simulated Annealing \\
 ~\cite{sko:2012}& Deformation & Triangle Mesh & ALM \\

### 2012-12-20 paper.tex
Tuner 1 2

@@
 
- See \textbf{Figure 1} for an example of a Reducer Network. \note{Desai: Make figure 1}.
+ See \textbf{Figure \ref{fig:red1}} for an example of a Reducer Network. \note{Desai: Make figure 1}.
+
+\begin{figure}[h]
+\includegraphics[scale=0.3]{figure/redNetwork.pdf}
+\caption{An Reducer Network we used to produce one of our results.
+The input shape is sliced into two layers with the stratum partition node.
+The top slice is then partitioned into columns. Each column is assigned
+a stack of material layers.}
+\label{fig:red1}
+\end{figure}
 
 \subsection{Tuners}
+Tuner is an interface between a Reducer Node and an optimization algorithm.
+A Tuner contains a pointer to a Reducer Node and a pointer to a generic optimization subroutine.
+When a Tuner is linked to a Reducer Node, 
+it can tune the free variables contained in the sub-tree rooted at that node.
 \note{Desai: can you write this section, I don't know the details}
 \subsection{Tuning the Reducer Network}
-
+A Tuner initializes the optimization by querying the search space from its Reducer Node.
+The Reducer Node computes the search space by traversing its sub-tree and collecting
+free variables.
+The search space specifies the number of free variables, the type of each free variable
+(discrete or continuous) and the bounds of these variables.
+With the search space specifies, the Tuner's optimization subroutine executes.
+The optimization subroutine may ask for additional information such as
+the error value of a variable assignment and the gradient. These queries are answered
+with call-back functions set up by the Tuner before executing the optimization subroutine.
 \subsection{Tuner Network}

### 2012-12-20 paper.tex
tuner graph

@@
 \note{Desai: also this section :) }
+For some fabrication problems, the best material to assign to a location
+depends on the material assignment at nearby locations. 
+Tuning the free variables as if they were independent usually yields
+unsatisfactory results.
+Therefore, we allow the tuner to share information according to 
+a user-specified graph structure. 
+This allows our framework to be interfaced with a wide range of existing
+graph based optimization and inference algorithms.
+For example, consider the Floyd–Steinberg dithering algorithm where the error of a pixel is distributed
+to $4$ of its neighbors (right, lower left, down and lower right). The graph structure of this algorithm is illustrated in Figure~\ref{fig:tuner}.
+\begin{figure}[h]
+\includegraphics[scale=0.3]{figure/tuner.pdf}
+\caption{A sample Tuner Graph for the Floyd–Steinberg dithering algorithm.}
+\label{fig:tuner}
+\end{figure}
 %\section{System Description}

### 2012-12-21 paper.tex
tuner network combined with reducer network

--- 2012-12-20 paper.tex
@@
 
- See \textbf{Figure 1} for an example of a Reducer Network. \note{Desai: Make figure 1}.
+ See \textbf{Figure \ref{fig:red1}} for an example of a Reducer Network. \note{Desai: Make figure 1}.
+
+\begin{figure}[h]
+\includegraphics[scale=0.3]{figure/redNetwork.pdf}
+\caption{An Reducer Network we used to produce one of our results.
+The input shape is sliced into two layers with the stratum partition node.
+The top slice is then partitioned into columns. Each column is assigned
+a stack of material layers.}
+\label{fig:red1}
+\end{figure}
 
 \subsection{Tuners}
+Tuner is an interface between a Reducer Node and an optimization algorithm.
+A Tuner contains a pointer to a Reducer Node and a pointer to a generic optimization subroutine.
+When a Tuner is linked to a Reducer Node, 
+it can tune the free variables contained in the sub-tree rooted at that node.
 \note{Desai: can you write this section, I don't know the details}
 \subsection{Tuning the Reducer Network}
-
+A Tuner initializes the optimization by querying the search space from its Reducer Node.
+The Reducer Node computes the search space by traversing its sub-tree and collecting
+free variables.
+The search space specifies the number of free variables, the type of each free variable
+(discrete or continuous) and the bounds of these variables.
+With the search space specifies, the Tuner's optimization subroutine executes.
+The optimization subroutine may ask for additional information such as
+the error value of a variable assignment and the gradient. These queries are answered
+with call-back functions set up by the Tuner before executing the optimization subroutine.
 \subsection{Tuner Network}
 \note{Desai: also this section :) }
+For some fabrication problems, the best material to assign to a location
+depends on the material assignment at nearby locations. 
+Tuning the free variables as if they were independent usually yields
+unsatisfactory results.
+Therefore, we allow the tuner to share information according to 
+a user-specified graph structure. 
+This allows our framework to be interfaced with a wide range of existing
+graph based optimization and inference algorithms.
+For example, consider the Floyd–Steinberg dithering algorithm where the error of a pixel is distributed
+to $4$ of its neighbors (right, lower left, down and lower right). 
+The graph structure of this algorithm is illustrated in Figure~\ref{fig:tuner}.
+The tuner is combined with the Reducer Network in Figure~\ref{fig:red1}.
+A simplified view of the combined graph is shown in Figure~\ref{fig:combine}.
+Executing each tuner in order is equivalent to running the Floyd–Steinberg dithering algorithm.
+
+\begin{figure}[h]
+\includegraphics[scale=0.3]{figure/tuner.pdf}
+\caption{A sample Tuner Graph for the Floyd–Steinberg dithering algorithm.}
+\label{fig:tuner}
+\end{figure}
+
+\begin{figure}[h]
+\includegraphics[scale=0.3]{figure/netAndTuner.pdf}
+\caption{Combined graph for the error diffusion example.}
+\label{fig:combine}
+\end{figure}
 %\section{System Description}

### 2012-12-21 paper.tex
pseudo code

@@
 \usepackage{hyperref}
+\usepackage{program}
 \title{Spec2Fab: A  Graph-Based Framework for Fabricating Fabrication Algorithms}
@@
 
- See \textbf{Figure \ref{fig:red1}} for an example of a Reducer Network. \note{Desai: Make figure 1}.
+ See \textbf{Figure \ref{fig:red1}} for an example of a Reducer Network. \note{Desai: Make figure 1}.\\
+The sample Reducer Network can be constructed with the following pseudo-code.
+%There are may be a better place to put the pseudo code
+%\begin{program} can't figure out how to put it into a box
+\begin{verbatim}
+stratum->addInput(inputNode,0);
+column->addInput(stratum, 0);
+//add layered material to each column
+for(ii =0;ii<column->getNOutput();ii++){
+  layer = new LayeredMaterial(2);
+  layer->addInput(column,ii);
+}
+uniform = new UniformMaterial(0);
+uniform->addInput(stratum,1);
+\end{verbatim}
+%\caption{The Hello World! program in Java.}
+%\end{program}
 
@@
 Executing each tuner in order is equivalent to running the Floyd–Steinberg dithering algorithm.
+
+The Tuner graph can be constructed using the following pseudo-code
+%Can't figure out how to put it into a box
+\begin{verbatim}
+for(ii=0;ii<column->resolution;ii++){
+  for(jj =0;jj<column->resolution;jj++){
+  //add 4 neighbors for each tuner
+      tuner[ii][jj].nbr.push_back(ii,jj+1);
+      tuner[ii][jj].nbr.push_back(ii+1,jj-1);
+      tuner[ii][jj].nbr.push_back(ii+1,jj);
+      tuner[ii][jj].nbr.push_back(ii+1,jj+1);    
+    }
+  }
+}
+\end{verbatim}
 

### 2012-12-21 paper.tex
Cleaning up

@@
 We divide this review into two broad categories, optimizing for desired optical properties and optimizing for desired mechanical properties.
-Finally we will briefly review work done on modular shader languages as they have influenced our current work.
+We conclude by commenting on the similarities between these approaches.
 
 Optimizing and manufacturing objects with desired optical characteristics is a popular problem in computer graphics.
-Building objects which embed image in their caustics has been explored by Finch \textit{et al.} ~\shortcite{Finckh:2010} and Papas \textit{et al.}\shortcite{Marios:2011}.
+Building objects which embed images in their caustics has been explored by Finch \textit{et al.} ~\shortcite{Finckh:2010} and Papas \textit{et al.}\shortcite{Marios:2011}.
 Optimization based approaches have also been employed to control the subsurface scattering of printed 3D models ~\cite{Hasan:2010}.
-These approaches have also been extended to optically decrypt hidden images ~\cite{Papas:2012}.
+These methods have also been extended to optically decrypt hidden images ~\cite{Papas:2012}.
 Finally, optimal shadow casting surfaces have been produced which emulate a given set of input images ~\cite{Bermano:2012}.
@@
 
-\autoref{tb:algorithms} shows the coordinate reduction method as well as the optimization scheme used in all cited works.
+\autoref{tb:algorithms} shows the coordinate reduction methods as well as the optimization schemes used in all cited works.
 A motivating observation for this research is that, despite different applications, these previous works share, not only a common methodology, but a set of common reduced coordinate components.
@@
 We couple this with a ``Tuner Network'' which automatically tunes the parameters of the Reducer Network to produce a fabricable object.
-Finally we provide an extensible API which utilizes these structures to produce numerous material assignment algorithms from a set of primitive operations.
+Ultimately  we use these data structures to build an extensible, easy to use API which can produce numerous material assignment algorithms from a set of primitive operations.
 \section{Methods}
@@
 \subsection{The Reducer Network}
-Computing material assignments at output device resolution is computationally intractable.
+Computing material assignments at output device resolution is computationally inefficient.
 Because of this, material assignments are computed  using a reduced representation.
@@
 Because the network describes a nested set of partitions of unity we can efficiently perform material queries by passing a query point through the network until it arrives at a parameterization node.
-We note that Reducer Networks do not inherently enforce material continuity between disjoint regions in the graph however, for material assignment problems this is neither required nor desired.
+We note that Reducer Networks do not inherently enforce material continuity between disjoint regions in the graph, however, for material assignment problems this is neither required nor desired.
 
- See \textbf{Figure \ref{fig:red1}} for an example of a Reducer Network. \note{Desai: Make figure 1}.\\
-The sample Reducer Network can be constructed with the following pseudo-code.
+\autoref{fig:red1} shows an example Reducer Network which can be constructed with the following pseudo-code.
 %There are may be a better place to put the pseudo code
@@
 \includegraphics[scale=0.3]{figure/redNetwork.pdf}
-\caption{An Reducer Network we used to produce one of our results.
-The input shape is sliced into two layers with the stratum partition node.
+\caption{A Reducer Network used to produce one of our results.
+The input geometry is sliced into two layers with the stratum partition node.
 The top slice is then partitioned into columns. Each column is assigned
@@
 \subsection{Tuners}
-Tuner is an interface between a Reducer Node and an optimization algorithm.
-A Tuner contains a pointer to a Reducer Node and a pointer to a generic optimization subroutine.
-When a Tuner is linked to a Reducer Node, 
-it can tune the free variables contained in the sub-tree rooted at that node.
-\note{Desai: can you write this section, I don't know the details}
+We define tuners as an abstract interface between a Reducer Node and an optimization algorithm.
+Specifically a tuner is comprised of an optimization scheme, an error metric and a goal.
+Each tuner is attached to a specific geometric node in the Reducer Network.
+It then acts to optimize, or tune, the free variables associated with the subtree rooted at this node.
+One can think of this as a self-tuning shader network.
+This organizational structure allows us to easily optimize subdomains of our object using different tuners.
+We provide a mechanism for scheduling tuner execution thus allowing both serial and parallel processing.
+\note{Add a figure showing an example tuner}
 \subsection{Tuning the Reducer Network}
-A Tuner initializes the optimization by querying the search space from its Reducer Node.
+A Tuner initializes an optimization by querying the search space from its Reducer Node.
 The Reducer Node computes the search space by traversing its sub-tree and collecting
-free variables.
-The search space specifies the number of free variables, the type of each free variable
+free variables. The search space specifies the number of free variables, the type of each free variable
 (discrete or continuous) and the bounds of these variables.
-With the search space specifies, the Tuner's optimization subroutine executes.
+With the search space specified, the Tuner's optimization subroutine executes.
 The optimization subroutine may ask for additional information such as
@@
 with call-back functions set up by the Tuner before executing the optimization subroutine.
+We note that gradient computation of our material function $\lambda$ can be performed by efficiently traversing the Reducer Network.
 \subsection{Tuner Network}
-\note{Desai: also this section :) }
-For some fabrication problems, the best material to assign to a location
-depends on the material assignment at nearby locations. 
-Tuning the free variables as if they were independent usually yields
-unsatisfactory results.
-Therefore, we allow the tuner to share information according to 
-a user-specified graph structure. 
-This allows our framework to be interfaced with a wide range of existing
-graph based optimization and inference algorithms.
+For many fabrication problems, tuners cannot act in isolation.
+For instance,  occasionally the best material at a given point in space is dependent upon the material assignment at nearby locations.
+Tuning the free variables as if they were independent usually yields unsatisfactory results.
+Therefore, we allow the tuner to share information according to a user-specified graph structure.
+This allows our framework to be interfaced with a wide range of existing graph based optimization and inference algorithms.
 For example, consider the Floyd–Steinberg dithering algorithm where the error of a pixel is distributed

### 2012-12-21 paper.tex
Conclusions

@@
 \begin{abstract}
-
+Computational fabrication problems are often concerned with optimal material assignment.
+They attempt to compute a spatially varying material distribution that yields specified real-world behavior.
+In this paper we introduce Spec2Fab, a graph based framework that simplifies the design, development and implementation of these algorithms.
+We illustrate the utility of our framework by giving showing implemented fabrication algorithms as well as their manufactured results.
 \end{abstract}
@@
 \note{I think we should just go with the results we have, texture etc... show the reducer network, tuner network, simulated results and manufactured result (if you have them}
-\section{Results}
+\section{Results and Discussion}
 We used various generators in our experiments.
@@
 balancing bird with texture.
-\section{Possible Extension}
-UI to specify input deformation.
+%%\section{Possible Extension}
+%%UI to specify input deformation.
+\section{Limitations and Future Work}
+
 \section{Conclusion}
+We have presented Spec2Fab a graph based framework for building fabrication algorithms.
+By using the Reducer and Tuner Networks we reveal similarities between different fabrication algorithms allowing us to maximize component reuse.
+This both accelerates and eases implementation.
+We have also shown how using Spec2Fab facilitates the development and testing of new algorithms since Spec2Fab makes exploring the space of fabrication problems more efficient.
 \section*{Acknowledgements}

### 2012-12-21 paper.tex
table half way

--- 2012-12-21 paper.tex
@@
 \usepackage{hyperref}
-\usepackage{program}
+\usepackage{multirow}
 \title{Spec2Fab: A  Graph-Based Framework for Fabricating Fabrication Algorithms}
@@
 \section{Results}
-We used various generators in our experiments.
+We used various Reducer Nodes , simulation code and optimization algorithms in our experiments.
+A summary is listed in Table~\ref{tab:built-in}
+\begin{table}
+\centering %why
+\begin{tabular}{|p{2.5cm}|p{2.5cm}|p{2.5cm}|}
+\hline 
+Reducer Node & simulator & optimization\\
+\hline 
+Geometry Node & optics & \multirow{4}{*}{Error Diffusion, SPSA}\\
+ InputMesh, Stratum, Column&\\ \cline{1-2}
+Material Node & deformation  \\
+Constant, Layered,
+QuadLayer, SubdivisionSufrace& \\
+\hline 
+\end{tabular}
+\caption{Components we implemented and used in the experiments.}
+\label{tab:built-in}
+\end{table}
+
 \subsection{Print Material Characterization and Measurement}

### 2012-12-21 paper.tex

--- 2012-12-21 paper.tex
@@
 \note{I think we should just go with the results we have, texture etc... show the reducer network, tuner network, simulated results and manufactured result (if you have them}
-\section{Results and Discussion}
-We used various generators in our experiments.
+\section{Results}
+We used various Reducer Nodes , simulation code and optimization algorithms in our experiments.
+A summary is listed in Table~\ref{tab:built-in}
+\begin{table}
+\centering %why
+\begin{tabular}{|p{2.5cm}|p{2.5cm}|p{2.5cm}|}
+\hline 
+Reducer Node & simulator & optimization\\
+\hline 
+Geometry Node & optics & \multirow{4}{*}{Error Diffusion, SPSA}\\
+ InputMesh, Stratum, Column&\\ \cline{1-2}
+Material Node & deformation  \\
+Constant, Layered,
+QuadLayer, SubdivisionSufrace& \\
+\hline 
+\end{tabular}
+\caption{Components we implemented and used in the experiments.}
+\label{tab:built-in}
+\end{table}
 \subsection{Print Material Characterization and Measurement}

### 2012-12-21 paper.tex
table 2

@@
 A summary is listed in Table~\ref{tab:built-in}
-\begin{table}
-\centering %why
-\begin{tabular}{|p{2.5cm}|p{2.5cm}|p{2.5cm}|}
+\begin{table*}
+\centering
+\begin{tabular}{p{4cm}|p{4cm}|p{4cm}}
 \hline 
@@
 \hline 
-Geometry Node & optics & \multirow{4}{*}{Error Diffusion, SPSA}\\
- InputMesh, Stratum, Column&\\ \cline{1-2}
+Geometry Node & optics & \multirow{4}{4cm}{Error diffusion, SPSA, Branch and bound}\\
+ InputMesh, Stratum, Column&
+ Reflectance and transmittance, caustics\\ \cline{1-2}
 Material Node & deformation  \\
-Constant, Layered,
-QuadLayer, SubdivisionSufrace& \\
+Constant, Layered,QuadLayer, SubdivisionSufrace& 
+non-linear elasticity
+\\
 \hline
@@
 \label{tab:built-in}
-\end{table}
+\end{table*}
 \subsection{Print Material Characterization and Measurement}

### 2012-12-21 paper.tex
table 3

@@
 \section{Results}
-We used various Reducer Nodes , simulation code and optimization algorithms in our experiments.
-A summary is listed in Table~\ref{tab:built-in}
+We used various Reducer Nodes , simulator and optimization algorithms in our experiments.
+A summary of primitive components is listed in Table~\ref{tab:built-in}.
+Table~\ref{tab:example} lists for each example, the components involved.
 \begin{table*}
@@
 Material Node & deformation  \\
-Constant, Layered,QuadLayer, SubdivisionSufrace& 
+ConstantMaterial, 
+LayeredMaterial, QuadLayerMaterial, SubdivSurfMaterial & 
 non-linear elasticity
@@
 \end{table*}
-\subsection{Print Material Characterization and Measurement}
+
+\begin{table*}
+\centering
+\begin{tabular}{p{4cm}|p{4cm}|p{4cm}|p{4cm}}  %error metric is not interesting
+\hline 
+Example & Reducer Nodes & simulator & optimization\\
+\hline 
+Texture& Stratum, Column, LayeredMaterial & reflectance & Error diffusion \\
+\hline
+Subsurface scattering& Stratum, Column, LayeredMaterial & reflectance , transmittance & Branch and bound\\
+\hline 
+Caustics 1 & Column, QuadLayerMaterial & & SA \\
+\hline 
+Caustics 2 & Column, SubdivSurfMaterial & caustics & SPSA \\
+\hline
+Deformation & Column, LayeredMaterial& elasticity & Branch and bound\\
+\end{tabular}
+\caption{Components we implemented and used in the experiments.}
+\label{tab:example}
+\end{table*}
+
+\subsection{Textured Model}
+We expand the set of printable colors by stacking translucent materials. We then applied
+dithering with our expanded colors.
+Results are shown in Figure~\ref{fig:texture}
+
+%\subsection{Print Material Characterization and Measurement}
+%We used existing measurements of Objet print materials.
 \subsection{Subsurface Scattering, Deformation and Mass}
@@
 
-\subsection{Textured Model}
-Input: a textured 3D model and
-measured Albedo of print material.
-
-Output: (Probably gray-scale) Material arranged for different printers in different formats: STL, fable,Gcode.
-
-Printers: Our printer, Makerbot, Objet, maybe Zcorp.
-
-When printing texture, only the outer layer matters. We used 
-a composition of two generators: a very high resolution grid
-for the outer layer and a uniform material for the inside.
-
-We expand the set of printable colors by stacking translucent materials. We then applied
-dithering with our expanded colors.
-Results are shown in Figure~\ref{fig:texture}
 \subsection{New Examples for Mechanical Properties}

### 2012-12-21 paper.tex
forged results. Go home and add pictures

@@
 Deformation & Column, LayeredMaterial& elasticity & Branch and bound\\
+\hline
 \end{tabular}
@@
 \subsection{Textured Model}
-We expand the set of printable colors by stacking translucent materials. We then applied
-dithering with our expanded colors.
+We expand the set of printable colors by stacking translucent materials.
+We then applied dithering with our expanded colors.
 Results are shown in Figure~\ref{fig:texture}
+\subsection{Subsurface Scattering}
+We replicated \cite{Hasan:2010} using our framework.
 
-%\subsection{Print Material Characterization and Measurement}
-%We used existing measurements of Objet print materials.
-\subsection{Subsurface Scattering, Deformation and Mass}
-Combining previous work on replicating
-subsurface scattering and deformation behavior, 
-we produced
-material with a particular
-look and deformation properties as shown in Figure~\ref{fig:deform}.
-We als considered one additional property:mass. 
-In this example, we
-tried to make the material as light as possible.
+\subsection{Refractive Caustics}
+We replicated two algorithms 
+presented in \cite{Marios:2011} and \cite{Finckh:2010} for computing goal-based caustics.
+The first version computes a 2D grid of micro-lenses. 
+The optimization permutes the location of the micro-lenses using SA to achieve a smooth surface.
+This algorithm doesn't require any simulation.
 
-We tried different combinations of generators in this experiment.
-We compared the performance of these different generator
-in terms of run-time and error.
+In the second algorithm , we used subdivision surfaces to represent the surface for simplicity.
+The original algorithm used B-spline surfaces.
+We used a generic caustics shader for height field 
+instead of a specialized shader for spline surfaces.
+Our algorithm took 6 hours to finish with $4000$ control points for the model and $600\times 600$ resolution for the caustic image. 
+A picture of our printed result under desired lighting is shown in Figure~\ref{fig:caustic}.
+\begin{figure}
+	\centering
+ 	\includegraphics[width=0.3\textwidth]{figure/caustic.jpg}
+\caption{Teapot with a caustic image.}
+\label{fig:caustic}
+\end{figure}
+
+\subsection{Subsurface Scattering and Deformation}
+We first replicated \cite{Bickel:2010} to 
+print materials with specified elasticity.
+We then combined it with subsurface scattering
+matching to print material that approximates
+both the subsurface scattering property and the deformation behavior.
+The result is shown in Figure~\ref{fig:deform}.
+%We tried different combinations of generators in this experiment.
+%We compared the performance of these different generator
+%in terms of run-time and error.
 \begin{enumerate}
@@
 \label{fig:err}
-\end{figure}
-
-\subsection{Caustics for a Mesh}
-We demonstrate how to produce a 3D model with specific caustic shape under a particular lighting,
-similar to \cite{Finckh:2010}. The difference is that we optimize on an arbitrary 3D model,
-and we use a generic rendering package (NVidia optiX). 
-We represented the surface with a spline surface.
-Our algorithm took 6 hours to finish
-with $4000$ spline control points for the model and $600\times 600$ resolution for the caustic image. A 
-picture of our printed result under desired lighting is shown in Figure~\ref{fig:caustic}.
-
-\begin{figure}
-	\centering
- 	\includegraphics[width=0.3\textwidth]{figure/caustic.jpg}
-\caption{Teapot with a caustic image.}
-\label{fig:caustic}
 \end{figure}

### 2012-12-21 paper.tex
more forged results before I go home

@@
 The result is shown in Figure~\ref{fig:deform}.
+The combination is done by simply alternating tuners for the two
+separate problems.
 %We tried different combinations of generators in this experiment.
@@
 %in terms of run-time and error.
-\begin{enumerate}
-\item Spline for top layer, fine-grained voxelization for mid layer
-and a coarse grid for bottom layer.
-\item Voxels for top layer, splines for middle layer and a coarse
-bottom layer.
-\item Find-grained voxels for top layer and coarse grid for bottom layer.
-\end{enumerate}
+%\begin{enumerate}
+%\item Spline for top layer, fine-grained voxelization for mid layer
+%and a coarse grid for bottom layer.
+%\item Voxels for top layer, splines for middle layer and a coarse
+%bottom layer.
+%\item Find-grained voxels for top layer and coarse grid for bottom layer.
+%\end{enumerate}
 
@@
 \subsection{New Examples for Mechanical Properties}
-Ball bounce to certain height. We used a higher resolution
-grid for the out layer and very low resolution
-for the inner mesh.
+%Ball bounce to certain height. We used a higher resolution
+%grid for the out layer and very low resolution
+%for the inner mesh.
+%
+%A plot of bounce height after each iteration.
+%The height and desired height is plotted in Figure~\ref{fig:ball}
+%\begin{figure}
+%	\centering
+% 	\includegraphics[width=0.3\textwidth]{figure/ballHeight.pdf}
+%\caption{Simulated height per-iteration of a ball bouncing after free-falling at 1 meter height.
+%	Redline is desired height.}
+%\label{fig:ball}
+%\end{figure}
 
-A plot of bounce height after each iteration.
-The height and desired height is plotted in Figure~\ref{fig:ball}
-\begin{figure}
-	\centering
- 	\includegraphics[width=0.3\textwidth]{figure/ballHeight.pdf}
-\caption{Simulated height per-iteration of a ball bouncing after free-falling at 1 meter height.
-	Redline is desired height.}
-\label{fig:ball}
-\end{figure}
-
-A loaded die as shown in Figure~\ref{fig:die}. This example is interesting because
-a local change will have some global effect.
+A loaded die as shown in Figure~\ref{fig:die}. 
+This example is a showcase for a global optimization algorithm
+because a local change of material assignment will influence the global behavior.
 We used very high resolution grid for the surface to match texture

### 2012-12-21 paper.tex
Editing results

@@
 \note{I think we should just go with the results we have, texture etc... show the reducer network, tuner network, simulated results and manufactured result (if you have them}
-\section{Results}
-We used various Reducer Nodes , simulator and optimization algorithms in our experiments.
-A summary of primitive components is listed in Table~\ref{tab:built-in}.
-Table~\ref{tab:example} lists for each example, the components involved.
+\section{Results and Discussion}
+Table~\ref{tab:built-in} shows a list of nodes implemented in our framework.
+With this set of nodes we can reproduce all previous work previously discussed.
+This validates our assertion, that the space of fabrication  algorithms can be spanned effectively using the Reducer and Tuner networks.
+Secondly it illustrates how we can leverage component reuse to quickly create such algorithms.
+Table~\ref{tab:example} lists the components of the framework used to recreate each example.
 \begin{table*}
 \centering
-\begin{tabular}{p{4cm}|p{4cm}|p{4cm}}
+\begin{tabular}{lc}
 \hline 
-Reducer Node & simulator & optimization\\
+\textbf{Reducer Node} & \textbf{Description} \\
+Geometry Nodes &\\
 \hline
-Geometry Node & optics & \multirow{4}{4cm}{Error diffusion, SPSA, Branch and bound}\\
- InputMesh, Stratum, Column&
- Reflectance and transmittance, caustics\\ \cline{1-2}
-Material Node & deformation  \\
-ConstantMaterial, 
-LayeredMaterial, QuadLayerMaterial, SubdivSurfMaterial & 
-non-linear elasticity
-\\
+InputMesh & Loads shape to which materials will be assigned\\\
+Stratum & Divides an input volume into an outer layer of given thickness and an interior blob\\
+Column & Divides an input volume into a number of columns\\
+\hline
+Material Nodes &\\
+\hline
+ConstantMaterial & Assigns a constant material to an input volume \\
+LayeredMaterial &  Assigns a layered set of materials to an input volume \\
+QuadLayerMaterial & ??? \\
+SubdivSurfMateral & ??? \\
 \hline
@@
 \centering
-\begin{tabular}{p{4cm}|p{4cm}|p{4cm}|p{4cm}}  %error metric is not interesting
+\begin{tabular}{llll}  %error metric is not interesting
 \hline 
-Example & Reducer Nodes & simulator & optimization\\
+\textbf{Example} & \textbf{Reducer Nodes} & \textbf{Simulator} & \textbf{Optimization}\\
 \hline 
 Texture& Stratum, Column, LayeredMaterial & reflectance & Error diffusion \\
-\hline
 Subsurface scattering& Stratum, Column, LayeredMaterial & reflectance , transmittance & Branch and bound\\
-\hline 
 Caustics 1 & Column, QuadLayerMaterial & & SA \\
-\hline 
 Caustics 2 & Column, SubdivSurfMaterial & caustics & SPSA \\
-\hline
 Deformation & Column, LayeredMaterial& elasticity & Branch and bound\\
@@
 \subsection{Textured Model}
-We expand the set of printable colors by stacking translucent materials.
+Here we design an algorithm to print textured models using a two-tone printer.
+We expand the set of printable colors by stacking translucent materials using the LayeredMaterial node.
 We then applied dithering with our expanded colors.
-Results are shown in Figure~\ref{fig:texture}
+\autoref{fig:texture} shows the results of this method.
 \subsection{Subsurface Scattering}
@@
 \subsection{Refractive Caustics}
-We replicated two algorithms 
-presented in \cite{Marios:2011} and \cite{Finckh:2010} for computing goal-based caustics.
-The first version computes a 2D grid of micro-lenses. 
-The optimization permutes the location of the micro-lenses using SA to achieve a smooth surface.
-This algorithm doesn't require any simulation.
+We have also implemented two algorithms for computing goal-based caustics;  ~\cite{Marios:2011} and ~\cite{Finckh:2010}.
+The first version of this algorithm computes  a set of micro-lenses which produce the desired caustic image.
+The optimization applies simulated annealing in order to permute the location of these micro-lenses in order to achieve a smooth surface.
+Of note is the fact that this algorithm does not quire a simulation algorithm.
+Despite this it is still implementable within our framework.
 
-In the second algorithm , we used subdivision surfaces to represent the surface for simplicity.
+In the second algorithm , we use subdivision surfaces to represent a smooth caustic caustic surface.
+This is in contrast to the potentially discontinuous surface in the method above.
 The original algorithm used B-spline surfaces.
-We used a generic caustics shader for height field 
-instead of a specialized shader for spline surfaces.
+We also replace the specialized renderer from the original publication with a generic, fast caustics rendering technique ~\cite{Yuksel:2009}.
 Our algorithm took 6 hours to finish with $4000$ control points for the model and $600\times 600$ resolution for the caustic image.
@@
 \subsection{Subsurface Scattering and Deformation}
-We first replicated \cite{Bickel:2010} to 
-print materials with specified elasticity.
-We then combined it with subsurface scattering
-matching to print material that approximates
-both the subsurface scattering property and the deformation behavior.
+We first replicated \cite{Bickel:2010} to print materials with specified elasticity. We then combined it with subsurface scattering
+matching to print material that approximates both the subsurface scattering property and the deformation behavior.
 The result is shown in Figure~\ref{fig:deform}.
-The combination is done by simply alternating tuners for the two
+In our case we perform coupling at the tuner level by alternating tuner execution for the two
 separate problems.
+This shows how our framework can facilitates the creation of new fabrication problems by allowing easy reuse of previous work and also providing a ``playground'' in which one can explore different computational approaches.
 %We tried different combinations of generators in this experiment.

### 2012-12-21 paper.tex
Editing results

@@
 Lambda can either output material parameters or a discrete material assignment for a spatial point $\left(x,y,z\right)$ given some parameters, here denoted by $\theta$.
+We allow our material assignment nodes to assign a void material to regions of the mesh.
+This allows us to treat surface displacements and material assignments in a unified fashion.
 Because the network describes a nested set of partitions of unity we can efficiently perform material queries by passing a query point through the network until it arrives at a parameterization node.
@@
 Table~\ref{tab:built-in} shows a list of nodes implemented in our framework.
-With this set of nodes we can reproduce all previous work previously discussed.
+With this set of nodes we can reproduce all work previously discussed.
 This validates our assertion, that the space of fabrication  algorithms can be spanned effectively using the Reducer and Tuner networks.
-Secondly it illustrates how we can leverage component reuse to quickly create such algorithms.
-Table~\ref{tab:example} lists the components of the framework used to recreate each example.
+Secondly it illustrates how we can leverage component reuse to quickly create such algorithms.\autoref{tab:example} lists the components of the framework used to recreate each example.
 \begin{table*}
@@
 The first version of this algorithm computes  a set of micro-lenses which produce the desired caustic image.
-The optimization applies simulated annealing in order to permute the location of these micro-lenses in order to achieve a smooth surface.
+The optimization applies simulated annealing to permute the location of these micro-lenses in order to construct a smooth surface.
 Of note is the fact that this algorithm does not quire a simulation algorithm.
@@
 
-In the second algorithm , we use subdivision surfaces to represent a smooth caustic caustic surface.
+In the second algorithm, we use subdivision surfaces to represent a smooth caustic surface.
 This is in contrast to the potentially discontinuous surface in the method above.
-The original algorithm used B-spline surfaces.
+The original algorithm used B-spline surfaces however we have replaced these with a subdivision surface.
 We also replace the specialized renderer from the original publication with a generic, fast caustics rendering technique ~\cite{Yuksel:2009}.
 Our algorithm took 6 hours to finish with $4000$ control points for the model and $600\times 600$ resolution for the caustic image.
-A picture of our printed result under desired lighting is shown in Figure~\ref{fig:caustic}.
+A picture of our printed result under desired lighting is shown in \autoref{fig:caustic}.
 \begin{figure}
@@
 separate problems.
-This shows how our framework can facilitates the creation of new fabrication problems by allowing easy reuse of previous work and also providing a ``playground'' in which one can explore different computational approaches.
+Here we see that our framework facilitates the creation of new fabrication problems by allowing easy reuse of previous work and also providing a ``playground'' in which one can explore different computational approaches.
+\autoref{fig:err} contains two error plots showing that the subsurface scattering and deformation errors decrease after each tuner iteration.
+
 %We tried different combinations of generators in this experiment.
@@
 
-Two error plots showing subsurface scattering and deformation errors decrease
-after each iteration in Figure~\ref{fig:err}.
-
 \begin{figure}
@@
 
-\subsection{New Examples for Mechanical Properties}
-%Ball bounce to certain height. We used a higher resolution
-%grid for the out layer and very low resolution
-%for the inner mesh.
+%\subsection{New Examples for Mechanical Properties}
+%%Ball bounce to certain height. We used a higher resolution
+%%grid for the out layer and very low resolution
+%%for the inner mesh.
+%%
+%%A plot of bounce height after each iteration.
+%%The height and desired height is plotted in Figure~\ref{fig:ball}
+%%\begin{figure}
+%%	\centering
+%% 	\includegraphics[width=0.3\textwidth]{figure/ballHeight.pdf}
+%%\caption{Simulated height per-iteration of a ball bouncing after free-falling at 1 meter height.
+%%	Redline is desired height.}
+%%\label{fig:ball}
+%%\end{figure}
 %
-%A plot of bounce height after each iteration.
-%The height and desired height is plotted in Figure~\ref{fig:ball}
+%
+%A loaded die as shown in Figure~\ref{fig:die}. 
+%This example is a showcase for a global optimization algorithm
+%because a local change of material assignment will influence the global behavior.
+%We used very high resolution grid for the surface to match texture
+%of a die. The inner lay has only $3\times 3$ resolution.
 %\begin{figure}
 %	\centering
-% 	\includegraphics[width=0.3\textwidth]{figure/ballHeight.pdf}
-%\caption{Simulated height per-iteration of a ball bouncing after free-falling at 1 meter height.
-%	Redline is desired height.}
-%\label{fig:ball}
+% 	\includegraphics[width=0.25\textwidth]{figure/die.png}
+%\caption{A printed loaded die}
+%\label{fig:die}
 %\end{figure}
-
-A loaded die as shown in Figure~\ref{fig:die}. 
-This example is a showcase for a global optimization algorithm
-because a local change of material assignment will influence the global behavior.
-We used very high resolution grid for the surface to match texture
-of a die. The inner lay has only $3\times 3$ resolution.
-\begin{figure}
-	\centering
- 	\includegraphics[width=0.25\textwidth]{figure/die.png}
-\caption{A printed loaded die}
-\label{fig:die}
-\end{figure}
-It has a certain probability to land on "1".
-A table of probability distribution of landing on each side
-is shown in Table~\ref{tab:dice}.
-
-\begin{table}
-\centering
-  \begin{tabular}{ |c| p{0.7in} | p{0.7in} | }
-  \hline
-  face & simulated probability & measured probability\\
-  \hline
-  1 & 0.5 & 0.5\\
-  \hline
-  2 & 0.1 & 0.1\\
-  \hline
-  3 & 0.1 & 0.1\\
-  \hline
-  4 & 0.1 & 0.1\\
-  \hline
-  5 & 0.1 & 0.1\\
-  \hline
-  6 & 0.1 & 0.1\\
-
-  \hline
-  \end{tabular}
-  \caption{Simulated and measured dice probability}
-  \label{tab:dice}
-\end{table}
-
-A plot of simulated probability of landing on "1" after each iteration
-is shown in Figure~\ref{fig:dieErr}.
-
-\begin{figure}
-	\centering
- 	\includegraphics[width=0.3\textwidth]{figure/die.pdf}
-\caption{Probability of die landing on 1 after each iteration.}
-\label{fig:dieErr}
-\end{figure}
-
-Printer:objet, ours.
-
-More ideas:
-balancing bird with texture.
-%%\section{Possible Extension}
-%%UI to specify input deformation.
+%It has a certain probability to land on "1".
+%A table of probability distribution of landing on each side
+%is shown in Table~\ref{tab:dice}.
+%
+%\begin{table}
+%\centering
+%  \begin{tabular}{ |c| p{0.7in} | p{0.7in} | }
+%  \hline
+%  face & simulated probability & measured probability\\
+%  \hline
+%  1 & 0.5 & 0.5\\
+%  \hline
+%  2 & 0.1 & 0.1\\
+%  \hline
+%  3 & 0.1 & 0.1\\
+%  \hline
+%  4 & 0.1 & 0.1\\
+%  \hline
+%  5 & 0.1 & 0.1\\
+%  \hline
+%  6 & 0.1 & 0.1\\
+%
+%  \hline
+%  \end{tabular}
+%  \caption{Simulated and measured dice probability}
+%  \label{tab:dice}
+%\end{table}
+%
+%A plot of simulated probability of landing on "1" after each iteration
+%is shown in Figure~\ref{fig:dieErr}.
+%
+%\begin{figure}
+%	\centering
+% 	\includegraphics[width=0.3\textwidth]{figure/die.pdf}
+%\caption{Probability of die landing on 1 after each iteration.}
+%\label{fig:dieErr}
+%\end{figure}
+%
+%Printer:objet, ours.
+%
+%More ideas:
+%balancing bird with texture.
+%%%\section{Possible Extension}
+%%%UI to specify input deformation.
 \section{Limitations and Future Work}

### 2012-12-21 paper.tex
paper tex

--- 2012-12-21 paper.tex
@@
         	(d)objet}\label{teaser}
-	\label{fig:texture}
  }
@@
 presented in \cite{Marios:2011} and \cite{Finckh:2010} for computing goal-based caustics.
-The first version computes a 2D grid of micro-lenses. 
+The first version computes a 2D grid composed of micro-lenses. 
 The optimization permutes the location of the micro-lenses using SA to achieve a smooth surface.
+Each tuner is connected to its four neighbors.
+During the execution of an individual tuner, the optimization algorithm makes a randomized decision about
+ whether or not to swap its micro-lens with one of its neighbors.
+The tuners are run in sequence until some convergence criteria is hit.
+(it's also easy to implement a parallel version).
 This algorithm doesn't require any simulation.

### 2012-12-21 paper.tex
table 2 explain

--- 2012-12-21 paper.tex
@@
 LayeredMaterial &  Assigns a layered set of materials to an input volume \\
-QuadLayerMaterial & ??? \\
-SubdivSurfMateral & ??? \\
+QuadLayerMaterial & Like LayeredMaterial, but the materials are separated by a quadrangle\\
+SubdivSurfMateral & Like LayeredMaterial, but the materials are separated by a subdivision surface \\
 \hline
@@
 The optimization applies simulated annealing to permute the location of these micro-lenses in order to construct a smooth surface.
+Each tuner is connected to its four neighbors.
+During the execution of an individual tuner, the optimization algorithm makes a randomized decision about
+ whether or not to swap its micro-lens with one of its neighbors.
+The tuners are run in sequence until some convergence criteria is met.
 Of note is the fact that this algorithm does not quire a simulation algorithm. 

### 2012-12-21 paper.tex
add result table

@@
 Secondly it illustrates how we can leverage component reuse to quickly create such algorithms.\autoref{tab:example} lists the components of the framework used to recreate each example.
+
+For each example, we show the target, the simulated output, and the fabricated result in Figure~\ref{tab:result}.
+
 \begin{table*}
@@
 \centering
+\begin{tabular}{|l|l|l|l|}
+\hline 
+\textbf{Example} & \textbf{Target} & \textbf{Simulation} & \textbf{Printed Result}\\
+\hline 
+Texture&  \includegraphics[width=3cm]{figure/globeTarget.png}& \includegraphics[width=3cm]{figure/globeSim.png}
+& \includegraphics[width=3cm]{figure/globe.png}\\
+&  \includegraphics[width=3cm]{figure/mapTarget.png}& \includegraphics[width=3cm]{figure/mapSim.png}
+& \includegraphics[width=3cm]{figure/map.png}\\
+\hline
+\end{tabular}
+\caption{Components we implemented and used in the experiments.}
+\label{tab:example}
+\end{table*}
+
+\begin{table*}
+\centering
 \begin{tabular}{llll}  %error metric is not interesting
@@
 \end{tabular}
-\caption{Components we implemented and used in the experiments.}
-\label{tab:example}
+\caption{Fabricated results.}
+\label{tab:result}
 \end{table*}

### 2012-12-21 paper.tex
table mis indexing
table figures
rename a file

@@
 \centering
-\begin{tabular}{|l|l|l|l|}
-\hline 
-\textbf{Example} & \textbf{Target} & \textbf{Simulation} & \textbf{Printed Result}\\
-\hline 
-Texture&  \includegraphics[width=3cm]{figure/globeTarget.png}& \includegraphics[width=3cm]{figure/globeSim.png}
-& \includegraphics[width=3cm]{figure/globe.png}\\
-&  \includegraphics[width=3cm]{figure/mapTarget.png}& \includegraphics[width=3cm]{figure/mapSim.png}
-& \includegraphics[width=3cm]{figure/map.png}\\
-\hline
-\end{tabular}
-\caption{Components we implemented and used in the experiments.}
-\label{tab:example}
-\end{table*}
-
-\begin{table*}
-\centering
 \begin{tabular}{llll}  %error metric is not interesting
@@
 \caption{Fabricated results.}
+\label{tab:example}
+\end{table*}
+
+\begin{table*}
+\centering
+\begin{tabular}{|p{2cm}|l|l|l|}
+\hline 
+\textbf{Example} & \textbf{Target} & \textbf{Simulation} & \textbf{Printed Result}\\
+\hline 
+Texture&  \includegraphics[width=3cm]{figure/globeTarget.png}& \includegraphics[width=3cm]{figure/globeSim.png}
+& \includegraphics[width=3cm]{figure/globe.png}\\
+&  \includegraphics[width=3cm]{figure/mapTarget.png}& \includegraphics[width=3cm]{figure/mapSim.png}
+& \includegraphics[width=3cm]{figure/map.png}\\
+\hline
+Subsurface Scattering&  \includegraphics[width=3cm]{figure/chessTarget.png}& \includegraphics[width=3cm]{figure/chessSim.png}
+& \includegraphics[width=3cm]{figure/chess.png}\\
+\hline
+Caustics &  \includegraphics[width=3cm]{figure/causticsTarget.png}& \includegraphics[width=3cm]{figure/causticsSim.png}
+& \includegraphics[width=3cm]{figure/caustics.png}\\
+\hline
+\end{tabular}
+\caption{Components we implemented and used in the experiments.}
 \label{tab:result}

### 2012-12-21 paper.tex
teaser

@@
  \teaser{
-   \begin{subfigure}[b]{0.3\textwidth}
+   \begin{subfigure}[b]{0.2\textwidth}
 	\centering
-    	\includegraphics[width=0.6\textwidth]{figure/bunny_orig.png}
+    	\includegraphics[width=\textwidth]{figure/globe.png}
       	\caption{}
@@
         ~ 
-        \begin{subfigure}[b]{0.18\textwidth}
+        \begin{subfigure}[b]{0.2\textwidth}
                 \centering
-    	\includegraphics[width=\textwidth]{figure/bunny_print1.jpg}
+    	\includegraphics[width=\textwidth]{figure/map.png}
                 \caption{}
@@
                 \centering
-    	\includegraphics[width=\textwidth]{figure/bunny_print2.jpg}
+    	\includegraphics[width=\textwidth]{figure/chess.png}
                 \caption{}
@@
         ~
-        \begin{subfigure}[b]{0.18\textwidth}
+        \begin{subfigure}[b]{0.2\textwidth}
                 \centering
-    	\includegraphics[width=\textwidth]{figure/bunny_print3.jpg}
+    	\includegraphics[width=\textwidth]{figure/caustics.png}
                 \caption{}
@@
         \end{subfigure}
-        \caption{A textured mesh printed with different types of 3D printers.
-        	(a)original model.(b)printed with our printer.(c)makerbot.
-        	(d)objet}\label{teaser}
+        \caption{Various effects printed with a 3D printer.
+        	(a)(b)textured models,(c)a model with a subsurface-scattering resembling a marble chess-board.
+        	(d)a caustics image projected by an object under proper lighting}\label{teaser}
  }

### 2012-12-21 paper.tex
add figure for a single tuner

@@
 We provide a mechanism for scheduling tuner execution thus allowing both serial and parallel processing.
-\note{Add a figure showing an example tuner}
 \subsection{Tuning the Reducer Network}
-A Tuner initializes an optimization by querying the search space from its Reducer Node.
+\autoref{fig:tuner0} shows a typical workflow for a tuner.
+\begin{figure}
+\includegraphics[width=0.4\textwidth]{figure/tuner0.png}
+\caption{Typical workflow for a Tuner.}
+\label{fig:tuner0}
+\end{figure}
+A Tuner initializes its optimization procedure by querying the search space from its Reducer Node.
 The Reducer Node computes the search space by traversing its sub-tree and collecting
@@
 with call-back functions set up by the Tuner before executing the optimization subroutine. 
+The call-back function typically performs the following three steps:
+using Reducer Node to convert a variable assignment back to material assignment
+over the volume, running simulation with the new material assignment
+and computing errors given the simulated result.
 We note that gradient computation of our material function $\lambda$ can be performed by efficiently traversing the Reducer Network.
@@
 \end{tabular}
-\caption{Fabricated results.}
+\caption{Example pipelines constructed for our experiments.}
 \label{tab:example}
@@
 \end{tabular}
-\caption{Components we implemented and used in the experiments.}
+\caption{Fabricated objects.}
 \label{tab:result}
@@
 We then applied dithering with our expanded colors.
-\autoref{fig:texture} shows the results of this method.
+The first two rows in \autoref{tab:result} shows the results of this method.
 \subsection{Subsurface Scattering}

### 2012-12-21 paper.tex
minor \"fixes\"

@@
 
+\usepackage{amsfonts}
 \usepackage{caption}
@@
         \end{subfigure}
-        \caption{Various effects printed with a 3D printer.
+        \caption{3D-printed objects with various effects designed by our API.
         	(a)(b)textured models,(c)a model with a subsurface-scattering resembling a marble chess-board.
@@
 In this paper we introduce Spec2Fab, a graph based framework that simplifies the design, development and implementation of these algorithms.
-We illustrate the utility of our framework by giving showing implemented fabrication algorithms as well as their manufactured results.
+We illustrate the utility of our framework by
+showing implemented fabrication algorithms as well as their manufactured results. 
 \end{abstract}
@@
 
-\note{Teaser should be all different results produced using spec2Fab, texture, subsurface scattering, caustics etc...}
+%\note{Teaser should be all different results produced using spec2Fab, texture, subsurface scattering, caustics etc...}
 
@@
 A geometry node takes a volumetric region as input and produces a partition of unity of this region as output.
-The leaf nodes of our graph are the parameterization nodes which associate a material assignment function of the form $\lambda\left(x,y,z,\theta\right)$ to an input volumetric region.
-Lambda can either output material parameters or a discrete material assignment for a spatial point $\left(x,y,z\right)$ given some parameters, here denoted by $\theta$.
+The leaf nodes of our graph are the parameterization nodes which associate a material assignment function of the form $\lambda\left(x,y,z, \boldsymbol{\theta}\right)$ to an input volumetric region.
+$\lambda$ can either output material parameters or a discrete material assignment for a spatial point $\left(x,y,z\right)$ given some parameters, here denoted by $ \boldsymbol{\theta}$.
 We allow our material assignment nodes to assign a void material to regions of the mesh.
@@
 using Reducer Node to convert a variable assignment back to material assignment
-over the volume, running simulation with the new material assignment
+function $\lambda$, running simulation with the new material assignment
 and computing errors given the simulated result.
-We note that gradient computation of our material function $\lambda$ can be performed by efficiently traversing the Reducer Network.
+We note that our material function $\lambda$ can 
+be efficiently evaluated by traversing the Reducer Network.
+%I need to think about this
+%We note that gradient computation of our material function $\lambda$ can also 
+%be performed by efficiently traversing the Reducer Network.
 \subsection{Tuner Network}
@@
 Tuning the free variables as if they were independent usually yields unsatisfactory results.
-Therefore, we allow the tuner to share information according to a user-specified graph structure.
+Therefore, we allow the tuners to share information according to a user-specified graph structure.
 This allows our framework to be interfaced with a wide range of existing graph based optimization and inference algorithms.

### 2012-12-21 paper.tex
Spelling and Grammar check

@@
 Computational fabrication couples new digital manufacturing techniques with novel numerical algorithms to produce objects with remarkable physical characteristics.
-These methods are of great interest in computer graphics for two reasons: First, they provide us with  new class of output devices which can render into  real-life and second, they yield valuable insight into the accuracy of our numerical models of the world.
+These methods are of great interest in computer graphics for two reasons: First, they provide us with  a new class of output devices which can render into  real-life and second, they yield valuable insight into the accuracy of our numerical models of the world.
 
@@
 The algorithms that solve these problems are often complicated to develop, implement, test and modify.
-We provide a new graph-based framework which decomposes such problems into a small set of constituent components alleviating the above issues as well as facilitating the development and testing of new algorithms.
+We provide a new graph-based framework which decomposes such problems into a small set of constituent components alleviating the above issues as well as facilitating the development and testing of new methods.
 
@@
 
-Fabricating objects with desired deformation characteristics has been explored less in the literature.
-Some recent examples include simulating and manufacturing layered composites ~\cite{Bickel:2010} as well as the design and construction of balloons with a desired shape while inflated ~\cite{sko:2012}.
+Fabricating objects with desired mechanical characteristics has been explored less in the literature.
+Some recent examples include simulating and manufacturing layered composites ~\cite{Bickel:2010} as well as the design and construction of balloons with a prescribed shape while inflated ~\cite{sko:2012}.
 Finally, material optimization has been employed to create mechanical clones of human faces ~\cite{Bickel:2012}.
@@
 We will then show how these two components interact to provide a compact graphical description of the material assignment problem.
-Finally we will show our basis set of components that we use to produce a wide-range of fabrication algorithms.
+Finally, we will detail the basis set of components that we use to produce a wide-range of fabrication algorithms.
 \subsection{The Reducer Network}
@@
 Because the network describes a nested set of partitions of unity we can efficiently perform material queries by passing a query point through the network until it arrives at a parameterization node.
-We note that Reducer Networks do not inherently enforce material continuity between disjoint regions in the graph, however, for material assignment problems this is neither required nor desired.
+We note that Reducer Networks do not inherently enforce material continuity between disjoint regions of the object, however, for material assignment problems this is neither required nor desired.
 
@@
 \subsection{Tuning the Reducer Network}
-\autoref{fig:tuner0} shows a typical workflow for a tuner.
+\autoref{fig:tuner0} shows a typical workflow for the tuner.
 \begin{figure}
@@
 using Reducer Node to convert a variable assignment back to material assignment
-function $\lambda$, running simulation with the new material assignment
+function $\lambda$, running a simulation with the new material assignment
 and computing errors given the simulated result.
@@
 This allows our framework to be interfaced with a wide range of existing graph based optimization and inference algorithms.
-For example, consider the Floyd–Steinberg dithering algorithm where the error of a pixel is distributed
+For example, consider the Floyd–Steinberg dithering algorithm in which the error at a given pixel is distributed
 to $4$ of its neighbors (right, lower left, down and lower right).
@@
 
-\note{I think we should just go with the results we have, texture etc... show the reducer network, tuner network, simulated results and manufactured result (if you have them}
+%\note{I think we should just go with the results we have, texture etc... show the reducer network, tuner network, simulated results and manufactured result (if you have them}
 \section{Results and Discussion}
@@
 \subsection{Textured Model}
-Here we design an algorithm to print textured models using a two-tone printer.
+Here we design an algorithm to print textured models using a two material printer.
 We expand the set of printable colors by stacking translucent materials using the LayeredMaterial node.
-We then applied dithering with our expanded colors.
+We then applied dithering using this expanded gamut.
 The first two rows in \autoref{tab:result} shows the results of this method.
@@
 The tuners are run in sequence until some convergence criteria is met.
-Of note is the fact that this algorithm does not quire a simulation algorithm. 
-Despite this it is still implementable within our framework.
+Of note is the fact that this method does not require a simulation algorithm. 
+Despite this, it is still implementable within our framework.
 
@@
 This is in contrast to the potentially discontinuous surface in the method above. 
-The original algorithm used B-spline surfaces however we have replaced these with a subdivision surface. 
+The original algorithm used a B-spline surface representation, however we have replaced this with a subdivision surface. 
 We also replace the specialized renderer from the original publication with a generic, fast caustics rendering technique ~\cite{Yuksel:2009}.
@@
 This both accelerates and eases implementation.
-We have also shown how using Spec2Fab facilitates the development and testing of new algorithms since Spec2Fab makes exploring the space of fabrication problems more efficient.
+We have also shown that Spec2Fab facilitates the development and testing of new algorithms since Spec2Fab makes exploring the space of fabrication problems more efficient.
 \section*{Acknowledgements}

### 2013-01-06 paper.tex
intro, previous work

@@
 \usepackage{multirow}
-\title{Spec2Fab: A  Graph-Based Framework for Fabricating Fabrication Algorithms}
+%\title{A Graph-Based Reduction for Optimal Material Assignment} 
+\title{A reduced representation for computational fabrication}
+% A reduced representation for computational fabrication
+%\title{Spec2Fab: A Graph-Based Reduction for Computational Fabrication Algorithms}
+% High-fidelity Mapping From Specification to Fabrication 
+% A graph-based material assignment 
+% reduction-simulation-optimization
+% Exploring the space of computational fabrication algorithms
 
@@
 In this paper we introduce Spec2Fab, a graph based framework that simplifies the design, development and implementation of these algorithms.
-We illustrate the utility of our framework by
-showing implemented fabrication algorithms as well as their manufactured results. 
+We illustrate the utility of our framework by showing implemented fabrication algorithms as well as their manufactured results.
 \end{abstract}
@@
 \section{Introduction}
-Computational fabrication couples new digital manufacturing techniques with novel numerical algorithms to produce objects with remarkable physical characteristics.
+
+% Desktop Manufacturing is taking off
+% Stress multi-material 3D printing
+
+% The need
+% Users would like to specify high-level goals for the object rather the direct specification of materials
+% some examples:
+
+% There is already of number of algorithms for specific solutions. 
+% But each of them is custom, they are difficult to extend and modify, combine
+% There is a general structure of these algorithms that has gone exploited: reduction, optimization, simulation
+% This suggests that you can build a system for integrating/combining, but also exploring modifying individual pieces
+
+% In our framework, we propose an optimization component that
+% searches through the space of all possible device outputs
+% obtained by the simulator to nd the one that best reproduces
+% the desired object. Unfortunately, this search space
+% is usually high-dimensional. For example, when the printing
+% volume has N voxels and each of these voxels can be
+% assigned to one of M base materials, the search space
+% has NM dimensions. To overcome this problem, we reduce
+% the search space to a lower-dimensional space using
+% a reduction model.
+
+% In this paper we propose a system (that exploits this structure) for building algorithms that compute optimal material assignment for computational fabrication
+% this build around two data-strictures: the reducer network (parameterizing the space of material assignments)  and the tuner network (the data structure for specifying the optimization).
+We also have an API.
+
+%Computational fabrication couples new digital manufacturing techniques with novel numerical algorithms to produce objects with remarkable physical characteristics.
 These methods are of great interest in computer graphics for two reasons: First, they provide us with  a new class of output devices which can render into real-life and second, they yield valuable insight into the accuracy of our numerical models of the world.
 
-In this paper we focus on a fundamental problem in producing any such custom object:  optimal material assignment.
+%In this paper we focus on a fundamental problem in producing any such custom object:  optimal material assignment.
 Given an object one must find a spatially varying material distribution that satisfies some given criteria.
@@
 \section{Related Work}
+
+% Computational Fabrication
+% BRDFs: Weyrich, Matusik, 
+% Refractive: Papas, Architectural Caustics, Finsch
+% Subsurface Scattering: Dong, Hasan
+% Shadows: Pauly (Shadow Art), ShadowPix
+% Deformation: Face Cloning, Balloons, Bickel
+% Albedo/Shading: Reliefs
+% Geometry compression: Digital Bas-Relief from 3D Scenes
+
+% Shade trees:
+% abstract shade trees
+% Yam, Siggraph Asia 2011
+
 Here we will review previous algorithms for solving the optimal material assignment problem .
@@
 \section{Contributions}
-The overall contribution of our work is a flexible framework for the construction of material assignment algorithms.
+The overall contribution of our work is a flexible framework for the construction of material assignment for computational fabrication algorithms.
 Our second contribution is the ``Reducer Network'',  a graphical data structure which describes both the geometric partitioning and material parameterization of  a given object.
@@
 Ultimately  we use these data structures to build an extensible, easy to use API which can produce numerous material assignment algorithms from a set of primitive operations.
+% 1. Flexible framework for material assignment
+% 2. Data structures
+% 3. API
 \section{Methods}

### 2013-01-11 paper.tex
intro

@@
 %\title{A Graph-Based Reduction for Optimal Material Assignment}
-\title{A reduced representation for computational fabrication}
+\title{A Reduced Representation for Computational Fabrication}
 % A reduced representation for computational fabrication
@@
 Computational fabrication problems are often concerned with optimal material assignment.
+
 They attempt to compute a spatially varying material distribution that yields specified real-world behavior.
+
 In this paper we introduce Spec2Fab, a graph based framework that simplifies the design, development and implementation of these algorithms.
+
 We illustrate the utility of our framework by showing implemented fabrication algorithms as well as their manufactured results.
+
 \end{abstract}
@@
 %\note{Teaser should be all different results produced using spec2Fab, texture, subsurface scattering, caustics etc...}
-
 \section{Introduction}
-
+% state of the world
 % Desktop Manufacturing is taking off
 % Stress multi-material 3D printing
+Computational design and 3D printing have been gaining attention among the general public but also within the computer graphics community.
+Computational design methods allow a wider audience to create custom objects and parts.
+These created designs can be automatically fabricated using a number of different 3D printing technologies.
+The range of the printing materials constantly expands and it is now possible to create and fabricate heterogeneous objects that combine a number of different materials.
 
-% The need
+% transitioning to the need
+When designing multi-material objects to be fabricated, users have to directly provide a material for each point inside of the object volume.
+In practice, an object is described using a collection of meshes, where each mesh is assigned a desired printing material.
+This process can be in many cases non-intuitive and users need to have access to all printing materials to ensure that the physical object looks and behaves the way they want.
+Even more importantly, objects are designed for a specific 3D printer and a set of materials. There is currently no way to translate between different printer-specific designs.
+
+% the need
 % Users would like to specify high-level goals for the object rather the direct specification of materials
 % some examples:
+There is a need to for a computationally efficient and general process that translates virtual objects specified in device-independent manner in terms of their mechanical and appearance properties to output-device-specific computer programs that produce the best possible approximation of these digital objects.
+Specifying objects in terms of their physical properties, for example, albedo values, rather than specific materials is much more user-intuitive.
+However, this is still one of the most important unsolved problems in digital direct manufacturing.
 
+% Other approaches
 % There is already of number of algorithms for specific solutions.
 % But each of them is custom, they are difficult to extend and modify, combine
+Computer graphics researchers have started designing algorithms for specific instances of this process, for example, subsurface scattering~\cite{Hasan:2010,Dong:2010} or deformation properties~\cite{Bickel:2010}.
+However, each of these instances is custom and difficult to extend or modify.
+Combining different process instances, e.g., designing and fabricating an object that has both desired reflectance and deformation is currently not possible.
+
 % There is a general structure of these algorithms that has gone exploited: reduction, optimization, simulation
 % This suggests that you can build a system for integrating/combining, but also exploring modifying individual pieces
+We observe that all these process instances share a similar structure.
+They rely on the ability to accurately simulate the physical properties of an object given its geometry and material assignment.
+They use this simulation within the optimization framework to search the space of all possible material assignments in order to find the one that best reproduces the desired properties.
+Unfortunately, due to the combinatorial nature of the search space the naive optimization approach is not tractable.
+For example, when the printing volume has $N$ voxels and each of these voxels can be assigned to one of $M$ base materials, the search space has $N^M$ dimensions.
+To overcome this problem, the search space is reduced to a lower-dimensional space using a reduction model.
+The goal of the reduction step is to shrink the search space as much as possible without pruning out good solutions.
 
-% In our framework, we propose an optimization component that
-% searches through the space of all possible device outputs
-% obtained by the simulator to nd the one that best reproduces
-% the desired object. Unfortunately, this search space
-% is usually high-dimensional. For example, when the printing
-% volume has N voxels and each of these voxels can be
-% assigned to one of M base materials, the search space
-% has NM dimensions. To overcome this problem, we reduce
-% the search space to a lower-dimensional space using
-% a reduction model.
+The reduction-optimization structure suggests that it is possible to provide a more general abstraction mechanism for translating specifications to fabrication instructions.
+In this paper we take the first step in achieving this goal.
+In particular, we and focus on the solution for building algorithms that compute optimal material assignment.
+Our solution is built around two data structures.
+The reducer network is graph-based framework that allows us to parameterize the spaces of material assignments.
+The tuner network is a data structure for specifying the optimization process.
+Our solution also provides an API that for intuitively specifying the desired object, the simulation, and these two data structures.
+Our approach has a number of advantages: different components of the process can be easily replaced, components can be reused across different, different parameterizations of the material domain and optimization strategies can be easily explored.
+
+We show that this framework supports a number of different computational design and fabrication scenarios.
+We demonstrate the results of these algorithms and we also demonstrate that different specifications can be combined.
 

### 2013-01-11 paper.tex
abstract

@@
 \begin{abstract}
-Computational fabrication problems are often concerned with optimal material assignment.
-
-They attempt to compute a spatially varying material distribution that yields specified real-world behavior.
-
-In this paper we introduce Spec2Fab, a graph based framework that simplifies the design, development and implementation of these algorithms.
-
-We illustrate the utility of our framework by showing implemented fabrication algorithms as well as their manufactured results.
-
+Digital fabrication allows to virtually design objects and then translate them to the corresponding physical equivalents.
+With the increasing popularity of multi-material 3D printing, these objects can be composed from multiple materials that have different properties.
+A key computational problem is how to compute a spatially varying material distribution that yields specified real-world behavior of the object.
+During the last few years a number of instances of this problem have been examined that tackle different aspects of object behavior, e.g.,  appearance or elastic deformation.
+In this paper, we propose an abstraction mechanism that simplifies the design, development, and implementation of these processes.
+Our solution relies on two data structures: a graph-based reducer network that efficiently parameterizes the space of material assignments and a tuner network that describes the optimization process to achieve desired material assignment.
+A corresponding API provides a natural way of specifying user-defined translation processes and the desired object.
+We illustrate the utility of our framework by showing implemented fabrication algorithms as well as the corresponding manufactured results.
 \end{abstract}

### 2013-01-12 paper.tex
related work

@@
 \begin{abstract}
-Digital fabrication allows to virtually design objects and then translate them to the corresponding physical equivalents.
+Digital fabrication allows us to virtually design objects and then translate them to their corresponding physical equivalents.
 With the increasing popularity of multi-material 3D printing, these objects can be composed from multiple materials that have different properties.
-A key computational problem is how to compute a spatially varying material distribution that yields specified real-world behavior of the object.
+Computing a spatially varying material distribution that yields specified real-world behavior of the object when manufactured, is a key problem.
 During the last few years a number of instances of this problem have been examined that tackle different aspects of object behavior, e.g.,  appearance or elastic deformation.
@@
 These created designs can be automatically fabricated using a number of different 3D printing technologies.
-The range of the printing materials constantly expands and it is now possible to create and fabricate heterogeneous objects that combine a number of different materials.
+The range of the printing materials constantly expands and it is now possible to fabricate heterogeneous objects that combine a number of different materials.
 
 % transitioning to the need
-When designing multi-material objects to be fabricated, users have to directly provide a material for each point inside of the object volume.
+When designing fabricable multi-material objects, users have to directly specify materials for each point inside of the object volume.
 In practice, an object is described using a collection of meshes, where each mesh is assigned a desired printing material.
-This process can be in many cases non-intuitive and users need to have access to all printing materials to ensure that the physical object looks and behaves the way they want.
-Even more importantly, objects are designed for a specific 3D printer and a set of materials. There is currently no way to translate between different printer-specific designs.
+This process can be, in many cases, non-intuitive requiring that users understand the properties of printing materials in order to obtain the desired results.
+Even more importantly, objects are designed for a specific 3D printer and a set of materials.
+There is currently no way to convert between different printer-specific designs.
 
@@
 % some examples:
-There is a need to for a computationally efficient and general process that translates virtual objects specified in device-independent manner in terms of their mechanical and appearance properties to output-device-specific computer programs that produce the best possible approximation of these digital objects.
+% users need to specify things in a functional manner,
+% it is difficult to make new algorithms because they are monolithic, no code reuse,
+There is a need for a computationally efficient and general process that translates virtual objects specified in device-independent manner in terms of their mechanical and appearance properties to output-device-specific computer programs that produce the best possible approximation of these digital objects.
 Specifying objects in terms of their physical properties, for example, albedo values, rather than specific materials is much more user-intuitive.
-However, this is still one of the most important unsolved problems in digital direct manufacturing.
+% Developers needs
+However, this is still one of the most important unsolved problems in digital manufacturing.
 
@@
 % But each of them is custom, they are difficult to extend and modify, combine
-Computer graphics researchers have started designing algorithms for specific instances of this process, for example, subsurface scattering~\cite{Hasan:2010,Dong:2010} or deformation properties~\cite{Bickel:2010}.
+Computer graphics researchers have started designing algorithms for specific instances of this process, for example, subsurface scattering~\cite{Hasan:2010:PRO,Dong:2010:FSS} or deformation properties~\cite{Bickel:2010:DAF}.
 However, each of these instances is custom and difficult to extend or modify.
@@
 In this paper we take the first step in achieving this goal.
-In particular, we and focus on the solution for building algorithms that compute optimal material assignment.
-Our solution is built around two data structures.
-The reducer network is graph-based framework that allows us to parameterize the spaces of material assignments.
-The tuner network is a data structure for specifying the optimization process.
-Our solution also provides an API that for intuitively specifying the desired object, the simulation, and these two data structures.
-Our approach has a number of advantages: different components of the process can be easily replaced, components can be reused across different, different parameterizations of the material domain and optimization strategies can be easily explored.
-
-We show that this framework supports a number of different computational design and fabrication scenarios.
-We demonstrate the results of these algorithms and we also demonstrate that different specifications can be combined.
-
-% In this paper we propose a system (that exploits this structure) for building algorithms that compute optimal material assignment for computational fabrication
-% this build around two data-strictures: the reducer network (parameterizing the space of material assignments)  and the tuner network (the data structure for specifying the optimization).
-We also have an API.
-
-%Computational fabrication couples new digital manufacturing techniques with novel numerical algorithms to produce objects with remarkable physical characteristics.
-These methods are of great interest in computer graphics for two reasons: First, they provide us with  a new class of output devices which can render into real-life and second, they yield valuable insight into the accuracy of our numerical models of the world.
-
-%In this paper we focus on a fundamental problem in producing any such custom object:  optimal material assignment.
-Given an object one must find a spatially varying material distribution that satisfies some given criteria.
-The algorithms that solve these problems are often complicated to develop, implement, test and modify.
-We provide a new graph-based framework which decomposes such problems into a small set of constituent components alleviating the above issues as well as facilitating the development and testing of new methods.
+In particular, we focus on the solution for building algorithms that compute optimal material assignment.
+Our solution entails two data structures.
+The \emph{reducer network} is a graph-based data structure that allows us to parameterize the space of material assignments.
+The \emph{tuner network} is a data structure for specifying the optimization process.
+Our solution also provides an easy to use API for specifying the desired object, setting up the simulation, and defining parameters for the reducer and tuner network.
+In general, our framework simplifies the construction of new computational fabrication algorithms.
+More specifically, different components of the process can be easily replaced, components can be reused across different processes, different parameterizations of the material domain and optimization strategies can be easily explored.
+In order to show these advantages, we illustrate how existing computational design processes fit in this framework and how they can be combined.
+We demonstrate the results of these algorithms on a variety of different examples.
 
 \section{Related Work}
-
-% Computational Fabrication
-% BRDFs: Weyrich, Matusik,
-% Refractive: Papas, Architectural Caustics, Finsch
-% Subsurface Scattering: Dong, Hasan
-% Shadows: Pauly (Shadow Art), ShadowPix
-% Deformation: Face Cloning, Balloons, Bickel
-% Albedo/Shading: Reliefs
 % Geometry compression: Digital Bas-Relief from 3D Scenes
@@
 
-Here we will review previous algorithms for solving the optimal material assignment problem .
-We divide this review into two broad categories, optimizing for desired optical properties and optimizing for desired mechanical properties.
-We conclude by commenting on the similarities between these approaches.
+Many instances of the computational design pipeline have been proposed recently.
+They span a wide range of functional properties (e.g., mechanical, optical, appearance).
+These properties drive the simulation, optimization, and reductions.
+In the area of computational design of objects with desired mechanical properties, Bickel and colleagues~\shortcite{Bickel:2010:DAF} have designed a system for manufacturing multi-layer composites with a given elastic behavior.
+Skouras et al.~\shortcite{sko:2012} provide design and construction of balloons with a prescribed shape while inflated.
+Furthermore, material optimization has been employed to create mechanical clones of human faces ~\cite{Bickel:2012}.
 
-Optimizing and manufacturing objects with desired optical characteristics is a popular problem in computer graphics.
-Building objects which embed images in their caustics has been explored by Finch \textit{et al.} ~\shortcite{Finckh:2010} and Papas \textit{et al.}\shortcite{Marios:2011}.
-Optimization based approaches have also been employed to control the subsurface scattering of printed 3D models ~\cite{Hasan:2010}.
-These methods have also been extended to optically decrypt hidden images ~\cite{Papas:2012}.
-Finally, optimal shadow casting surfaces have been produced which emulate a given set of input images ~\cite{Bermano:2012}.
+Optimizing and manufacturing objects with desired appearance and optical characteristics have been also explored.
+Weyrich et al.~\shortcite{Weyrich:2009:FMF} compute surface micro-geometry that yields a desired BRDF.
+Similar approaches have been proposed~\cite{Finckh:2010,Marios:2011} to produce refractive surfaces that form desired caustics.
+These methods have been extended to optically decrypt hidden images~\cite{Papas:2012}.
+Complementary work examines fabricating surfaces with spatially varying reflectance~\cite{Matusik:2009:PSR,Malzbender:2012:PRF} and diffuse shading \cite{Alexa:2010:RAI}.
+Another set of approaches uses optimization to compute shadow casting surfaces and volumes~\cite{Mitra:2009:SA,Bermano:2012,Baran:2012:MLA} to reproduce a given set of input images.
+Finally, optimization-based approaches have also been employed to control the subsurface scattering of 3D printed multi-layered models~\cite{Dong:2010:FSS,Hasan:2010:PRO}.
 
-Fabricating objects with desired mechanical characteristics has been explored less in the literature.
-Some recent examples include simulating and manufacturing layered composites ~\cite{Bickel:2010} as well as the design and construction of balloons with a prescribed shape while inflated ~\cite{sko:2012}.
-Finally, material optimization has been employed to create mechanical clones of human faces ~\cite{Bickel:2012}.
+Our reducer network is inspired by Cook's shade trees~\cite{Cook1984} data structure and their modern implementation in current rendering systems (e.g., Maya, RenderMan, etc.).
+Using these approaches, complex shading effect can be achieved by combining a set of basic shading blocks.
+Our reducer network also uses a tree data structure that combines a set of primitives to compute a material assignment for each point inside of the object volume.
 
-\autoref{tb:algorithms} shows the coordinate reduction methods as well as the optimization schemes used in all cited works.
+Our tuner network is inspired by probabilistic graphical models~\cite{Jordan:1999} that have been popular for representing variable dependence in multi-variable optimization problems.
+These problems can be parallelized~\cite{GraphLab} according to the graph structure representing variable dependencies.
+
+%The user can define a graph s
+%Similar approaches have already proven useful for creating complex texture shading examples ~\cite{Cook1984}.
+Our goal in this paper is to produce an analogous mechanism for material assignment problems.
+
+%\autoref{tb:algorithms} shows the coordinate reduction methods as well as the optimization schemes used in all cited works.
 A motivating observation for this research is that, despite different applications, these previous works share, not only a common methodology, but a set of common reduced coordinate components.
@@
 This suggests that one could find a small set of components that can be tied together to synthesize existing and new methods.
-Similar approaches have already proven useful for creating complex texture shading examples ~\cite{Cook1984}.
-Our goal in this paper is to produce an analogous mechanism for material assignment problems.
+
 \begin{table*}[htp]
@@
 \hline
-~\cite{Bickel:2010}& Deformation & Layered Materials  & Branch and Bound \\
+~\cite{Bickel:2010:DAF}& Deformation & Layered Materials  & Branch and Bound \\
 ~\cite{Finckh:2010} & Optical (Caustics) & B-Spline Surface & SPSA \\
-~\cite{Hasan:2010}& Optical (Subsurface) & Layered Materials & Branch and Bound\\
+~\cite{Hasan:2010:PRO}& Optical (Subsurface) & Layered Materials & Branch and Bound\\
 ~\cite{Marios:2011} & Optical (Caustics) & Piecewise Constant Tiles & Simulated Annealing \\
@@
 Finally, we will detail the basis set of components that we use to produce a wide-range of fabrication algorithms.
+
 \subsection{The Reducer Network}
@@
 \section{Results and Discussion}
+\autoref{tb:algorithms} shows the coordinate reduction methods as well as the optimization schemes used in all cited works.
+A motivating observation for this research is that, despite different applications, these previous works share, not only a common methodology, but a set of common reduced coordinate components.
+These, in conjunction with (often off-the-shelf) optimization techniques form new material assignment algorithms.
+This suggests that one could find a small set of components that can be tied together to synthesize existing and new methods.
+
 Table~\ref{tab:built-in} shows a list of nodes implemented in our framework.
@@
 \subsection{Subsurface Scattering}
-We replicated \cite{Hasan:2010} using our framework.
+We replicated \cite{Hasan:2010:PRO} using our framework.
 
@@
 \subsection{Subsurface Scattering and Deformation}
-We first replicated \cite{Bickel:2010} to print materials with specified elasticity. We then combined it with subsurface scattering
+We first replicated \cite{Bickel:2010:DAF} to print materials with specified elasticity. We then combined it with subsurface scattering
 matching to print material that approximates both the subsurface scattering property and the deformation behavior.

### 2013-05-03 thesis/1_cover.tex
add tex files

%%
%% MIT Thesis - Title Page
%%

\thispagestyle{empty}

\begin{centering}
\rule{\textwidth}{.05in}\\ \vspace{.10in}

\Large \textbf{\textsf{ Spec2Fab: A Reducer-Tuner Model for Translating Specifications to 3D Prints
}} \\
\normalsize

\vspace{.1in}
by \\

\vspace{.1in}
Donglai Wei \\

\vspace{.1in} B.S., Computer Science,
Carnegie Mellon University, 2011 \\

\vspace{.0in} S.M., Electrical Engineering and Computer Science,
M.I.T., 2013 \\

\vspace{.1in}
\rule{\textwidth}{.05in}\\

\vspace{.2in}

Proposal for Thesis Research in Partial Fuillment\\
of the requirements for the degree of Master of Science\\

\vspace{.15in}

\vspace{.1in} March 2015

\vspace{.15in} \copyright\ 2015
Massachusetts Institute of Technology \\
All Rights Reserved. \\

\end{centering}

\vspace{.3in}

\noindent
Signature of Author: \underline{\mbox{\hspace{4.28in}}} \\
\vspace{-.25in}
{\flushright Department of Electrical Engineering and Computer Science \\
March 18, 2015\\
}

\vspace{.15in}

\noindent
Certified by: \underline{\mbox{\hspace{4.827in}}} \\
\vspace{-.25in}
{\flushright Your first supervisor's name here \\
Title of supervisor, e.g., Professor of Electrical Engineering and Computer Science \\
Thesis Supervisor \\
}

\vspace{.15in}

\noindent
Certified by: \underline{\mbox{\hspace{4.827in}}} \\
\vspace{-.25in}
{\flushright Your second supervisor's name here \\
Title of supervisor, e.g., Professor of Electrical Engineering and Computer Science \\
Thesis Supervisor \\
}

\vspace{.15in}

\noindent
Accepted by: \underline{\mbox{\hspace{4.79in}}} \\
\vspace{-.25in}
{\flushright Leslie A.~Kolodziejski \\
Professor of Electrical Engineering and Computer Science \\
Chair, Committee for Graduate Students \\
}

\cleardoublepage

### 2013-05-03 thesis/1_cover_thesis.tex
add tex files

--- 2013-05-03 thesis/1_cover.tex
@@
 
-\Large \textbf{\textsf{ Spec2Fab: A Reducer-Tuner Model for Translating Specifications to 3D Prints
+\Large \textbf{\textsf{ Your title goes here
 }} \\
@@
 \vspace{.1in}
-Donglai Wei \\
+Your name goes here \\
 
-\vspace{.1in} B.S., Computer Science,
-Carnegie Mellon University, 2011 \\
+\vspace{.1in} B.S., Electrical Engineering,
+some other school, 2010 \\
 
 \vspace{.0in} S.M., Electrical Engineering and Computer Science,
-M.I.T., 2013 \\
+M.I.T., 2012 \\
 
@@
 
-Proposal for Thesis Research in Partial Fuillment\\
-of the requirements for the degree of Master of Science\\
+Submitted to the Department of Electrical Engineering and Computer Science \\
+in partial fulfillment of the requirements for the degree of \\
 
 \vspace{.15in}
+
+Doctor of Philosophy \\ % <--- replace this with Master of Science if you want a master's instead
+in Electrical Engineering and Computer Science \\
+at the Massachusetts Institute of Technology \\
 

### 2013-05-03 thesis/DataStructures.tex
add tex files

\chapter{Data Structures}
\label{chap:struct}
In this section, I describe the structure of the \emph{reducer tree} as well as all types of \emph{reducer nodes} implemented in our framework. We also show the structure of individual \emph{tuners} and how they can be arranged into the \emph{tuner network}.

\section{The Reducer Tree}
 Estimating material assignments at output device resolution is computationally intractable. Therefore, material assignment has to be computed using a reduced representation. We specify this representation using a \emph{reducer tree}. This structure is conceptually similar to those used in programmable shading systems (such as Cook's shade trees~\shortcite{Cook1984} or Maya Shader Networks). These systems are primarily concerned with assigning known materials and textures to an object's surface whereas we are seeking an optimal volumetric assignment from a defined set of materials. In order to accomplish this task, we build a tree-based data structure which contains the entire object volume as its root node. We define two classes of \emph{reducer nodes}: \emph{geometry nodes} and \emph{material nodes}.

\paragraph{Geometry Nodes:}A \emph{geometry node} takes a volumetric region as input and produces a partition of this region into smaller sub-regions. 
These can be attached to the object geometry or they can be defined in a global coordinate system.
To demonstrate the flexibility of the \emph{reducer tree}, we define a small yet powerful set of partitioning nodes which are described as follows %used in our prototype
 (\autoref{fig:geometryNodes}):\vspace{-0.25\baselineskip}
\begin{itemize}
\item Plane Node --  partitions the space into two half-spaces, \vspace{-0.25\baselineskip}
\item Column Node -- takes as input the number of columns and accordingly partitions the space,\vspace{-0.25\baselineskip}
\item Voxel Node -- takes as input voxel size and uniformly partitions the space,\vspace{-0.25\baselineskip}
\item B-spline Node -- partitions a volume into two regions cut by a B-spline,\vspace{-0.25\baselineskip}
\item Stratum Node -- takes a single positive distance parameter as an input and partitions the volume into two regions divided by the iso-distance surface.\vspace{-0.25\baselineskip}
\end{itemize}

\begin{figure}
\includegraphics[width=0.7\linewidth]{figure/geometryNodes}
\caption{2D representations  of the \emph{geometry nodes} used in our \emph{reducer tree}.}
\label{fig:geometryNodes}
\end{figure}

\paragraph{Material Nodes:} The \emph{leaf nodes} of the \emph{reducer tree} are the material parameterization nodes. These contain a material assignment function $\lambda\left(x\right)$ that maps spatial coordinates to materials. We allow our \emph{material nodes} to assign a void material to regions of the volume. Hence, surface displacements and material assignments can be treated in a unified fashion.
While \emph{material node} can be extended to implement arbitrary material assignment functions (such as Functionally Graded Materials), all the following results require only a single type of \emph{material node}, \emph{layered node}, which assigns $k$ material layers of varying thickness to a geometry partition. We can even assign a constant material to a region using a \emph{layered node} with a single layer.

\emph{Geometry nodes} and \emph{material nodes} can be connected into a tree structure that describes a material assignment function throughout the input geometry. 
The essential property of this data structure is that it naturally adapts to the input geometry. This key feature allows it to be reused for different shapes.
\autoref{fig:red1} shows two examples of \emph{reducer trees} and the resulting geometric distributions of materials.
Since the tree describes a nested set of partitions, we can efficiently perform material queries by passing a query point through the tree until it arrives at a parameterization node. 
We note that the \emph{reducer tree} does not inherently enforce material continuity between disjoint regions of the object; however, for material assignment problems, this is neither required nor desired.

\begin{figure}[h]
\includegraphics[width=0.7\linewidth]{figure/redNetworkNew.pdf}
\caption{Two examples of our \emph{reducer tree}. Left: in order to create an object producing a caustic, the input shape is first divided into columns. Next, each column is sliced by a plane.
By assigning materials to lower parts of the columns, the microfacet surface is created.
Right: a textured object with subsurface scattering properties is produced by first dividing the input shape using a \emph{stratum node}. Then, the outer layer is sliced into columns, which create a texture once materials are assigned. The inner part of the object obtains a material with given subsurface scattering properties.  
}
\label{fig:red1}
\end{figure}

\section{Tuners and Tuning the Reducer Tree}
We define \emph{tuners} as an abstract interface between a \emph{reducer node} and an optimization algorithm. 
A \emph{reducer node} has parameters that control its space partitioning and material composition, e.g., \emph{stratum node} has a parameter which determines its thickness, \emph{column node} has parameters that control the width of columns.
A \emph{tuner} is responsible for tuning these parameters to achieve a specified goal.
A \emph{tuner} is comprised of an optimization scheme, an error metric, a simulator and a goal (\autoref{fig:tuner0}). 
In order to create an optimal material assignment, \emph{tuner nodes} must be attached to the \emph{reducer tree}. The developer links each \emph{tuner} to a \emph{reducer node} in the \emph{reducer tree}. Each \emph{tuner} then traverses the \emph{reducer subtree} (rooted at this \emph{reducer node}) and constructs a parameter list by querying each visited \emph{reducer node}. The developer can label parameters as fixed or free. \emph{Tuner nodes} contain specific optimization routines (e.g., a quadratic program solver). The \emph{tuner node} then uses this routine to optimize its associated free parameters. During execution, additional information (e.g., parameters, errors, etc.) from neighboring Tuner Nodes can be obtained via the \emph{tuner network} (Section~\ref{sec:TunerNetwork}).  Tuner execution can be scheduled (again by the programmer) allowing both serial and parallel processing.

\autoref{fig:combine} (left) shows a simple example in which two \emph{tuners} are attached to sibling nodes in a \emph{reducer tree}. The first \emph{tuner} is responsible for \emph{layered} and \emph{void material nodes }while the second is responsible for several \emph{layered material nodes}.

\begin{figure}
\includegraphics[width=0.7\linewidth]{figure/tuner2.pdf}
\caption{A diagram of the \emph{tuner} workflow. Arrows indicate flow and type of information passed between the individual \emph{tuner} components.}
\label{fig:tuner0}
\end{figure}

\section{Tuner Network}
\label{sec:TunerNetwork}
For many fabrication problems, \emph{tuners} should not act in isolation. For instance, an optimal material assignment at a given point depends on the material assignment in the neighborhood. Tuning the free parameters without taking into account this dependency usually yields suboptimal results. Therefore, we allow the \emph{tuners} to share information according to a user-specified graph structure. This allows our framework to interface with a wide range of existing graph-based optimization and inference algorithms. For example, Figure~\ref{fig:combine} (right) shows one of the \emph{tuner networks} used in our experiments.
In this network, each node is connected to its four neighbors. In Figure~\ref{fig:ReducerTreesAdditional}, \emph{tuners} enclosed in dashed boxes are connected in this form. \emph{Tuner networks} do not always exhibit this regular connectivity. For instance, \emph{tuners} can be completely unconnected (\autoref{fig:combine} (left) or be organized into groups which feature intra- but not inter-group connections.

\begin{figure}[h]
\centering
\includegraphics[width=0.7\linewidth]{figure/tunedrt.pdf}
\caption{ 
	Left: Two \emph{tuners} attached to a \emph{reducer tree}. Each \emph{tuner} is responsible for tuning the nodes in its attached subtree (denoted by shapes with similarly colored outlines). 
	Right: One type of \emph{tuner network} used in our experiments.}
\label{fig:combine}
\end{figure}

### 2013-05-03 thesis/Overview.tex
add tex files

\chapter{Design Goals}
\label{chap:design}
The design of our general translational framework is guided by the following principles:

\begin{itemize}

\item \textbf{Modularity:} Spec2Fab translators are complicated both algorithmically and from a software engineering point of view. To combat this, any proposed framework must break the problem into a manageable number of small, reusable building blocks.

\item \textbf{Extensibility:} Developers must be able to add their own building blocks to the system. This allows the system to grow in conjunction with the capabilities of newer 3D printers.
\vspace{-0.25\baselineskip}

\item \textbf{Device Independence:} Spec2Fab translators should be device independent. They should be easily adaptable to different types of 3D printers.
\item \textbf{Input Geometry Independence:} Spec2Fab translators should be geometry independent. For example, a process for applying a texture to a 3D printed object should work for \textbf{any} object.
\vspace{-0.25\baselineskip}
\end{itemize}

We aim to separate the Spec2Fab process into two phases, the process configuration phase and the process use phase. The process configuration phase is typically done once by a skilled developer who  constructs a Spec2Fab translator. The process use phase is typically performed multiple times by an end-user who is only required to provide an object specification (e.g., object geometry and deformation properties) and a target device.

	The process configuration phase produces a Spec2Fab translator which will assign a desired volumetric material distribution to a user supplied input geometry given a user specified goal. We describe this phase using two new data structures, the \emph{reducer tree} and \emph{tuner network}. The \emph{reducer tree} parameterizes a volumetric material assignment using a small set of \emph{geometry} and \emph{material nodes} while the \emph{tuner network} is used to describe an optimization process as a connected set of \emph{tuner} objects.  Both \emph{nodes} and \emph{tuners} can be easily recombined and reused thus making  our framework highly modular. Furthermore,  \emph{nodes} and \emph{tuners} define abstract interfaces and thus developers can easily add new types of each. This makes our framework extensible.

	\emph{Reducers} and \emph{tuners} are chosen to be independant of printer capabilities. Instead we account for printer type by altering the available materials that the translator may assign to the input geometry.  This is important since it grants the \emph{reducer-tuner} model  device independence. Finally, the \emph{geometry nodes} of the \emph{reducer tree} are designed to function irrespective of input shape. Since the Spec2Fab translators produced by our algorithm use a composition of these node types, they are geometry independent.

	In the following sections I will describe the \emph{reducer tree} and the \emph{tuner network}, their constituent components and the mechanisms by which they interact.

### 2013-05-03 thesis/RelatedWork.tex
add tex files

\chapter{Related Work}
\label{chap:relate}
% Geometry compression: Digital Bas-Relief from 3D Scenes
\biglet{T}{he} new data structures draw ideas from previous work in rendering and optimization.
The \emph{reducer tree} is inspired by Cook's shade trees~\cite{Cook1984} and their modern implementation in current rendering systems (e.g., Maya, RenderMan, etc.). Using these approaches, complex effects can be achieved by combining a set of basic shading blocks. The \emph{reducer tree} also uses a tree data structure that combines a set of primitives to compute a material assignment for each point inside of an object volume and describes a spatial-partition of the object volume. While there are many space-partitioning data structures (BSPs, Quad-trees, KD-trees, etc.), they are difficult to specify by hand and they are typically tied to the object geometry. Our \emph{reducer tree} is intuitive to construct but sufficiently general for representing material distributions. In addition, it is specified in an object-independent manner -- the same \emph{reducer tree} can be reused for processing different objects. Our second, new data structure which is responsible for optimizing material assignment is the \emph{tuner network}. It is inspired by probabilistic graphical models~\cite{Jordan:1999} that have been popular for representing variable dependence in multi-variate optimization problems. These problems can be parallelized~\cite{GraphLab} according to the associated graph structure.

Our work is also inspired by the many instances of specification to fabrication translation pipelines that have been proposed recently. These pipelines span a wide range of functional goals (e.g., mechanical, optical, appearance). They drive the simulation, optimization, and reductions chosen for each method. 
One example of such processes is recent work on optimizing material composition to achieve prescribed deformation behavior. 
Bickel and colleagues~\shortcite{Bickel:2010:DAF} have designed a system for manufacturing multi-layer composites with a given elastic behavior.
 Skouras \textit{et al}.~\shortcite{sko:2012} provide design and construction of balloons with a prescribed shape while inflated. Furthermore, material optimization has been employed to create mechanical clones of human faces ~\cite{Bickel:2012}.

Optimizing and manufacturing objects with desired appearance and optical characteristics has also been explored. Weyrich \textit{et al}.~\shortcite{Weyrich:2009:FMF} compute surface micro-geometry that yields a desired BRDF. Similar approaches have been proposed~\cite{Finckh:2010,Marios:2011} to produce refractive surfaces that form user-defined caustics. These methods have been extended to optically decrypt hidden images~\cite{Papas:2012}. Complementary work examines fabricating surfaces with spatially varying reflectance~\cite{Matusik:2009:PSR,Malzbender:2012:PRF} and diffuse shading \cite{Alexa:2010:RAI}. Another set of approaches uses optimization to compute shadow casting surfaces and volumes~\cite{Mitra:2009:SA,Bermano:2012,Baran:2012:MLA} that reproduce a given set of input images. Finally, optimization-based approaches have also been employed to control the subsurface scattering of 3D printed multi-layered models~\cite{Dong:2010:FSS,Hasan:2010:PRO}. We seek to exploit the common form of the above works in order to generalize them.

There have been studies of material assignment representations in other fields, primarily in mechanical engineering. 
Here we only list a few representative works. Kumar \textit{et al}.~\shortcite{Kumar1999} describe material composition by dividing a volume into sub-volumes. They perform material interpolation  using local, sub-volume coordinate systems. 
Jackson ~\shortcite{Jackson2000} explores several mesh data structures for spatial sub-division. Kou and Tan~\shortcite{Kou2007} give a comprehensive review of spatial partition schemes and material interpolation functions. Kou \textit{et al}.~\shortcite{Kou2012} use a hierarchy of procedures to define material composition with a small number of design parameters. They run particle swarm optimization ~\cite{kennedy1995} on the design parameters to minimize thermal stress of an object. Their work focused on smoothly varying materials. There is no discussion of high-frequency discrete material assignment for capturing details. They are limited to global optimization algorithms such as Particle Swarm Optimization because the dependency structure between the design variables is not modeled.
In computer graphics, procedural descriptions for material assignment have also been studied.
Cutler \textit{et al}.~\shortcite{Cutler2002} describe a scripting language for specifying layered solid models and describing material composition. Vidim\v{c}e \textit{et al}.~\shortcite{Vidimce2013} provide a fabrication language and a programmable pipeline for specifying material composition directly and precisely throughout a volume. In contrast, Spec2Fab can be used to design algorithms that only require object properties rather than a precise description of material assignment.

In this work we focus on constructing a common model for encompassing the entire Spec2Fab problem. We are motivated by the similarities present in state-of-the-art algorithms.  \autoref{tb:algorithms} shows the coordinate reduction methods as well as the optimization schemes used in all these prior approaches. Our key observation is that previous works share a common methodology and  a common set reduced coordinate components. These components are then combined with (often off-the-shelf) optimization techniques to form new material assignment algorithms. This suggests that one could find a small set of components that can be tied together to synthesize  advanced methods. In this paper we attempt to identify these components as well as a suitable model for their interaction.

\begin{table*}[htp]
\centering
\begin{tabular}{clll}
\hline
\textbf{Paper} & \textbf{Goal} & \textbf{Reduced Coordinates}  & \textbf{Optimization} \\
\hline
~\cite{Finckh:2010} & Optical (Caustics) & B-Spline Surface & Stochastic Approximation \\
~\cite{Marios:2011} & Optical (Caustics) & Piecewise Constant Tiles & Simulated Annealing \\
~\cite{Alexa:2010:RAI}& Optical (Relief) & Height Field & Gradient Descent\\
~\cite{Weyrich:2009:FMF} &Optical (Reflectance)&Piecewise Constant Tiles& Simulated Annealing\\
~\cite{Papas:2012} & Optical (Refraction) & Piecewise Constant Tiles & Simulated Annealing \\
~\cite{Mitra:2009:SA}&Optical (Shadows)&Voxel Grid&Custom Discrete\\
~\cite{Baran:2012:MLA}&Optical (Shadows)& Layered Materials & Quadratic Program \\
~\cite{Bermano:2012} & Optical (Shadows) & Height Field & Custom/Simulated Annealing \\
~\cite{Dong:2010:FSS}&Optical (Subsurface) &Layered Materials&Conjugate Gradient\\
~\cite{Hasan:2010:PRO}& Optical (Subsurface) & Layered Materials & Branch and Bound\\
~\cite{Bickel:2010:DAF}& Mechanical (force) & Layered Materials  & Branch and Bound \\
~\cite{Bickel:2012} & Mechanical (shape) &  Height Field &  Newton-Raphson \\
~\cite{sko:2012}& Mechanical (shape) & Triangle Mesh & Augmented Lagrangian Method \\
\hline
\end{tabular}
\caption{The goal type, reduction type and optimization used by prior computational fabrication approaches.}
\label{tb:algorithms}
\end{table*}

### 2013-05-03 thesis/abstract.tex
add tex files

\chapter*{}
\label{chap:abstract}
\begin{center}
\vspace{-8em}
{\large \textsf{\textbf{Spec2Fab: A Reducer-Tuner Model for Translating Specifications to 3D Prints}}} \\
by (Desai Chen)

\vspace{.2in}

Submitted to the Department of Electrical Engineering and Computer Science \\
in partial fulfillment of the requirements for the degree of \\
Doctor of Philosophy \\ % <--- replace this with Master of Science if you want a master's instead
\end{center}

\noindent\textsf{\textbf{Abstract}}

\noindent Multi-material 3D printing allows objects to be composed of complex, heterogenous arrangements of materials. It is often more natural to define a functional goal than to define the material composition of an object. Translating these functional requirements to fabricable 3D prints is still an open research problem. Recently, several specific instances of this problem have been explored (e.g.,  appearance or elastic deformation), but they exist as isolated, monolithic algorithms. In this paper, we propose an abstraction mechanism that simplifies the design, development, implementation, and reuse of these algorithms. Our solution relies on two new data structures: a \emph{reducer tree} that efficiently parameterizes the space of material assignments and a \emph{tuner network} that describes the optimization process used to compute material arrangement. We provide an application programming interface for specifying the desired object and for defining parameters for the \emph{reducer tree} and \emph{tuner network}. We illustrate the utility of our framework by implementing several fabrication algorithms as well as demonstrating the manufactured results.

\noindent\rule[0.5ex]{2in}{1pt} \\
Thesis Supervisor: Your first advisor's name goes here \\
Title: Title of supervisor, e.g., Professor of Electrical Engineering and Computer Science

\vspace{.1in}

\noindent Thesis Supervisor: Your second advisor's name goes here \\
Title: Title of supervisor, e.g., Professor of Electrical Engineering and Computer Science

### 2013-05-03 thesis/chap1.tex
add tex files

%%
%% MIT Thesis - Chapter 1
%%

\renewcommand{\figdir}{figures/chap1}
%
\chapter{Introduction}
\label{chap:intro}
%
\biglet{3}{D} printing receives a lot of attention as it aims to democratize fabrication.
The ever expanding range of printing materials allows for fabrication of complex objects with spatially varying appearance, optical characteristics, and mechanical properties.
One of the most important unsolved problems in this area is how to compute an object's material composition from a functional or behavioral description. I will call this process \em specification to fabrication translation (Spec2Fab). 
The goal of this work is to provide a convenient abstraction for specifying such translators. This is necessary to move past the current direct specification model of 3D printing.

Today,  3D printing of an object requires a material be directly specified for each voxel inside the object volume. This approach is fraught with difficulties. First, 3D printable models become specific to a single printer type, i.e., the models are built from materials provided by a given printer. Consider the inconvenience that would result from  word processing documents being compatible with specific 2D printers. Second, working directly with printing materials rather than material properties is extremely challenging for users. Imagine the difficulty in finding the right combination of printing materials that would provide a specific color, stiffness, or refractive index.

Our work is motivated by the recent research efforts in the computer graphics community to create specific instances of the translation process, for example, subsurface scattering~\cite{Hasan:2010:PRO,Dong:2010:FSS} or deformation properties~\cite{Bickel:2010:DAF}. However, each of these instances is a custom, monolithic solution which is difficult to extend, combine, or modify. Our main insight is that all these process instances share a similar structure. First, they rely on the ability to accurately simulate the physical properties of an object given its geometry and material assignment. They use this simulation within an optimization framework to search the space of all possible material assignments in order to find the one that best reproduces the desired properties. Due to the combinatorial nature of the search space the naive optimization approach is not tractable. For example, when the printing volume has $N$ voxels and each of these voxels can be assigned to one of $M$ base materials, the search space has $N^M$ dimensions. To overcome this problem, the search space is reduced to a lower-dimensional space using a reduction model. The goal of the reduction step is to aggressively shrink the search space in a domain-specific manner such that it still contains good approximations to the optimal solution. This search space reduction combined with the right choice of the optimization algorithm delivers a computationally tractable approximation.

The reduction-optimization structure suggests that it is possible to provide a more general abstraction mechanism for translating 3D models to printer and material-specific representations. In this paper we take the first step in achieving this goal. Our solution relies on two novel data structures which are designed to aid the fabrication process. The \emph{reducer tree} is a tree-based data structure that allows us to parameterize the space of material assignments. The \emph{tuner network} is a data structure for specifying the optimization process. Our solution also provides an API for specifying the desired object, setting up the simulation, and defining parameters for the \emph{reducer tree} and \emph{tuner network}. In general, our framework simplifies the construction of new computational fabrication algorithms. More specifically, different components of the process can be easily replaced and other components easily reused. Various optimization strategies can also be explored with lower implementation burden. In order to show these advantages, we illustrate how existing computational design processes fit into this framework and how they can be combined. We demonstrate the results of these algorithms on a variety of different examples fabricated using 3D printers.

### 2013-05-03 thesis/Conclusion.tex
add chapters

\chapter{Conclusion}
In this proposal I have taken the first step towards solving an open problem in computational fabrication --  creating a general translation process that transforms user-defined model specifications into printer and material-specific representations. Our process relies on two data structures to make this general translation process expressive and computationally tractable: a \emph{reducer tree} and a \emph{tuner network}. We have shown how existing instances of this translation can be expressed and combined within our system. We believe that our API and its reference implementation will simplify and encourage development of new translation processes.

Our framework offers many exciting opportunities for future work. First, it would be extremely useful to implement many additional simulators in order to allow computing a variety of other properties, e.g., structural soundness, stability, material cost, and printing time. These simulators could be employed to expand the range of possible user-defined specifications. Similarly, only relatively simple error metrics have been tested within the tuning process. The development of more sophisticated and, in particular, perceptually-driven material metrics remains a relatively unexplored research area. Finally, it would be very beneficial to couple our API with a visual interface to further simplify the task of translator construction. It is not obvious what the best visual interface for specifying functional or physical properties of these objects is and more research in this area is necessary.

### 2013-05-03 thesis/DataStructures.tex
center diagram
add chapters

@@
 \label{chap:struct}
-In this section, I describe the structure of the \emph{reducer tree} as well as all types of \emph{reducer nodes} implemented in our framework.
+\biglet{I}{n} this section, I describe the structure of the \emph{reducer tree} as well as all types of \emph{reducer nodes} implemented in our framework.
 We also show the structure of individual \emph{tuners} and how they can be arranged into the \emph{tuner network}.
@@
 
-\begin{figure}
+\begin{figure}[h]
+\centering
 \includegraphics[width=0.7\linewidth]{figure/geometryNodes}
@@
 \begin{figure}[h]
+\centering
 \includegraphics[width=0.7\linewidth]{figure/redNetworkNew.pdf}
@@
 
-\begin{figure}
+\begin{figure}[h]
+\centering
 \includegraphics[width=0.7\linewidth]{figure/tuner2.pdf}

### 2013-05-03 thesis/Results.tex
add chapters

\chapter{Proposed Experiments}
\label{chap:results}
\begin{figure*}[t]
\includegraphics[width=\linewidth]{figure/TexturedExamples.pdf}
\caption {The reducer-tuner model should enable creating objects of arbitrary shapes with embedded textures.}
\label{fig:texturedExamples}
\end{figure*}
\biglet{I}{n} order to evaluate capabilities of our system, I will implement a number of existing translation processes.
Furthermore, the ease with which different algorithm components can be combined enabled creation of two new translation processes.
The first is an algorithm that can produce objects with desired refractive properties and an associated texture.

The second allows us to apply a desired texture to an object with prescribed deformation behavior.
All of these processes, both from prior work and new ones, easily fit into our framework, and were manufactured using a Stratasys Object500 Connex  multi-material printer.
The following paragraphs provide a detailed description of how the individual algorithms were designed with our system.
All \emph{reducer trees} and the \emph{tuner networks} used for producing these results are presented in \autoref{fig:ReducerTreesAdditional}.

\paragraph{Spatially-varying Albedo:}
We have designed a Spec2Fab translator that allows for 3D printing of textured models (Figure~\ref{fig:texturedExamples}).
Being able to apply precisely specified spatially-varying albedo values to printed models is a crucial capability.
However, no standard processes have been designed for this task so far. The input to our algorithm is a shape and its desired albedo texture. Since the texture is only affected by materials close to the surface, we use a \emph{stratum node} to divide the input shape into a thin shell and an inner volume. We then divide the outer layer into columns. The set of printable colors is expanded by stacking translucent materials using the \verb|LayeredMaterial| Node.
The number of layers is fixed to the number of print materials. The reduced parameters are the thickness values of each material layer. For each column, the \emph{tuner}'s optimizer looks up the proper stacking that produces the closest albedo value. Due to printer resolution, the range of albedo values that can be achieved is quantized. We therefore implement an error diffusion algorithm by connecting neighboring \emph{tuners}. In this simple algorithm, the simulation is a table lookup -- we measure the albedo value corresponding to different base materials.

\paragraph{Heterogeneous Subsurface Scattering:}
We have replicated the subsurface scattering process of Ha\v{s}an et al.~\shortcite{Hasan:2010:PRO} using our framework (Figure~\ref{fig:sub}).
The input to our algorithm is a 3D mesh along with subsurface-scattering profiles defined at a set of surface points. We use the same \emph{reducer tree} as in the texture example thereby simplifying the process configuration phase.
The only difference is that we allow each column to have four layers of varying thickness and material. We use a branch and bound optimization algorithm which has been modified to handle continuous parameters by allowing discrete increments. We implement a bound estimate callback function specific to this problem.
Each column is optimized independently using the algorithm. The simulation computes a scattering profile for given a stacking and the error metric compares the simulated and goal profiles using squared error.
%We note that the ability to reuse Reducer Nodes simplifies the configuration of new processes.

\begin{figure}
\centering
\includegraphics[width=0.65\linewidth]{figure/fig_chess.pdf}
\caption{
	A marble chessboard with prescribed subsurface scattering properties.
	The insets show the samples under thin line illumination, and the graph shows the convergence of tuners for 10 out of 100 scattering profiles used in the example. The error is measured by square distance between two profiles, each containing 400 coefficients.}
\label{fig:sub}
\end{figure}

\paragraph{Goal-based Caustics:}
We have configured two different processes for computing goal-based caustics (Figure~\ref{fig:caust2}). While they define exactly the same goal, they have very different \emph{reducer trees} and \emph{tuner networks}.
The first process is based on the work of Papas et al.~\shortcite{Marios:2011}. It computes a set of micro-lenses which produce the desired caustic image. The image is pre-processed into a set of Gaussian distributions. Each distribution is matched with a microlens. The optimization applies simulated annealing to permute the location of these micro-lenses in order to construct a smooth surface. In the \emph{tuner network}, each \emph{tuner} is connected to its four neighbors. During the execution of an individual \emph{tuner}, the optimization algorithm makes a randomized decision about whether or not to swap its micro-lens with one of its neighbors based on smoothness of the surface. The \emph{tuners} are executed many times until a user-specified convergence criterion is met. In our examples, we use $45^2$ microlens and ran all the \emph{tuners} for $2000$ iterations. In the second process, based on the work of Finckh et al.~\shortcite{Finckh:2010}, we use a \emph{B-spline node} to represent a smooth caustic surface. This is in contrast to the potentially discontinuous surface in the method above. The reduced parameters are the height of each spline control point. We implement a simple caustics simulator for height fields. The simulated image is compared to the goal image using mean squared error. We used $60\times 60$ control points and render the simulated image at $240\times 240$ pixel resolution.

\begin{figure}
\centering
\includegraphics[width=0.65\linewidth]{figure/fig_caustic.pdf}
\caption {3D printed lens arrays that each produce a caustic image of Einstein.
Below we show convergence plots for both the microfacet and smooth surface optimizations.
The portrait is available from the United States Library of Congress's Prints and Photographs division,
now in the public domain.
}
\label{fig:caust2}
\end{figure}
%\vspace{-\baselineskip}

\paragraph{Elastic Behavior:}
In the spirit of Bickel et al.~\shortcite{Bickel:2009} we have implemented an algorithm to compute material distribution based on a desired force-displacement response. The input to this algorithm is a mesh, a simulation configuration, and a desired shape. Simulation configuration includes vertex constraints and forces applied to the mesh. For this example, we use a co-rotational finite element method (FEM) simulation with linearly elastic materials to estimate the objects deformation. For the \emph{reducer tree}, we use a voxel partition to divide the object into a low-resolution grid. We assign a single material to each grid cell. The FEM simulator queries the \emph{reducer tree} for material assignments at arbitrary spatial locations. We use the same branch and bound algorithm as in our subsurface-scattering process but with a different bound computation callback function. We use the mean squared distance between the simulated and the desired shapes as the error metric. We have designed a simple experiment to validate our process in which we set the goal of our optimization to be a given deformed state (\autoref{fig:book}).

\begin{figure}
\centering
\includegraphics[width=0.65\linewidth]{figure/fig_sub.pdf}
\caption {A 3D printed book with prescribed deformation behavior under load.
The plot shows the error (in meters) as a function of iteration number of our branch and bound based \emph{tuner}.
The blue line shows the smallest error seen so far while the red line the \emph{tuner}'s progress exploring material subtrees~\protect\cite{Bickel:2009}.}
\label{fig:book}
\end{figure}

\paragraph{Combining Caustics and Spatially-varying Albedo:}
The first of our new combined translation processes incorporates both smooth caustics and texture mapping. More specifically, we compute a transparent slab with a texture image that, when illuminated, casts a prescribed caustic image. The input slab is split into two pieces using a \emph{plane node} as shown in Figure~\ref{fig:ReducerTreesAdditional}.
The top piece is tuned to produce an input image. The material in the top piece is then fixed. The bottom piece is then tuned to produce a caustics image.

\paragraph{Combining Deformable Object and Spatially-varying Albedo:}
Our second new process combines spatially-varying albedo and elastic deformation properties. This is a very useful combination since when modeling objects we would like to specify both their appearance and ``feel''. In this process, the input shape is divided into a thin shell and an inner volume. We optimize for the deformation behavior and the texture independently due to the limitations of our current FEM simulator. As the outer shell is very thin, it has negligible influence on overall object deformation.

\begin{figure*}[t]
\centering
\includegraphics*[clip, width = \linewidth]{figure/ReducerNetworksSuplemental}
\caption{The figure shows all \emph{reducer trees} used in this paper.
\textbf{Smooth caustics:} The smooth caustics tree consists of a spline surface that divides the geometry into an inner surface filled with a transparent material and an outer, void surface. This allows us to approximate displacement mapping.  Here, a single \emph{tuner} is used deform the spline surface.
\textbf{Smooth caustics/texture:} The smooth caustics/texture \emph{reducer tree} splits the object into upper and lower sections using a plane. The upper section then uses the Smooth caustics \emph{reducer tree} to define surface displacements while the lower section uses a set of columns as texture pixels. Here, a single \emph{tuner} solves for the caustic image and a set of \emph{tuners} with regular connectivity solves for the textured image.  \textbf{Deformation/texture:} The object is divided into an outer layer and inner volume using a stratum node. The interior volume is then voxelized and each voxel is assigned a layered material. As in the previous example, the outer layer is divided into columns which are used as pixels for the texture image. The \emph{tuner} setup is also similar to the previous example except the single \emph{tuner} is used to optimize the mechanical behavior of the object. \textbf{Facet caustics:} Here, we build facets by dividing an object into columns and then bisecting the columns horizontally with a plane. The orientation of this plane defines the angle of the facet surface. We use a separate \emph{tuner} to optimize each plane orientation.
\textbf{Subsurface scattering/texture:} The subsurface scattering/texture \emph{reducer tree} partitions the object into an inner volume and outer layer using a \emph{stratum node}. The inner volume is unimportant in this example so we place a constant material there. The outer material is divided into pixels using the \emph{column node}. These columns are filled with layered materials. We optimize each column separately using an associated \emph{tuner}. }
\label{fig:ReducerTreesAdditional}
\end{figure*}

\chapter{Discussion}
\biglet{T}{hrough} our series of experiments, the \emph{reducer tree} and \emph{tuner network} have allowed us to reuse a large number of software components.
In the extreme case, we arrive at our subsurface scattering algorithm by trivially adapting the same \emph{reducer tree} for texture mapping objects.
The power of component reuse is further elucidated by the presence of \emph{column nodes} in most examples and by our ability to reuse optimization schemes (such as branch and bound) in multiple algorithms.
The \emph{reducer tree} and \emph{tuner network} make these similarities easy to observe and exploit.
The only component whose reusability was not demonstrated in this paper is simulation.
In this work, we have aimed to fabricate objects with a wide range of physical properties and this necessitates the use of a wide range of simulation algorithms. Finally, once a whole process is configured, it is independent of input geometry and goal parameters. For example, we have run the spatially-varying albedo process with different geometries and input textures

The \emph{reducer-tuner model} is ideally suited for multi-material printing capable of producing objects with a wide range of different properties.
In order to showcase these strengths, we have fabricated our examples for an Objet500 Connex -- a phase change inkjet printer that uses photopolymers with a wide range of optical and mechanical properties. Even though only two materials can be used and mixed within a single object, our framework has been proven to be very useful. 
As the number of materials that can be printed simultaneously will grow, we expect the methodology presented here to increase in utility.
For other types of 3D printing technologies, Spec2Fab framework has a reduced use. In the case of 3D printing using a single, rigid material (e.g., fused filament fabrication or Stereolithography) the framework can be used to tune geometry of objects. For plaster-based 3D printers that produce full-color 3D prints, Spec2Fab framework can be employed to compute proper texturing of objects.

### 2013-05-03 thesis/abstract.tex
change name title

@@
 in partial fulfillment of the requirements for the degree of \\
-Doctor of Philosophy \\ % <--- replace this with Master of Science if you want a master's instead
+Master of Science \\ % <--- replace this with Master of Science if you want a master's instead
 \end{center}
@@
 \noindent\rule[0.5ex]{2in}{1pt} \\
-Thesis Supervisor: Your first advisor's name goes here \\
-Title: Title of supervisor, e.g., Professor of Electrical Engineering and Computer Science
+Thesis Supervisor: Wojciech Matusik\\
+Title:  Associate Professor of Electrical Engineering and Computer Science
 
-\vspace{.1in}
+%\vspace{.1in}
 
-\noindent Thesis Supervisor: Your second advisor's name goes here \\
-Title: Title of supervisor, e.g., Professor of Electrical Engineering and Computer Science
+%\noindent Thesis Supervisor: Your second advisor's name goes here \\
+%Title: Title of supervisor, e.g., Professor of Electrical Engineering and Computer Science

### 2013-05-03 thesis/abstract.tex
abstract future tense

@@
 Recently, several specific instances of this problem have been explored (e.g.,  appearance or elastic deformation), but they exist as isolated, monolithic algorithms.
-In this paper, we propose an abstraction mechanism that simplifies the design, development, implementation, and reuse of these algorithms.
-Our solution relies on two new data structures: a \emph{reducer tree} that efficiently parameterizes the space of material assignments and a \emph{tuner network} that describes the optimization process used to compute material arrangement.
-We provide an application programming interface for specifying the desired object and for defining parameters for the \emph{reducer tree} and \emph{tuner network}.
-We illustrate the utility of our framework by implementing several fabrication algorithms as well as demonstrating the manufactured results.
+In this proposal, I propose an abstraction mechanism that simplifies the design, development, implementation, and reuse of these algorithms.
+The solution relies on two new data structures: a \emph{reducer tree} that efficiently parameterizes the space of material assignments and a \emph{tuner network} that describes the optimization process used to compute material arrangement.
+As part of thesis work, I will provide an application programming interface for specifying the desired object and for defining parameters for the \emph{reducer tree} and \emph{tuner network}.
+I will illustrate the utility of my new framework by implementing several fabrication algorithms as well as demonstrating the manufactured results.
 

### 2013-05-03 thesis/Overview.tex
add chapters
we I future tense

@@
 \label{chap:design}
-The design of our general translational framework is guided by the following principles:
+\biglet{T}{he} design of my general translation framework is guided by the following principles:
 
@@
 
-We aim to separate the Spec2Fab process into two phases, the process configuration phase and the process use phase.
+I aim to separate the Spec2Fab process into two phases, the process configuration phase and the process use phase.
 The process configuration phase is typically done once by a skilled developer who  constructs a Spec2Fab translator.
@@
 	The process configuration phase produces a Spec2Fab translator which will assign a desired volumetric material distribution to a user supplied input geometry given a user specified goal.
-We describe this phase using two new data structures, the \emph{reducer tree} and \emph{tuner network}.
+A developer can describe this phase using two new data structures, the \emph{reducer tree} and \emph{tuner network}.
 The \emph{reducer tree} parameterizes a volumetric material assignment using a small set of \emph{geometry} and \emph{material nodes} while the \emph{tuner network} is used to describe an optimization process as a connected set of \emph{tuner} objects.
-Both \emph{nodes} and \emph{tuners} can be easily recombined and reused thus making  our framework highly modular.
+Both \emph{nodes} and \emph{tuners} can be easily recombined and reused thus making my framework highly modular.
 Furthermore,  \emph{nodes} and \emph{tuners} define abstract interfaces and thus developers can easily add new types of each.
-This makes our framework extensible.
+This makes my framework extensible.
 
-	\emph{Reducers} and \emph{tuners} are chosen to be independant of printer capabilities.
-Instead we account for printer type by altering the available materials that the translator may assign to the input geometry.
+	\emph{Reducers} and \emph{tuners} are chosen to be independent of printer capabilities.
+Instead, a user can account for printer type by altering the available materials that the translator may assign to the input geometry.
 This is important since it grants the \emph{reducer-tuner} model  device independence.
 Finally, the \emph{geometry nodes} of the \emph{reducer tree} are designed to function irrespective of input shape.
-Since the Spec2Fab translators produced by our algorithm use a composition of these node types, they are geometry independent.
+Since the Spec2Fab translators represented by my data structures use a composition of these node types, they are geometry independent.
 

### 2013-05-03 thesis/RelatedWork.tex
we I future tense

@@
 While there are many space-partitioning data structures (BSPs, Quad-trees, KD-trees, etc.), they are difficult to specify by hand and they are typically tied to the object geometry.
-Our \emph{reducer tree} is intuitive to construct but sufficiently general for representing material distributions.
+My \emph{reducer tree} is intuitive to construct but sufficiently general for representing material distributions.
 In addition, it is specified in an object-independent manner -- the same \emph{reducer tree} can be reused for processing different objects.
-Our second, new data structure which is responsible for optimizing material assignment is the \emph{tuner network}.
+My second, new data structure which is responsible for optimizing material assignment is the \emph{tuner network}.
 It is inspired by probabilistic graphical models~\cite{Jordan:1999} that have been popular for representing variable dependence in multi-variate optimization problems.
@@
 
-Our work is also inspired by the many instances of specification to fabrication translation pipelines that have been proposed recently.
+This work is also inspired by the many instances of specification to fabrication translation pipelines that have been proposed recently.
 These pipelines span a wide range of functional goals (e.g., mechanical, optical, appearance).
@@
 Finally, optimization-based approaches have also been employed to control the subsurface scattering of 3D printed multi-layered models~\cite{Dong:2010:FSS,Hasan:2010:PRO}.
-We seek to exploit the common form of the above works in order to generalize them.
+I seek to exploit the common form of the above works in order to generalize them.
 
 There have been studies of material assignment representations in other fields, primarily in mechanical engineering. 
-Here we only list a few representative works.
+Here I only list a few representative works.
 Kumar \textit{et al}.~\shortcite{Kumar1999} describe material composition by dividing a volume into sub-volumes.
@@
 
-In this work we focus on constructing a common model for encompassing the entire Spec2Fab problem.
-We are motivated by the similarities present in state-of-the-art algorithms.
+In this work I will focus on constructing a common model for encompassing the entire Spec2Fab problem.
+I am motivated by the similarities present in state-of-the-art algorithms.
 \autoref{tb:algorithms} shows the coordinate reduction methods as well as the optimization schemes used in all these prior approaches.
-Our key observation is that previous works share a common methodology and  a common set reduced coordinate components.
+A key observation is that previous works share a common methodology and  a common set reduced coordinate components.
 These components are then combined with (often off-the-shelf) optimization techniques to form new material assignment algorithms.
 This suggests that one could find a small set of components that can be tied together to synthesize  advanced methods.
-In this paper we attempt to identify these components as well as a suitable model for their interaction.
+In this thesis I will attempt to identify these components as well as a suitable model for their interaction.
 

### 2013-05-03 thesis/Conclusion.tex
we I tense

@@
 In this proposal I have taken the first step towards solving an open problem in computational fabrication --  creating a general translation process that transforms user-defined model specifications into printer and material-specific representations.
-Our process relies on two data structures to make this general translation process expressive and computationally tractable: a \emph{reducer tree} and a \emph{tuner network}.
-We have shown how existing instances of this translation can be expressed and combined within our system.
-We believe that our API and its reference implementation will simplify and encourage development of new translation processes.
+My process relies on two data structures to make this general translation process expressive and computationally tractable: a \emph{reducer tree} and a \emph{tuner network}.
+I will show how existing instances of this translation can be expressed and combined within my system.
+I believe that my API and its reference implementation will simplify and encourage development of new translation processes.
 
-Our framework offers many exciting opportunities for future work.
+My system can offer many exciting opportunities for future work.
 First, it would be extremely useful to implement many additional simulators in order to allow computing a variety of other properties, e.g., structural soundness, stability, material cost, and printing time.
 These simulators could be employed to expand the range of possible user-defined specifications.
-Similarly, only relatively simple error metrics have been tested within the tuning process.
+Similarly, only relatively simple error metrics have been proposed within the tuning process.
 The development of more sophisticated and, in particular, perceptually-driven material metrics remains a relatively unexplored research area.
-Finally, it would be very beneficial to couple our API with a visual interface to further simplify the task of translator construction.
+Finally, it would be very beneficial to couple my API with a visual interface to further simplify the task of translator construction.
 It is not obvious what the best visual interface for specifying functional or physical properties of these objects is and more research in this area is necessary.

### 2013-05-03 thesis/DataStructures.tex
we I tense

@@
 \label{chap:struct}
-\biglet{I}{n} this section, I describe the structure of the \emph{reducer tree} as well as all types of \emph{reducer nodes} implemented in our framework.
-We also show the structure of individual \emph{tuners} and how they can be arranged into the \emph{tuner network}.
+\biglet{I}{n} this section, I describe the structure of the \emph{reducer tree} as well as all types of \emph{reducer nodes} that will be implemented in my framework.
+I also show the structure of individual \emph{tuners} and how they can be arranged into the \emph{tuner network}.
 
@@
 Therefore, material assignment has to be computed using a reduced representation.
-We specify this representation using a \emph{reducer tree}.
+A developer specifies this representation using a \emph{reducer tree}.
 This structure is conceptually similar to those used in programmable shading systems (such as Cook's shade trees~\shortcite{Cook1984} or Maya Shader Networks).
-These systems are primarily concerned with assigning known materials and textures to an object's surface whereas we are seeking an optimal volumetric assignment from a defined set of materials.
-In order to accomplish this task, we build a tree-based data structure which contains the entire object volume as its root node.
-We define two classes of \emph{reducer nodes}: \emph{geometry nodes} and \emph{material nodes}.
+These systems are primarily concerned with assigning known materials and textures to an object's surface whereas I am seeking an optimal volumetric assignment from a defined set of materials. 
+In order to accomplish this task, a developer builds a tree-based data structure which contains the entire object volume as its root node. 
+I define two classes of \emph{reducer nodes}: \emph{geometry nodes} and \emph{material nodes}.
 
@@
 These can be attached to the object geometry or they can be defined in a global coordinate system.
-To demonstrate the flexibility of the \emph{reducer tree}, we define a small yet powerful set of partitioning nodes which are described as follows %used in our prototype
+To demonstrate the flexibility of the \emph{reducer tree}, I define a small yet powerful set of partitioning nodes which are described as follows 
  (\autoref{fig:geometryNodes}):\vspace{-0.25\baselineskip}
@@
 \includegraphics[width=0.7\linewidth]{figure/geometryNodes}
-\caption{2D representations  of the \emph{geometry nodes} used in our \emph{reducer tree}.}
+\caption{2D representations  of the \emph{geometry nodes} used in \emph{reducer trees}.}
 \label{fig:geometryNodes}
@@
 These contain a material assignment function $\lambda\left(x\right)$ that maps spatial coordinates to materials.
-We allow our \emph{material nodes} to assign a void material to regions of the volume.
+\emph{Material nodes} can assign a void material to regions of the volume.
 Hence, surface displacements and material assignments can be treated in a unified fashion.
 While \emph{material node} can be extended to implement arbitrary material assignment functions (such as Functionally Graded Materials), all the following results require only a single type of \emph{material node}, \emph{layered node}, which assigns $k$ material layers of varying thickness to a geometry partition.
-We can even assign a constant material to a region using a \emph{layered node} with a single layer.
+As a special case, a constant material for a region can be implemented as a \emph{layered node} with a single layer.
 
@@
 \autoref{fig:red1} shows two examples of \emph{reducer trees} and the resulting geometric distributions of materials.
-Since the tree describes a nested set of partitions, we can efficiently perform material queries by passing a query point through the tree until it arrives at a parameterization node. 
-We note that the \emph{reducer tree} does not inherently enforce material continuity between disjoint regions of the object; however, for material assignment problems, this is neither required nor desired.
+Since the tree describes a nested set of partitions, it can efficiently perform material queries by passing a query point through the tree until it arrives at a parameterization node. 
+Note that the \emph{reducer tree} does not inherently enforce material continuity between disjoint regions of the object; however, for material assignment problems, this is neither required nor desired.
 
@@
 \includegraphics[width=0.7\linewidth]{figure/redNetworkNew.pdf}
-\caption{Two examples of our \emph{reducer tree}. Left: in order to create an object producing a caustic, the input shape is first divided into columns. Next, each column is sliced by a plane.
+\caption{Two examples of \emph{reducer trees}. Left: in order to create an object producing a caustic, the input shape is first divided into columns. Next, each column is sliced by a plane.
 By assigning materials to lower parts of the columns, the microfacet surface is created.
@@
 \section{Tuners and Tuning the Reducer Tree}
-We define \emph{tuners} as an abstract interface between a \emph{reducer node} and an optimization algorithm. 
+I define \emph{tuners} as an abstract interface between a \emph{reducer node} and an optimization algorithm. 
 A \emph{reducer node} has parameters that control its space partitioning and material composition, e.g., \emph{stratum node} has a parameter which determines its thickness, \emph{column node} has parameters that control the width of columns.
@@
 Tuning the free parameters without taking into account this dependency usually yields suboptimal results.
-Therefore, we allow the \emph{tuners} to share information according to a user-specified graph structure.
-This allows our framework to interface with a wide range of existing graph-based optimization and inference algorithms.
-For example, Figure~\ref{fig:combine} (right) shows one of the \emph{tuner networks} used in our experiments.
+Therefore, I allow the \emph{tuners} to share information according to a user-specified graph structure.
+This allows my framework to interface with a wide range of existing graph-based optimization and inference algorithms.
+For example, Figure~\ref{fig:combine} (right) shows one of the \emph{tuner networks}.
 In this network, each node is connected to its four neighbors.
@@
 	Left: Two \emph{tuners} attached to a \emph{reducer tree}. Each \emph{tuner} is responsible for tuning the nodes in its attached subtree (denoted by shapes with similarly colored outlines). 
-	Right: One type of \emph{tuner network} used in our experiments.}
+	Right: One example of \emph{tuner network} that will be used in experiments.}
 \label{fig:combine}

### 2013-05-03 thesis/Results.tex
we I tense

@@
 \biglet{I}{n} order to evaluate capabilities of our system, I will implement a number of existing translation processes.
-Furthermore, the ease with which different algorithm components can be combined enabled creation of two new translation processes.
-The first is an algorithm that can produce objects with desired refractive properties and an associated texture.
-
-The second allows us to apply a desired texture to an object with prescribed deformation behavior.
-All of these processes, both from prior work and new ones, easily fit into our framework, and were manufactured using a Stratasys Object500 Connex  multi-material printer.
-The following paragraphs provide a detailed description of how the individual algorithms were designed with our system.
-All \emph{reducer trees} and the \emph{tuner networks} used for producing these results are presented in \autoref{fig:ReducerTreesAdditional}.
+Furthermore, the ease with which different algorithm components can be combined should enable creation of new combinations of translation processes.
+In this proposal, I will discuss two combinations in detail, while I can potentially make more combinations within the capabilities of the proposed system.
+The first combination is an algorithm that can produce objects with desired refractive properties and an associated texture.
+The second algorithm applies a desired texture to an object with prescribed deformation behavior.
+All of these processes, both from prior work and new ones, should easily fit into our framework. I plan to manufacture the objects using a Stratasys Object500 Connex  multi-material printer.
+The following paragraphs provide a detailed description of how the individual algorithms can be designed with my system.
+All \emph{reducer trees} and the \emph{tuner networks} for producing these results are presented in \autoref{fig:ReducerTreesAdditional}.
 
 \paragraph{Spatially-varying Albedo:}
-We have designed a Spec2Fab translator that allows for 3D printing of textured models (Figure~\ref{fig:texturedExamples}).
+I will design a Spec2Fab translator that allows 3D printing of textured models (Figure~\ref{fig:texturedExamples}).
 Being able to apply precisely specified spatially-varying albedo values to printed models is a crucial capability.
 However, no standard processes have been designed for this task so far.
-The input to our algorithm is a shape and its desired albedo texture.
-Since the texture is only affected by materials close to the surface, we use a \emph{stratum node} to divide the input shape into a thin shell and an inner volume.
-We then divide the outer layer into columns.
+The input to the texturing algorithm is a shape and its desired albedo texture.
+Since the texture is only affected by materials close to the surface, I can use a \emph{stratum node} to divide the input shape into a thin shell and an inner volume.
+The outer layer can be divided into columns.
 The set of printable colors is expanded by stacking translucent materials using the \verb|LayeredMaterial| Node.
@@
 Due to printer resolution, the range of albedo values that can be achieved is quantized.
-We therefore implement an error diffusion algorithm by connecting neighboring \emph{tuners}.
-In this simple algorithm, the simulation is a table lookup -- we measure the albedo value corresponding to different base materials.
+I therefore can implement an error diffusion algorithm by connecting neighboring \emph{tuners}.
+In this simple algorithm, the simulation is a table lookup using measured albedo value corresponding to different base materials.
 
 \paragraph{Heterogeneous Subsurface Scattering:}
-We have replicated the subsurface scattering process of Ha\v{s}an et al.~\shortcite{Hasan:2010:PRO} using our framework (Figure~\ref{fig:sub}).
-The input to our algorithm is a 3D mesh along with subsurface-scattering profiles defined at a set of surface points.
+I will replicate the subsurface scattering process of Ha\v{s}an et al.~\shortcite{Hasan:2010:PRO} using my framework (Figure~\ref{fig:sub}).
+The input to this algorithm is a 3D mesh along with subsurface-scattering profiles defined at a set of surface points.
 We use the same \emph{reducer tree} as in the texture example thereby simplifying the process configuration phase.
-The only difference is that we allow each column to have four layers of varying thickness and material.
-We use a branch and bound optimization algorithm which has been modified to handle continuous parameters by allowing discrete increments.
-We implement a bound estimate callback function specific to this problem.
+The only difference is that I will allow each column to have four layers of varying thickness and material. 
+I will use a branch and bound optimization algorithm which has been modified to handle continuous parameters by allowing discrete increments.
+I will implement a bound estimate callback function specific to this problem.
 Each column is optimized independently using the algorithm. 
-The simulation computes a scattering profile for given a stacking and the error metric compares the simulated and goal profiles using squared error.
-%We note that the ability to reuse Reducer Nodes simplifies the configuration of new processes.
+The simulation computes a scattering profile for a given stacking and the error metric compares the simulated and goal profiles using squared error.
 
@@
 \caption{
-	A marble chessboard with prescribed subsurface scattering properties.
+	A marble chessboard with prescribed subsurface scattering properties produced by Ha\v{s}an et al.~\shortcite{Hasan:2010:PRO}.
 	The insets show the samples under thin line illumination, and the graph shows the convergence of tuners for 10 out of 100 scattering profiles used in the example.
@@
 \paragraph{Goal-based Caustics:}
-We have configured two different processes for computing goal-based caustics (Figure~\ref{fig:caust2}).
+I will configure two different processes for computing goal-based caustics (Figure~\ref{fig:caust2}).
 While they define exactly the same goal, they have very different \emph{reducer trees} and \emph{tuner networks}.
@@
 The \emph{tuners} are executed many times until a user-specified convergence criterion is met. 
-In our examples, we use $45^2$ microlens and ran all the \emph{tuners} for $2000$ iterations.
-In the second process, based on the work of Finckh et al.~\shortcite{Finckh:2010}, we use a \emph{B-spline node} to represent a smooth caustic surface.
+In the second process, based on the work of Finckh et al.~\shortcite{Finckh:2010}, I will use a \emph{B-spline node} to represent a smooth caustic surface.
 This is in contrast to the potentially discontinuous surface in the method above.
 The reduced parameters are the height of each spline control point.
-We implement a simple caustics simulator for height fields.
+I will implement a simple caustics simulator for height fields.
 The simulated image is compared to the goal image using mean squared error.
-We used $60\times 60$ control points and render the simulated image at $240\times 240$ pixel resolution.
 
@@
 \includegraphics[width=0.65\linewidth]{figure/fig_caustic.pdf}
-\caption {3D printed lens arrays that each produce a caustic image of Einstein.
+\caption {3D printed lens arrays that each produce a caustic image of Einstein. The algorithms are proposed by Papas et al.~\shortcite{Marios:2011} and Finckh et al.~\shortcite{Finckh:2010}.
 Below we show convergence plots for both the microfacet and smooth surface optimizations.
@@
 \paragraph{Elastic Behavior:}
-In the spirit of Bickel et al.~\shortcite{Bickel:2009} we have implemented an algorithm to compute material distribution based on a desired force-displacement response.
+In the spirit of Bickel et al.~\shortcite{Bickel:2009}, I will implemented an algorithm to compute material distribution based on a desired force-displacement response.
 The input to this algorithm is a mesh, a simulation configuration, and a desired shape.
 Simulation configuration includes vertex constraints and forces applied to the mesh.
-For this example, we use a co-rotational finite element method (FEM) simulation with linearly elastic materials to estimate the objects deformation.
-For the \emph{reducer tree}, we use a voxel partition to divide the object into a low-resolution grid.
-We assign a single material to each grid cell.
+For this example, I will use a co-rotational finite element method (FEM) simulation with linearly elastic materials to estimate the objects deformation.
+For the \emph{reducer tree}, I will use a voxel partition to divide the object into a low-resolution grid.
+I will assign a single material to each grid cell.
 The FEM simulator queries the \emph{reducer tree} for material assignments at arbitrary spatial locations.
-We use the same branch and bound algorithm as in our subsurface-scattering process but with a different bound computation callback function.
-We use the mean squared distance between the simulated and the desired shapes as the error metric.
-We have designed a simple experiment to validate our process in which we set the goal of our optimization to be a given deformed state (\autoref{fig:book}).
+I will use the same branch and bound algorithm as in our subsurface-scattering process but with a different bound computation callback function.
+I will use the mean squared distance between the simulated and the desired shapes as the error metric.
+I will design a simple experiment to validate this process in which I set the goal of our optimization to be a given deformed state (\autoref{fig:book}).
 
@@
 \paragraph{Combining Caustics and Spatially-varying Albedo:}
-The first of our new combined translation processes incorporates both smooth caustics and texture mapping.
-More specifically, we compute a transparent slab with a texture image that, when illuminated, casts a prescribed caustic image.
+The first of my new combined translation processes incorporates both smooth caustics and texture mapping.
+More specifically, I will compute a transparent slab with a texture image that, when illuminated, casts a prescribed caustic image.
 The input slab is split into two pieces using a \emph{plane node} as shown in Figure~\ref{fig:ReducerTreesAdditional}.
@@
 \paragraph{Combining Deformable Object and Spatially-varying Albedo:}
-Our second new process combines spatially-varying albedo and elastic deformation properties.
+My second new process combines spatially-varying albedo and elastic deformation properties.
 This is a very useful combination since when modeling objects we would like to specify both their appearance and ``feel''.
 In this process, the input shape is divided into a thin shell and an inner volume.
-We optimize for the deformation behavior and the texture independently due to the limitations of our current FEM simulator.
+I will optimize for the deformation behavior and the texture independently due to the limitations of our current FEM simulator.
 As the outer shell is very thin, it has negligible influence on overall object deformation.
@@
 \chapter{Discussion}
-\biglet{T}{hrough} our series of experiments, the \emph{reducer tree} and \emph{tuner network} have allowed us to reuse a large number of software components.
-In the extreme case, we arrive at our subsurface scattering algorithm by trivially adapting the same \emph{reducer tree} for texture mapping objects.
-The power of component reuse is further elucidated by the presence of \emph{column nodes} in most examples and by our ability to reuse optimization schemes (such as branch and bound) in multiple algorithms.
-The \emph{reducer tree} and \emph{tuner network} make these similarities easy to observe and exploit.
-The only component whose reusability was not demonstrated in this paper is simulation.
-In this work, we have aimed to fabricate objects with a wide range of physical properties and this necessitates the use of a wide range of simulation algorithms.
+\biglet{T}{hrough} the above series of experiments, I will confirm whether \emph{reducer tree} and \emph{tuner network} can allow us to reuse a large number of software components.
+In the extreme case, the subsurface scattering algorithm can be obtained by trivially adapting the same \emph{reducer tree} for texture mapping objects.
+The power of component reuse is further elucidated by the presence of \emph{column nodes} in most examples and by the reuse of optimization schemes (such as branch and bound) in multiple algorithms.
+The \emph{reducer tree} and \emph{tuner network} will make these similarities easy to observe and exploit.
+The only component whose reusability was not demonstrated in this proposal is simulation.
+In this work, I will aim to fabricate objects with a wide range of physical properties and this necessitates the use of a wide range of simulation algorithms.
 Finally, once a whole process is configured, it is independent of input geometry and goal parameters.
-For example, we have run the spatially-varying albedo process with different geometries and input textures
+For example, I can run the spatially-varying albedo process with different geometries and input textures
 
 The \emph{reducer-tuner model} is ideally suited for multi-material printing capable of producing objects with a wide range of different properties.
-In order to showcase these strengths, we have fabricated our examples for an Objet500 Connex -- a phase change inkjet printer that uses photopolymers with a wide range of optical and mechanical properties.
+In order to showcase these strengths, I will fabricated my examples for an Objet500 Connex -- a phase change inkjet printer that uses photopolymers with a wide range of optical and mechanical properties.
 Even though only two materials can be used and mixed within a single object, our framework has been proven to be very useful.

### 2013-05-03 thesis/chap1.tex
we I tense

@@
 
-Our work is motivated by the recent research efforts in the computer graphics community to create specific instances of the translation process, for example, subsurface scattering~\cite{Hasan:2010:PRO,Dong:2010:FSS} or deformation properties~\cite{Bickel:2010:DAF}.
+My work is motivated by the recent research efforts in the computer graphics community to create specific instances of the translation process, for example, subsurface scattering~\cite{Hasan:2010:PRO,Dong:2010:FSS} or deformation properties~\cite{Bickel:2010:DAF}.
 However, each of these instances is a custom, monolithic solution which is difficult to extend, combine, or modify.
@@
 Various optimization strategies can also be explored with lower implementation burden.
-In order to show these advantages, we illustrate how existing computational design processes fit into this framework and how they can be combined.
-We demonstrate the results of these algorithms on a variety of different examples fabricated using 3D printers.
+In order to show these advantages, I will illustrate how existing computational design processes fit into this framework and how they can be combined.
+I will demonstrate the results of these algorithms on a variety of different examples fabricated using 3D printers.

### 2013-05-03 thesis/Results.tex
figure caption

@@
 \includegraphics*[clip, width = \linewidth]{figure/ReducerNetworksSuplemental}
-\caption{The figure shows all \emph{reducer trees} used in this paper.
+\caption{The figure shows all \emph{reducer trees} proposed in this proposal.
 \textbf{Smooth caustics:} The smooth caustics tree consists of a spline surface that divides the geometry into an inner surface filled with a transparent material and an outer, void surface.
-This allows us to approximate displacement mapping.
-Here, a single \emph{tuner} is used deform the spline surface.
+Void material can be used to implement displacement mapping.
+Here, a single \emph{tuner} can be used ti deform the spline surface.
 \textbf{Smooth caustics/texture:} The smooth caustics/texture \emph{reducer tree} splits the object into upper and lower sections using a plane.
@@
 The \emph{tuner} setup is also similar to the previous example except the single \emph{tuner} is used to optimize the mechanical behavior of the object.
-\textbf{Facet caustics:} Here, we build facets by dividing an object into columns and then bisecting the columns horizontally with a plane.
+\textbf{Facet caustics:} Here, I will build facets by dividing an object into columns and then bisecting the columns horizontally with a plane.
 The orientation of this plane defines the angle of the facet surface. 
-We use a separate \emph{tuner} to optimize each plane orientation.
+I will use a \emph{tuner network} to optimize for smooth plane orientations.
 \textbf{Subsurface scattering/texture:} The subsurface scattering/texture \emph{reducer tree} partitions the object into an inner volume and outer layer using a \emph{stratum node}.
-The inner volume is unimportant in this example so we place a constant material there.
+The inner volume is unimportant in this example so I  can place a constant material there.
 The outer material is divided into pixels using the \emph{column node}.
 These columns are filled with layered materials.
-We optimize each column separately using an associated \emph{tuner}.
-}
+I can optimize each column separately using an associated \emph{tuner}.}
 \label{fig:ReducerTreesAdditional}
 \end{figure*}
-
 \chapter{Discussion}

### 2013-05-03 thesis/1_cover.tex
add cover page

@@
 \vspace{.1in}
-Donglai Wei \\
+Desai Chen\\
 
@@
 \vspace{-.25in}
-{\flushright Your first supervisor's name here \\
-Title of supervisor, e.g., Professor of Electrical Engineering and Computer Science \\
+{\flushright Wojciech Matusik\\
+Title of supervisor, Associate Professor of Electrical Engineering and Computer Science \\
 Thesis Supervisor \\
